### 2022-02-21 elsarticle-template-num.tex
Initial Overleaf Import

%% 
%% Copyright 2007-2020 Elsevier Ltd
%% 
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%% 
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%% 
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01
%%
%% 
%%
%% $Id: elsarticle-template-num.tex 190 2020-11-23 11:12:32Z rishi $
%%
%%
\documentclass[preprint, 3p, 12pt]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% For including figures, graphicx.sty has been loaded in
%% elsarticle.cls. If you prefer to use the old commands
%% please give \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers.
%% \usepackage{lineno}

\journal{Nuclear Instruments and Methods in Physics Research, A}

\begin{document}

\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for theassociated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for theassociated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for theassociated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \affiliation{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%% \fntext[label3]{}

\title{Fixed-optics four-dimensional emittance measurement at the Spallation Neutron Source}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{}
%% \affiliation[label1]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}
%%
%% \affiliation[label2]{organization={},
%%             addressline={},
%%             city={},
%%             postcode={},
%%             state={},
%%             country={}}

\author[author1]{A. Hoover}
\affiliation[author1]{organization={The University of Tennessee},%Department and Organization
            addressline={}, 
            city={Knoxville},
            postcode={37996}, 
            state={Tennessee},
            country={USA}}

\author[author2]{N. J. Evans}
\affiliation[author2]{organization={Oak Ridge National Laboratory},%Department and Organization
            addressline={One Bethel Valley Road}, 
            city={Oak Ridge},
            postcode={37831}, 
            state={Tennessee},
            country={USA}}

\begin{abstract}
Tentative: A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance could mitigate space charge effects in circular accelerators. A scheme to approximately create such a distribution is being tested in the Spallation Neutron Source (SNS). A critical component of these efforts is to measure the 4D emittance. The 4D emittance can be reconstructed from at least four measurements of the real-space moments with different transfer matrices connecting the reconstruction and measurement locations, accomplished by varying either the machine optics (multi-optics method) or the measurement location (fixed-optics method). In this paper, we discuss the implementation of a variant of the multi-optics method using the four available wire-scanners near the SNS target, as well as the modification of the wire-scanner region to utilize the fixed-optics method — a method that is preferred due to its speed but can potentially lead to unacceptable bias and uncertainty in the reconstructed emittances. We then demonstrate the usefulness of the fixed-optics method by reconstructing the 4D emittance as a function of time during accumulation in the SNS ring for several initial experiments. 
\end{abstract}

% %%Graphical abstract
% \begin{graphicalabstract}
% %\includegraphics{grabs}
% \end{graphicalabstract}

% %%Research highlights
% \begin{highlights}
% \item Research highlight 1
% \item Research highlight 2
% \end{highlights}

% \begin{keyword}
% %% keywords here, in the form: keyword \sep keyword

% %% PACS codes here, in the form: \PACS code \sep code

% %% MSC codes here, in the form: \MSC code \sep code
% %% or \MSC[2008] code \sep code (2000 is the default)

% \end{keyword}

\end{frontmatter}

%% \linenumbers

%% main text
\section{Introduction}
\label{sec:Introduction}

This is a sentence to fill some space.

\section{Methods}
\label{sec:Methods}

This is a sentence to fill some space.

\section{Example application}
\label{sec:Example application}

This is a sentence to fill some space.

\section{Conclusion}
\label{sec:Conclusion}

This is a sentence to fill some space.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

%% If you have bibdatabase file and want bibtex to generate the
%% bibitems, please use
%%
%%  \bibliographystyle{elsarticle-num} 
%%  \bibliography{<your bibdatabase>}

%% else use the following coding to input the bibitems directly in the
%% TeX file.

\begin{thebibliography}{00}

%% \bibitem{label}
%% Text of bibliographic item

\bibitem{}

\end{thebibliography}
\end{document}
\endinput
%%
%% End of file `elsarticle-template-num.tex'.

### 2022-02-21 article.tex
Delete template files

--- 2022-02-21 elsarticle-template-num.tex
@@
 %%
-\documentclass[preprint, 3p, 12pt]{elsarticle}
+\documentclass[preprint,3p,twocolumn]{elsarticle}
 
@@
 
-This is a sentence to fill some space.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Morbi cursus dapibus diam non euismod.
+Quisque vitae pulvinar nulla.
+Maecenas lobortis elementum varius.
+Suspendisse at purus nec massa pharetra luctus.
+Morbi tellus magna, aliquet a ultrices aliquet, mollis sed tortor.
+Nulla facilisi.
+Vestibulum in erat a turpis tempor porta.
+Nunc mi lorem, ornare eget nibh eget, lacinia posuere orci.
+Maecenas varius mattis nunc, ac facilisis nibh aliquet ut.
+Integer eu eros nulla.
+Etiam facilisis sapien vitae velit finibus mattis.
+
+Donec facilisis, orci a pretium venenatis, leo metus elementum ligula, sit amet mattis sem lectus ut dolor.
+Fusce mollis quis nunc vel venenatis.
+Nulla nibh dolor, malesuada nec dapibus interdum, commodo sed velit.
+Maecenas feugiat nisl in rutrum bibendum.
+Nam mi nunc, ornare eu congue at, lacinia vitae sapien.
+Nullam sagittis aliquam sem, a mollis ex.
+Quisque blandit ex tellus, id consectetur purus pretium eget.
+Integer ligula urna, tincidunt ut egestas in, auctor vel neque.
+Etiam in nunc semper, dapibus turpis a, rhoncus nulla.
+Phasellus bibendum tortor eu ante vehicula volutpat.
+Praesent eget lorem et tellus vestibulum pharetra.
+Mauris lacus risus, elementum commodo magna eu, feugiat faucibus tellus.
+Mauris interdum, mauris in mattis ultricies, massa felis tristique sem, et ultrices lacus orci consectetur nibh.
+
+Cras porttitor ut odio vel pharetra.
+Proin porttitor quis mi a ultrices.
+Morbi egestas neque at vestibulum tristique.
+Praesent consequat enim eget nulla condimentum vestibulum ac sed turpis.
+Suspendisse libero ex, mollis eget erat et, pretium iaculis sapien.
+Nulla ultricies feugiat sapien non pellentesque.
+Duis tortor felis, ullamcorper a porttitor sit amet, tempor quis lorem.
+Maecenas blandit faucibus dolor, eu laoreet libero interdum non.
+Aliquam interdum ante lacus, vitae porta nunc ultricies id.
+Fusce porta interdum leo a bibendum.
+Proin tristique purus et bibendum rutrum.
+Duis molestie vulputate urna, vitae interdum diam sodales nec.
+Nunc pulvinar purus erat, sit amet consectetur magna mattis eu.
+Etiam tempus malesuada feugiat.
+Vivamus vulputate nunc ut eros imperdiet lobortis.
+
+Interdum et malesuada fames ac ante ipsum primis in faucibus.
+Vivamus ultricies felis blandit dolor vestibulum semper.
+Nunc ultricies erat magna, id laoreet nisl maximus maximus.
+Etiam non tortor lectus.
+Suspendisse sodales mi elit, non malesuada orci condimentum ac.
+Sed tincidunt, urna eget facilisis ultricies, nulla diam laoreet nibh, sit amet ullamcorper eros leo faucibus nisi.
+Fusce eget vestibulum odio.
+Integer hendrerit erat sit amet tincidunt consequat.
+Quisque magna metus, iaculis ut tortor id, euismod posuere urna.
+Quisque a sapien tincidunt, laoreet eros eget, interdum lectus.
+Fusce ac faucibus felis.
+Praesent viverra lorem in porttitor viverra.
+Ut consectetur congue risus, vitae venenatis sapien imperdiet in.
+Sed rutrum, nulla ut ultrices suscipit, nulla lacus dapibus mi, id viverra ante velit nec mi.
+
+Vestibulum a turpis consequat, imperdiet lectus nec, gravida est.
+Morbi ut mi tempus tellus maximus ullamcorper at ut sem.
+Morbi dolor libero, finibus at porta a, suscipit a ex.
+Integer enim lectus, auctor a posuere commodo, egestas pharetra ipsum.
+Aliquam sit amet cursus risus.
+Praesent sollicitudin neque vitae mattis dignissim.
+Maecenas metus elit, molestie non fermentum a, iaculis sit amet diam.
+Nullam molestie aliquet sapien, hendrerit congue lacus.
+Sed nec nunc at tellus tincidunt scelerisque nec in turpis.
+Nam sed vulputate sem.
+Integer accumsan, odio ut vestibulum vehicula, tortor tellus sagittis nibh, eleifend finibus quam quam sagittis dui.
+Cras mollis diam nec lectus fringilla efficitur.
+\cite{Xiao2013}
 
@@
 
-\begin{thebibliography}{00}
+\bibliographystyle{elsarticle-num} 
+\bibliography{bibliography.bib}
 
-%% \bibitem{label}
-%% Text of bibliographic item
+% \begin{thebibliography}{00}
 
-\bibitem{}
+% %% \bibitem{label}
+% %% Text of bibliographic item
 
-\end{thebibliography}
+% \bibitem{}
+
+% \end{thebibliography}
+
 \end{document}

### 2022-02-22 article.tex
Change to times font

@@
 %%
-\documentclass[preprint,3p,twocolumn]{elsarticle}
+\documentclass[final,5p,twocolumn,times]{elsarticle}
 
@@
 %% \usepackage{lineno}
+
+\usepackage{subcaption}
 
@@
 
-This is a sentence to fill some space.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{figures/multi_optics_measurement.pdf}
+    % \par\medskip
+    \begin{tabular}{lll}
+        \small\textbf{Parameter} & \small\textbf{Measurement} & \small\textbf{Model} \\
+        % \midrule
+        \small$\beta_x$ [m/rad] & \small22.06 $\pm$ 0.29 & \small22.00 \\
+        \small$\beta_y$ [m/rad] & \small4.01 $\pm$ 0.02 & \small3.81 \\
+        \small$\alpha_x$ & \small2.33 $\pm$ 0.04 & \small2.37 \\
+        \small$\alpha_y$ & \small-0.49 $\pm$ 0.01 & \small-0.60 \\
+        \small$\varepsilon_1$ [mm~mrad] & \small33.02 $\pm$ \small0.05 & - \\
+        \small$\varepsilon_2$ [mm~mrad] & \small25.67 $\pm$ \small1.03 & - \\
+        \small$\varepsilon_x$ [mm~mrad] & \small32.85 $\pm$ \small0.05 & - \\
+        \small$\varepsilon_y$ [mm~mrad] & \small25.87 $\pm$ \small0.12 & - \\
+      \end{tabular}
+    % \par\medskip
+    \caption{Reconstructed beam parameters and graphical output (in normalized phase space) from a multi-optics emittance measurement of a production beam.}
+    \label{fig:multi_optics_measurement}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{figures/sensitivity_scan.pdf}
+    \caption{Scan of the phase advances at WS24.}
+    \label{fig:sensitivity_scan}
+\end{figure}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}{0.95\columnwidth}
+        \includegraphics[width=\textwidth]{figures/mismatch.pdf}
+        \caption{}
+        \label{fig:mismatch}
+    \end{subfigure}
+    \hspace{1cm}
+    \begin{subfigure}{0.95\columnwidth}
+        \includegraphics[width=\textwidth]{figures/mismatch_unequal_emittances.pdf}
+        \caption{}
+        \label{fig:mismatch_unequal_emittances}
+    \end{subfigure}
+    \caption{Simulated fractional error and standard deviation of reconstructed intrinsic emittances as a function of the beam mismatch parameter.
+(a) $\varepsilon_1 / \varepsilon_2 = 1$; (b) $\varepsilon_1 / \varepsilon_2 = 3$.}
+\end{figure*}
 
@@
 
-This is a sentence to fill some space.
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.49\columnwidth}
+        \includegraphics[width=\textwidth]{figures/emittances_exp1a.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.49\columnwidth}
+        \includegraphics[width=\textwidth]{figures/emittances_exp1b.pdf}
+    \end{subfigure}
+    \caption{Caption.}
+    \label{fig:mismatch}
+\end{figure}
 

### 2022-02-22 article.tex
Copy/paste thesis into body of text

--- 2022-02-21 elsarticle-template-num.tex
@@
 %%
-\documentclass[preprint, 3p, 12pt]{elsarticle}
+\documentclass[final,5p,twocolumn,times]{elsarticle}
 
@@
 
+\usepackage{subcaption} % subfigures
+\usepackage{gensymb} % \degree symbol
+\usepackage{bm}
+\usepackage{amsmath}
+
 \journal{Nuclear Instruments and Methods in Physics Research, A}
@@
 %% use the tnoteref command within \title for footnotes;
-%% use the tnotetext command for theassociated footnote;
+%% use the tnotetext command for the associated footnote;
 %% use the fnref command within \author or \address for footnotes;
-%% use the fntext command for theassociated footnote;
+%% use the fntext command for the associated footnote;
 %% use the corref command within \author for corresponding author footnotes;
-%% use the cortext command for theassociated footnote;
+%% use the cortext command for the associated footnote;
 %% use the ead command for the email address,
@@
 In this paper, we discuss the implementation of a variant of the multi-optics method using the four available wire-scanners near the SNS target, as well as the modification of the wire-scanner region to utilize the fixed-optics method — a method that is preferred due to its speed but can potentially lead to unacceptable bias and uncertainty in the reconstructed emittances.
-We then demonstrate the usefulness of the fixed-optics method by reconstructing the 4D emittance as a function of time during accumulation in the SNS ring for several initial experiments.
+We then demonstrate the usefulness of the fixed-optics method by reconstructing the 4D emittance as a function of time during accumulation in the SNS ring.
 \end{abstract}
@@
 
-This is a sentence to fill some space.
+A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance — i.e.
+volume in $x$-$x'$-$y$-$y'$ phase space — could mitigate space charge effects in circular accelerators \cite{Danilov2003, Burov2010, Holmes2018, Hoover2021}.
+A scheme to approximately create such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source \cite{Hoover2021HB, Hoover2021Thesis}.
+A critical component of these efforts is to measure the 4D beam emittance throughout accumulation.
 
-\section{Methods}
-\label{sec:Methods}
+[\dots...]
 
-This is a sentence to fill some space.
+\section{Four-dimensional emittance measurement}
+
+It is often sufficient to characterize a phase space distribution by its covariance matrix $\bm{\Sigma} = \langle{\mathbf{x}\mathbf{x}^T}\rangle$, where $\mathbf{x}$ is the phase space coordinate vector and $\langle{\dots}\rangle$ represents the average over the distribution.
+In the transverse plane:
+%
+\begin{equation}\label{eq:covariance_matrix}
+\begin{aligned}
+    \bm{\Sigma} &= 
+    \begin{bmatrix}
+        \langle{xx}\rangle & \langle{xx'}\rangle & \langle{xy}\rangle & \langle{xy'}\rangle \\
+        \langle{xx'}\rangle & \langle{x'x'}\rangle & \langle{x'y}\rangle & \langle{x'y'}\rangle \\
+        \langle{xy}\rangle & \langle{x'y}\rangle & \langle{yy}\rangle & \langle{yy'}\rangle \\
+        \langle{xy'}\rangle & \langle{x'y'}\rangle & \langle{yy'}\rangle & \langle{y'y'}\rangle 
+    \end{bmatrix}
+    &= 
+    \begin{bmatrix}
+        \bm{\sigma}_{xx} & \bm{\sigma}_{xy} \\
+        \bm{\sigma}^T_{xy} & \bm{\sigma}_{yy}
+    \end{bmatrix}.
+\end{aligned}
+\end{equation}
+%
+The covariance matrix defines an ellipsoid from $\mathbf{x}^T \bm{\Sigma}^{-1} \mathbf{x} = 1$.
+The 4D emittance $\varepsilon_{4D}$ is proportional to the volume of the this ellipsoid and is conserved in any linear focusing system.
+It is defined by
+%
+\begin{equation}
+    \varepsilon_{4D} = \left|{\bm{\Sigma}}\right|^{1/2} = \varepsilon_1\varepsilon_2 \le \varepsilon_x\varepsilon_y,
+\end{equation}
+%
+where $|...|$ is the determinant.
+We have also defined the intrinsic emittances $\varepsilon_{1,2}$, which are individually conserved.
+The intrinsic emittances are found by a symplectic diagonalization of $\bm{\Sigma}$ \cite{Dragtbook}, i.e., they are the imaginary components of the eigenvalues of $\bm{\Sigma}\mathbf{U}$, where $\mathbf{U}$ is the unit symplectic matrix:
+%
+\begin{equation}
+    \mathbf{U} = 
+    \begin{bmatrix}
+        0 & 1 & 0 & 0 \\
+        -1 & 0 & 0 & 0 \\
+        0 & 0 & 0 & 1 \\
+        0 & 0 & -1 & 0
+    \end{bmatrix}.
+\end{equation}
+%
+The apparent emittances $\varepsilon_x = \left|{\bm\sigma}_{xx}\right|^{1/2}$ and $\varepsilon_y = \left|{\bm\sigma}_{yy}\right|^{1/2}$ are conserved only in uncoupled linear focusing systems.
+The intrinsic and apparent emittances coincide in the absence of cross-plane correlations ($\bm{\sigma}_{xy} = 0$).
+
+The covariance matrix can be reconstructed from measurements of the $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{xy}\rangle$ moments.
+\cite{book:Minty2003}.
+We seek to reconstruct $\bm{\Sigma}$ at position $a$ by measuring $\langle{xx}\rangle$, $\langle{yy}\rangle$ and $\langle{xy}\rangle$ at position $b$, downstream of $a$.
+Assuming linear transport, the two covariance matrices are related by $\bm{\Sigma}_b = \mathbf{M} \bm{\Sigma}_a \mathbf{M}^T$, where $\mathbf{M}$ is the linear transfer matrix from $a$ to $b$.
+Each measurement gives the following linear system of equations:
+%
+\begin{equation}
+    \begin{bmatrix}
+        {\langle{xx}\rangle}^{} \\
+        {\langle{xy}\rangle}^{} \\
+        {\langle{yy}\rangle}^{} \\
+    \end{bmatrix}_b
+    = \mathbf{A}
+    \begin{bmatrix}
+        \langle{xx}\rangle \\
+        \langle{xx'}\rangle \\
+        \langle{xy}\rangle \\
+        \langle{xy'}\rangle \\
+        \langle{x'x'}\rangle \\
+        \langle{x'y}\rangle \\
+        \langle{x'y'}\rangle \\
+        \langle{yy}\rangle \\
+        \langle{yy'}\rangle \\
+        \langle{y'y'}\rangle \\
+    \end{bmatrix}_a
+    .
+\end{equation}
+%
+The transpose of the coefficient matrix $\mathbf{A}$ is \cite{Wolski2020}
+%
+\begin{equation}
+    \mathbf{A}^T = 
+    \begin{bmatrix}
+        M_{11}M_{11} & M_{11}M_{31} & M_{31}M_{31} \\
+        2M_{11}M_{12} & M_{12}M_{31} + M_{11}M_{32} & 2M_{31}M_{32} \\
+        2M_{11}M_{13} & M_{13}M_{31} + M_{11}M_{33} & 2M_{31}M_{33} \\
+        2M_{11}M_{14} & M_{14}M_{31} + M_{11}M_{34} & 2M_{31}M_{34} \\
+        M_{12}M_{12} & M_{12}M_{32} & M_{32}M_{32} \\
+        2M_{12}M_{13} & M_{13}M_{32} + M_{12}M_{33} & 2M_{32}M_{33} \\
+        2M_{12}M_{14} & M_{14}M_{32} + M_{12}M_{34} & 2M_{32}M_{34} \\
+        M_{13}M_{13} & M_{13}M_{33} & M_{33}M_{33} \\
+        2M_{13}M_{14} & M_{14}M_{33} + M_{13}M_{34} & 2M_{33}M_{34} \\
+        M_{14}M_{14} & M_{14}M_{34} & M_{34}M_{34}
+    \end{bmatrix}
+\end{equation}
+%
+where $M_{ij}$ is the $i$,$j$ element of $\mathbf{M}$.
+We repeat the measurement at least four times with different transfer matrices — either by varying the optics or varying the measurement location — and solve the system using linear least squares (LLSQ).
+
+\section{Implementation in the SNS}
+
+The real space moments of an accumulated beam in the SNS can be estimated using four wire-scanners — labeled WS20, WS21, WS23, and WS24 — in the ring-target beam transport (RTBT) section of the machine.
+The wire-scanner locations, quadrupole locations, and nominal optical functions are shown in Fig.~\ref{fig:rtbt}.
+%
+\begin{figure*}[!t]
+    \centering
+    \includegraphics[width=0.7\columnwidth]{figures/rtbt.png}
+    \hspace{1cm}
+    \includegraphics[width=\columnwidth]{figures/rtbt_optics.pdf}
+    \caption{The wire-scanner region of the ring-target beam transport (RTBT) section of the SNS.}
+    \label{fig:rtbt}
+\end{figure*}
+%
+
+The wire-scanners are run in parallel and take approximately five minutes to move across the beam and return to their original positions.
+Their step size is 3 mm and their dynamic range is approximately 100.
+They are run at a beam pulse frequency of 1 Hz.\footnote{Each data point corresponds to a separate beam pulse, so the measurement relies on pulse-to-pulse stability.} Each wire-scanner has a horizontal, vertical, and diagonal wire, producing $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$, where the $u$ axis is tilted at angle $\phi = \pi/4$ above the $x$ axis, as well as $\langle{xy}\rangle$ from
+%
+\begin{equation}
+    \langle{xy}\rangle = \frac{\langle{uu}\rangle - \langle{xx}\rangle \cos^2\phi - \langle{yy}\rangle \sin^2\phi}{2\sin\phi\cos\phi}
+    .
+\end{equation}
+%
+
+We first implemented a variant of the multi-optics method.
+In 2D emittance measurements, the phase advance from the reconstruction location to the measurement location is typically varied in a $180\degree$ range.\footnote{The phase advances are calculated under the assumption that the beam Twiss parameters are matched to the lattice Twiss parameters at the reconstruction location.} Prat and Aiba \cite{Prat2014} applied this strategy to the 4D emittance measurement: in the first half of the scan, the horizontal phase advance was varied while the vertical phase advance was held fixed, and in the second half of the scan, the vertical phase advance was varied while the horizontal phase advance was held fixed.
+Since the four SNS wire-scanners are already spaced somewhat evenly in phase advance, maximal phase coverage is possible by varying the phase advances at each wire-scanner in a $30\degree$ window.
+But control of the phase advances between each wire-scanner is limited due to the shared power supplies of the quadrupoles in the wire-scanner region.
+There are two power supplies in the wire-scanner region: one controls {QH18, QH20, QH22, QH24} and one controls {QH19, QH21, QH23, QH25} (the last five quadrupoles are controlled independently — see Fig.~\ref{fig:rtbt}).
+In addition to these constraints, the $\beta$ functions must be kept small in the wire-scanner region and must remain close to their nominal values at the target.
+
+We chose to vary the phase advances from QH18 (the first varied quadrupole) to WS24 (the last wire-scanner), which also changes the phase advances at WS20, WS21, and WS23 by similar amounts.
+To set the phase advances at WS24 while constraining the beam size in the wire-scanner region, the two power supplies (eight quadrupoles) upstream of WS24 were varied to minimize the following cost function:
+%
+\begin{equation}
+    C(\mathbf{g}) = \left\Vert{\tilde{\bm{\mu}} - \bm{\mu} }\right\Vert^2
+    + 
+    \epsilon
+    \left\Vert
+        \Theta\left(
+            \tilde{\bm{\beta}}_{max} - \bm{\beta}_{max}
+        \right)
+    \right\Vert^2
+    .
+\end{equation}
+%
+The quadrupole strengths are contained in the vector $\mathbf{g}$.
+The calculated and desired phase advances at WS24 are $\bm{\mu} = (\mu_x, \mu_y)$, and $\tilde{\bm{\mu}} = (\tilde{\mu}_x, \tilde{\mu}_y)$, respectively.
+The maximum calculated and allowed $\beta$ functions in the wire-scanner region are $\bm{\beta}_{max} = (\beta_{x_{max}}, \beta_{y_{max}})$ and $\tilde{\bm{\beta}}_{max} = (\tilde{\beta}_{x_{max}}, \tilde{\beta}_{y_{max}})$, respectively.
+$\Theta$ is the Heaviside step function.
+Finally, $\epsilon$ is a constant.
+
+This multi-optics method was tested on a fully accumulated production beam in the SNS using ten total measurements (forty profiles), taking around one hour.
+The result of the reconstruction is shown in Fig.~\ref{fig:multi_optics_measurement}.
+%
+\begin{figure}[!b]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/multi_optics_measurement.pdf}
+    % \par\medskip
+    \begin{tabular}{lll}
+        \small\textbf{Parameter} & \small\textbf{Measurement} & \small\textbf{Model} \\
+        % \midrule
+        \small$\beta_x$ [m/rad] & \small22.06 $\pm$ 0.29 & \small22.00 \\
+        \small$\beta_y$ [m/rad] & \small4.01 $\pm$ 0.02 & \small3.81 \\
+        \small$\alpha_x$ & \small2.33 $\pm$ 0.04 & \small2.37 \\
+        \small$\alpha_y$ & \small-0.49 $\pm$ 0.01 & \small-0.60 \\
+        \small$\varepsilon_1$ [mm~mrad] & \small33.02 $\pm$ \small0.05 & - \\
+        \small$\varepsilon_2$ [mm~mrad] & \small25.67 $\pm$ \small1.03 & - \\
+        \small$\varepsilon_x$ [mm~mrad] & \small32.85 $\pm$ \small0.05 & - \\
+        \small$\varepsilon_y$ [mm~mrad] & \small25.87 $\pm$ \small0.12 & - \\
+      \end{tabular}
+    % \par\medskip
+    \caption{Reconstructed beam parameters and graphical output (in normalized phase space) from a multi-optics emittance measurement of a production beam.}
+    \label{fig:multi_optics_measurement}
+\end{figure}
+%
+The best-fit ellipses in the $x$-$x'$ and $y$-$y'$ planes are normalized by the reconstructed Twiss parameters.
+The uncertainties in the parameters were calculated by propagating the standard deviations of the ten reconstructed moments obtained from the linear least squares (LLSQ) estimator.\footnote{See Appendix A of \cite{Faus-Golfe2016}.} The reconstructed Twiss parameters are close to the model parameters computed from the linear transfer matrices of the ring and RTBT, showing that the beam is matched to the nominal RTBT optics when it is extracted from the ring.
+The intrinsic emittances are almost equal to the apparent emittances, showing that there is very little cross-plane correlation in the beam.
+This is expected for a production beam.
+
+A comprehensive study of errors in the multi-optics 4D emittance measurement was completed at the SwissFEL Injector Test Facility (SITF) by Prat and Aiba in \cite{Prat2014}.
+They considered errors in the measured moments, quadrupole field and alignment errors, beam energy errors, beam mismatch at the reconstruction point, and dispersion/chromaticity \cite{Mostacci2012}, concluding that the multi-optics measurement remained accurate, reporting $< 5\%$ uncertainty in the intrinsic emittances.
+We initially performed similar studies using envelope tracking to estimate the reconstruction errors in the RTBT, also concluding that the method should remain accurate \cite{Hoover2021-IPAC}.
+Space charge forces, which can render the method invalid for high-perveance beams \cite{Anderson2002}, can be neglected: the space charge tune shift in the ring is around 3\%, and the distance between the reconstruction and measurement locations is much smaller than the length of the ring.
+
+Although the multi-optics method is feasible in the SNS, the fixed-optics method is desired because of its speed, which would allow the measurement of the intrinsic emittances as a function of time during injection and the evaluation of many different machine states within one study period.
+However, the nominal optics in the RTBT are ill-suited for the fixed-optics reconstruction: if only one set of optics from Fig.~\ref{fig:multi_optics_measurement} is used, the resulting covariance matrix is not positive-definite.
+We label this a failed fit.
+A nonlinear solver can be used to ensure a valid covariance matrix \cite{Raimondi1993}, but we found that the answer depended strongly on the initial guess provided to the solver, as well as on which set of optics in the scan was used in the reconstruction.
+
+To investigate the sensitivity of the fixed-optics reconstruction, we generated a covariance matrix with $\varepsilon_1 = \varepsilon_x$ = 32 mm~mrad and $\varepsilon_2 = \varepsilon_y$ = 25 mm~mrad, close to the measured values, and with Twiss parameters matched to the lattice.
+This covariance matrix was tracked to the wire-scanners using the transfer matrices from the fifth step in the scan of Fig.~\ref{fig:multi_optics_measurement}, and the reconstruction was performed many times as 3\% random noise was added to the $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$ moments.
+(The noise level was determined by repeatedly running the wire-scanners without changing the machine state; the profiles are highly reproducible and the maximum discrepancy between any two moments extracted from the profiles was 3\%.
+This corresponds to a fractional error of 1.5\% in the root-mean-square beam size.) This resulted in a large fraction of failed trials, but some successful trials.
+Fig.~\ref{fig:failed_fits} shows the emittances for the successful trials.
+%
+\begin{figure}[b!]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/failed_fits.pdf}
+    \caption{Caption..}
+    \label{fig:failed_fits}
+\end{figure}
+%
+%
+% \begin{figure}[h!]
+%     \centering
+%     \includegraphics[width=\columnwidth]{figures/profiles.pdf}
+%     \caption{Profiles from two consecutive wire-scanner measurements in the SNS.}
+%     \label{fig:profiles}
+% \end{figure}
+%
+Unlike the apparent emittances, the intrinsic emittances are strongly correlated and are not centered on the correct values.
+
+Sensitivity of fixed-optics 4D emittance measurements was observed by Woodley and Emma \cite{Woodley2000} and studied more recently by Agapov, Blair, and Woodley \cite{Agapov2007} as well as Faus-Golfe et al.
+\cite{Faus-Golfe2016}, all in the context of design studies for a future International Linear Collider (ILC).
+The motivation for these studies was to remove the cross-plane correlation in the beam to minimize the vertical emittance $\varepsilon_y$.
+Woodley and Emma proposed to abandon the fixed-optics method due to the bias in the reconstructed intrinsic emittances introduced by large errors in the measured moments, suggesting to instead measure the apparent emittances and iteratively minimize $\varepsilon_y$.
+Agapov, Blair, and Woodley revisited this problem and showed that the linear system used to reconstruct the cross-plane moments can easily become ill-conditioned, and therefore very sensitive to errors in the measured moments, suggesting the use of the coefficient number $C = \Vert \mathbf{A} \Vert \Vert \mathbf{A}^{-1} \Vert$ to characterize the sensitivity.
+Faus-Golfe et al.
+built on this work, studying the problem analytically.
+They suggested that the optics in the planned ILC emittance measurement station, which contains four wire-scanners, could be modified to allow use of the fixed-optics reconstruction.
+
+We performed a similar modification of the RTBT optics.
+Recall that there are only two knobs available in our case: the two power supplies in the wire-scanner region used to control the phase advances at the final wire-scanner.
+To search for a better set of optics, we varied the phase advances at the last wire-scanner ($\mu_x$, $\mu_y$) around their nominal values ($\mu_{x0}$, $\mu_{y0}$) in a $90\degree$ window.
+At each setting, a matched covariance matrix with $\varepsilon_1 = \varepsilon_2 = \varepsilon_x = \varepsilon_y$ was generated and tracked to the wire-scanner locations.
+The reconstruction was again simulated with 3\% random noise added to the ``measured" moments, repeating over a few thousand trials.
+The mean and standard deviation of the emittances were calculated over all successful trials.
+The fractional difference between the mean emittances and the true emittances are plotted for each optics setting in Fig.~\ref{fig:sensitivity_scan}, as well as the fractional standard deviations on the bottom row.
+%
+\begin{figure}[!b]
+    \centering
+    \includegraphics[width=\columnwidth]{figures/sensitivity_scan.pdf}
+    \caption{Scan of the phase advances at WS24.}
+    \label{fig:sensitivity_scan}
+\end{figure}
+
+Settings that produced no successful trials appear as white cells.
+The apparent emittances are not displayed because they remained within 1\% of their true values at every optics setting.
+Modifying the optics so that $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$ reduces the fractional errors to $\approx 7\%$ and the fractional standard deviation to $\approx 5\%$.
+The fraction of failed fits, which is very large along the diagonal in the figure, is reduced to zero.
+
+It is also important to examine the effect of mismatched beam parameters — $\alpha_x$, $\beta_x$, $\alpha_y$, $\beta_y$ — on the accuracy of the reconstruction.
+All previous phase advance calculations have assumed that the beam Twiss parameters are the same as the ring Twiss parameters at extraction.
+As seen in Fig.~\ref{fig:multi_optics_measurement}, this is approximately true for the normal injection scheme in the SNS.
+It is possible, however, for space charge to effectively modify the ring Twiss parameters, resulting in mismatch when entering the RTBT.
+This modification is small for the normal injection scheme, as shown in Fig.~\ref{fig:prod_meas}, but we have generated more significant mismatch in our studies of non-standard injection schemes.
+One example is shown in Table~\ref{tab:mismatch}.
+%
+\begin{table}[!p]
+    \centering
+    \caption{Measured mismatch in the RTBT.}
+    \begin{tabular}{lll}
+    % \midrule
+    \textbf{Parameter} & \textbf{Measured} & \textbf{Model} \\
+    % \midrule
+    $\beta_x$ [m/rad] & 6.26 & 5.49 \\
+    $\beta_y$ [m/rad] & 20.82 & 19.25 \\
+    $\alpha_x$ & -0.89 & -0.78 \\
+    $\alpha_y$ & 1.17 & 1.91 \\
+    % \midrule    
+    \end{tabular}
+    \label{tab:mismatch}
+\end{table}
+%
+
+The beam mismatch is unlikely to exceed these values in our studies.
+To examine the effect of mismatch, we first moved the operating point to $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$, then varied $\beta_x$ and $\beta_y$ within a $\pm 20\%$ window around their model values, $\alpha_x$ within a $\pm 15\%$ window, and $\alpha_y$ within a $-40\%, +10\%$ window to extend beyond the measured discrepancies, and finally repeated the Monte Carlo trials.
+Fig.~\ref{fig:mismatch} plots the fractional error and standard deviation of the reconstructed intrinsic emittances as a function of the sum of the mismatch parameters $M_x$ and $M_y$.\footnote{For ellipse 1 with Twiss parameters \{$\alpha_1$, $\beta_1$, $\gamma_1$\} and ellipse 2 with Twiss parameters \{$\alpha_2$, $\beta_2$, $\gamma_2$\}, the mismatch parameter $M$ is defined as $M = \frac{1}{2}(\beta_1\gamma_2 - 2\alpha_1\alpha_2 + \gamma_1\beta_2)$ \cite{book:Minty2003}.
+$M = 1$ if the ellipses are identical.}
+%
+\begin{figure*}
+    \centering
+    \begin{subfigure}{0.99\columnwidth}
+        \includegraphics[width=\textwidth]{figures/mismatch.pdf}
+        \caption{}
+        \label{fig:mismatch}
+    \end{subfigure}
+    \hspace{0.5cm}
+    \begin{subfigure}{0.99\columnwidth}
+        \includegraphics[width=\textwidth]{figures/mismatch_unequal_emittances.pdf}
+        \caption{}
+        \label{fig:mismatch_unequal_emittances}
+    \end{subfigure}
+    \caption{Simulated fractional error and standard deviation of reconstructed intrinsic emittances as a function of the beam mismatch parameter.
+(a) $\varepsilon_1 / \varepsilon_2 = 1$; (b) $\varepsilon_1 / \varepsilon_2 = 3$.}
+\end{figure*}
+
+The standard deviation remains acceptable, but the error of the mean emittances grows from $\approx 7\%$ to $\approx 12\%$ in some cases.
+With this level of bias in the measurement, it may be difficult to resolve a distribution with weak cross-plane correlations; however, the measurement should still resolve a distribution with strong cross-plane correlations.
+This is demonstrated in Fig.~\ref{fig:mismatch_correlatedbeam}, which repeats the calculations for an input beam with $\varepsilon_1 / \varepsilon_2 = 3$.
+The bias in the reconstruction is now largely absent — the mean reconstructed intrinsic emittances in the Monte Carlo trails are close to their correct values.
+
+We conclude that with small changes to the optics, the fixed-optics method should be sufficient for fast 4D emittance measurements in the SNS.
+Such measurements will be useful to measure the emittance growth during accumulation for qualitative comparison with simulation, as well as to evaluate various machine settings, within a single study period.
 
@@
 
-This is a sentence to fill some space.
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.49\columnwidth}
+        \includegraphics[width=\textwidth]{figures/emittances_exp1a.pdf}
+    \end{subfigure}
+    \begin{subfigure}{0.49\columnwidth}
+        \includegraphics[width=\textwidth]{figures/emittances_exp1b.pdf}
+    \end{subfigure}
+    \caption{Caption.}
+    \label{fig:measured_emittances}
+\end{figure}
 

### 2022-02-23 article.tex
Finish rough draft of body

@@
 \usepackage{amsmath}
+\usepackage{dblfloatfix} % Put figures at bottom of page
 
@@
 Tentative: A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance could mitigate space charge effects in circular accelerators.
-A scheme to approximately create such a distribution is being tested in the Spallation Neutron Source (SNS).
-A critical component of these efforts is to measure the 4D emittance.
+A scheme to approximately create such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source (SNS).
+A critical component of these efforts is to measure the 4D emittance of the beam.
 The 4D emittance can be reconstructed from at least four measurements of the real-space moments with different transfer matrices connecting the reconstruction and measurement locations, accomplished by varying either the machine optics (multi-optics method) or the measurement location (fixed-optics method).
@@
 volume in $x$-$x'$-$y$-$y'$ phase space — could mitigate space charge effects in circular accelerators \cite{Danilov2003, Burov2010, Holmes2018, Hoover2021}.
-A scheme to approximately create such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source \cite{Hoover2021HB, Hoover2021Thesis}.
-A critical component of these efforts is to measure the 4D beam emittance throughout accumulation.
+A scheme to approach such such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source \cite{Hoover2021HB, Hoover2021Thesis}.
+A critical component of these efforts is to measure the 4D beam emittance throughout accumulation, which remains close to zero in the desired case.
 
@@
 \begin{equation}\label{eq:covariance_matrix}
-\begin{aligned}
-    \bm{\Sigma} &= 
+    \bm{\Sigma} = 
     \begin{bmatrix}
@@
     \end{bmatrix}
-    &= 
+    = 
     \begin{bmatrix}
@@
     \end{bmatrix}.
-\end{aligned}
 \end{equation}
@@
 The covariance matrix defines an ellipsoid from $\mathbf{x}^T \bm{\Sigma}^{-1} \mathbf{x} = 1$.
-The 4D emittance $\varepsilon_{4D}$ is proportional to the volume of the this ellipsoid and is conserved in any linear focusing system.
+The 4D emittance $\varepsilon_{4D}$ is proportional to the volume of this ellipsoid and is conserved in any linear focusing system.
 It is defined by
@@
 where $|...|$ is the determinant.
-We have also defined the intrinsic emittances $\varepsilon_{1,2}$, which are individually conserved.
-The intrinsic emittances are found by a symplectic diagonalization of $\bm{\Sigma}$ \cite{Dragtbook}, i.e., they are the imaginary components of the eigenvalues of $\bm{\Sigma}\mathbf{U}$, where $\mathbf{U}$ is the unit symplectic matrix:
+We have also defined the intrinsic emittances $\varepsilon_{1,2}$, which are individually conserved and found by a symplectic diagonalization of $\bm{\Sigma}$ \cite{Dragtbook}, i.e., they are the imaginary components of the eigenvalues of $\bm{\Sigma}\mathbf{U}$ with
 %
@@
 
-The covariance matrix can be reconstructed from measurements of the $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{xy}\rangle$ moments.
-\cite{book:Minty2003}.
-We seek to reconstruct $\bm{\Sigma}$ at position $a$ by measuring $\langle{xx}\rangle$, $\langle{yy}\rangle$ and $\langle{xy}\rangle$ at position $b$, downstream of $a$.
+The covariance matrix at position $a$ along the beamline can be reconstructed by measuring $\langle{xx}\rangle$, $\langle{yy}\rangle$ and $\langle{xy}\rangle$ at position $b$, downstream of $a$.
 Assuming linear transport, the two covariance matrices are related by $\bm{\Sigma}_b = \mathbf{M} \bm{\Sigma}_a \mathbf{M}^T$, where $\mathbf{M}$ is the linear transfer matrix from $a$ to $b$.
-Each measurement gives the following linear system of equations:
+Thus, each measurement produces the following linear system of equations \cite{Wolski2020}:
 %
@@
     \end{bmatrix}_a
-    .
+    ,
 \end{equation}
 %
-The transpose of the coefficient matrix $\mathbf{A}$ is \cite{Wolski2020}
+with
 %
@@
     \end{bmatrix}
+    ,
 \end{equation}
@@
 where $M_{ij}$ is the $i$,$j$ element of $\mathbf{M}$.
-We repeat the measurement at least four times with different transfer matrices — either by varying the optics or varying the measurement location — and solve the system using linear least squares (LLSQ).
+We repeat the measurement at least four times with different transfer matrices and solve the system using linear least squares (LLSQ).
+The transfer matrix can be changed by varying the transfer matrix, which we refer to as the multi-optics method, or by varying the measurement location, which we refer to as the fixed-optics method.
 
@@
 The real space moments of an accumulated beam in the SNS can be estimated using four wire-scanners — labeled WS20, WS21, WS23, and WS24 — in the ring-target beam transport (RTBT) section of the machine.
-The wire-scanner locations, quadrupole locations, and nominal optical functions are shown in Fig.~\ref{fig:rtbt}.
+The wire-scanner locations, quadrupole locations, and nominal optical functions at the end of the RTBT are shown in Fig.~\ref{fig:rtbt}.
 %
@@
 Their step size is 3 mm and their dynamic range is approximately 100.
-They are run at a beam pulse frequency of 1 Hz.\footnote{Each data point corresponds to a separate beam pulse, so the measurement relies on pulse-to-pulse stability.} Each wire-scanner has a horizontal, vertical, and diagonal wire, producing $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$, where the $u$ axis is tilted at angle $\phi = \pi/4$ above the $x$ axis, as well as $\langle{xy}\rangle$ from
+They are run at a beam pulse frequency of 1 Hz.\footnote{Each data point corresponds to a separate beam pulse, so the measurement relies on pulse-to-pulse stability.} Each wire-scanner has three wires to measure the 1D projection of the distribution onto the $x$, $y$ and $u$ axes, where $u$ is tilted at an angle $\phi = \pi / 4$ above the $x$ axis; $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$ can be extracted from these projections, as well as $\langle{xy}\rangle$ from
 %
@@
 In 2D emittance measurements, the phase advance from the reconstruction location to the measurement location is typically varied in a $180\degree$ range.\footnote{The phase advances are calculated under the assumption that the beam Twiss parameters are matched to the lattice Twiss parameters at the reconstruction location.} Prat and Aiba \cite{Prat2014} applied this strategy to the 4D emittance measurement: in the first half of the scan, the horizontal phase advance was varied while the vertical phase advance was held fixed, and in the second half of the scan, the vertical phase advance was varied while the horizontal phase advance was held fixed.
-Since the four SNS wire-scanners are already spaced somewhat evenly in phase advance, maximal phase coverage is possible by varying the phase advances at each wire-scanner in a $30\degree$ window.
-But control of the phase advances between each wire-scanner is limited due to the shared power supplies of the quadrupoles in the wire-scanner region.
-There are two power supplies in the wire-scanner region: one controls {QH18, QH20, QH22, QH24} and one controls {QH19, QH21, QH23, QH25} (the last five quadrupoles are controlled independently — see Fig.~\ref{fig:rtbt}).
+Since the four SNS wire-scanners are already spaced somewhat evenly in phase advance, maximal phase coverage is possible by varying the phase advances at each wire-scanner in a $30\degree$ window; however, control of the phase advances between each wire-scanner is limited due to the shared power supplies of the RTBT quadrupoles.
+There are two power supplies in the wire-scanner region — one controls \{QH18, QH20, QH22, QH24\} and the other controls \{QH19, QH21, QH23, QH25\} — with the last five quadrupoles are controlled independently.
 In addition to these constraints, the $\beta$ functions must be kept small in the wire-scanner region and must remain close to their nominal values at the target.
 
-We chose to vary the phase advances from QH18 (the first varied quadrupole) to WS24 (the last wire-scanner), which also changes the phase advances at WS20, WS21, and WS23 by similar amounts.
-To set the phase advances at WS24 while constraining the beam size in the wire-scanner region, the two power supplies (eight quadrupoles) upstream of WS24 were varied to minimize the following cost function:
+The best we can do is to control the phase advances from the first varied quadrupole (QH18) to the last wire-scanner (WS24), which also modifies the phase advances at the other wire-scanners by similar amounts.
+To control these phase advances the two power supplies (eight quadrupoles) in the wire-scanner region were varied to minimize the following cost function:
 %
@@
 %
-The quadrupole strengths are contained in the vector $\mathbf{g}$.
-The calculated and desired phase advances at WS24 are $\bm{\mu} = (\mu_x, \mu_y)$, and $\tilde{\bm{\mu}} = (\tilde{\mu}_x, \tilde{\mu}_y)$, respectively.
-The maximum calculated and allowed $\beta$ functions in the wire-scanner region are $\bm{\beta}_{max} = (\beta_{x_{max}}, \beta_{y_{max}})$ and $\tilde{\bm{\beta}}_{max} = (\tilde{\beta}_{x_{max}}, \tilde{\beta}_{y_{max}})$, respectively.
-$\Theta$ is the Heaviside step function.
-Finally, $\epsilon$ is a constant.
+The quadrupole strengths are contained in the vector $\mathbf{g}$; the calculated phase advances are $\bm{\mu} = (\mu_x, \mu_y)$; the desired phase advances are $\tilde{\bm{\mu}} = (\tilde{\mu}_x, \tilde{\mu}_y)$; the maximum calculated $\beta$ functions in the wire-scanner region is $\bm{\beta}_{max} = (\beta_{x_{max}}, \beta_{y_{max}})$; the maximum allowed $\beta$ function in the wire-scanner region is $\tilde{\bm{\beta}}_{max} = (\tilde{\beta}_{x_{max}}, \tilde{\beta}_{y_{max}})$; $\Theta$ is the Heaviside step function; $\epsilon$ is a constant.
+After this process is completed, the remaining five quadrupoles before the target are varied to constrain the beam size at the target.
 
-This multi-optics method was tested on a fully accumulated production beam in the SNS using ten total measurements (forty profiles), taking around one hour.
-The result of the reconstruction is shown in Fig.~\ref{fig:multi_optics_measurement}.
+This multi-optics method was tested on a fully accumulated production beam in the SNS using ten total measurements (forty profiles), which was completed in one hour.
+The reconstructed Twiss parameters, emittances, and best-fit ellipses in the $x$-$x'$ and $y$-$y'$ planes (normalized by the reconstructed Twiss parameters) are displayed in Fig.~\ref{fig:multi_optics_measurement}.
 %
@@
 %
-The best-fit ellipses in the $x$-$x'$ and $y$-$y'$ planes are normalized by the reconstructed Twiss parameters.
-The uncertainties in the parameters were calculated by propagating the standard deviations of the ten reconstructed moments obtained from the linear least squares (LLSQ) estimator.\footnote{See Appendix A of \cite{Faus-Golfe2016}.} The reconstructed Twiss parameters are close to the model parameters computed from the linear transfer matrices of the ring and RTBT, showing that the beam is matched to the nominal RTBT optics when it is extracted from the ring.
+The uncertainties in the parameters were calculated by propagating the standard deviations of the ten reconstructed moments obtained from the linear least squares (LLSQ) estimator.\footnote{See Appendix A of \cite{Faus-Golfe2016}.} The reconstructed Twiss parameters are close to the model parameters computed from the linear transfer matrices of the ring and RTBT, showing that the beam is matched to the nominal ring optics when it is extracted from the ring.
 The intrinsic emittances are almost equal to the apparent emittances, showing that there is very little cross-plane correlation in the beam.
@@
 They considered errors in the measured moments, quadrupole field and alignment errors, beam energy errors, beam mismatch at the reconstruction point, and dispersion/chromaticity \cite{Mostacci2012}, concluding that the multi-optics measurement remained accurate, reporting $< 5\%$ uncertainty in the intrinsic emittances.
-We initially performed similar studies using envelope tracking to estimate the reconstruction errors in the RTBT, also concluding that the method should remain accurate \cite{Hoover2021-IPAC}.
-Space charge forces, which can render the method invalid for high-perveance beams \cite{Anderson2002}, can be neglected: the space charge tune shift in the ring is around 3\%, and the distance between the reconstruction and measurement locations is much smaller than the length of the ring.
+We initially performed similar studies using envelope tracking to estimate the reconstruction errors in the RTBT, also concluding that method should remain accurate \cite{Hoover2021-IPAC}: from repeated wire-scanner measurements with the same machine setup, we estimate the error in the measured moments to be only 3\%, and none of the other sources of uncertainty were found to have a large effect on the reconstructed emittances.
+Space charge forces, which can render the method invalid for high-perveance beams \cite{Anderson2002}, can be neglected: the space charge tune shift in the ring is around 3\%, and the distance between the reconstruction and measurement locations is much smaller than the length of the ring ($\approx$ 250 meters).
 
-Although the multi-optics method is feasible in the SNS, the fixed-optics method is desired because of its speed, which would allow the measurement of the intrinsic emittances as a function of time during injection and the evaluation of many different machine states within one study period.
-However, the nominal optics in the RTBT are ill-suited for the fixed-optics reconstruction: if only one set of optics from Fig.~\ref{fig:multi_optics_measurement} is used, the resulting covariance matrix is not positive-definite.
+In summary, the multi-optics emittance measurement is feasible in the SNS and should produce reasonably accurate values of the intrinsic beam emittances.
+The only downside is the slow measurement speed, for the following reasons.
+First, we are not only interested in the beam emittances at a single time, but are also interested in the growth and evolution of the emittances throughout accumulation.
+For example, it could be possible for $\varepsilon_2$ to remain small (as desired) for the first half of accumulation before growing to a much larger value in the second half of accumulation.
+Measurement of this emittance evolution would convey valuable information about the beam dynamics and allow for qualitative comparison with computer simulation.
+Second, it would be beneficial to quickly evaluate various machine states, the best of which will be unknown during initial experiments.
+Finally, a practical point: the time reserved for accelerator physics (AP) studies at the SNS is limited, and setup for initial experiments will be much longer than typical AP studies for reasons not discussed in this paper.
+Thus, the fixed-optics method is preferred in which the reconstruction is performed in one pass, without changing magnet strengths.
+A modest reduction in accuracy for the increase in speed is warranted since weak cross-plane correlations ($\varepsilon_1 \varepsilon_2 \approx \varepsilon_x \varepsilon_y$) are uninteresting for our purposes and do not need to be resolved.
+
+Unfortunately, the nominal optics in the RTBT are ill-suited for the fixed-optics reconstruction: if only one set of optics from Fig.~\ref{fig:multi_optics_measurement} is used, the resulting covariance matrix is not positive-definite.
 We label this a failed fit.
-A nonlinear solver can be used to ensure a valid covariance matrix \cite{Raimondi1993}, but we found that the answer depended strongly on the initial guess provided to the solver, as well as on which set of optics in the scan was used in the reconstruction.
+A nonlinear solver can be used to ensure a valid covariance matrix \cite{Raimondi1993}, but we found that the answer depended strongly on the initial guess provided to the solver and on the selected measurement index.
 
@@
 This covariance matrix was tracked to the wire-scanners using the transfer matrices from the fifth step in the scan of Fig.~\ref{fig:multi_optics_measurement}, and the reconstruction was performed many times as 3\% random noise was added to the $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$ moments.
-(The noise level was determined by repeatedly running the wire-scanners without changing the machine state; the profiles are highly reproducible and the maximum discrepancy between any two moments extracted from the profiles was 3\%.
-This corresponds to a fractional error of 1.5\% in the root-mean-square beam size.) This resulted in a large fraction of failed trials, but some successful trials.
+This resulted in a large fraction of failed trials, but some successful trials.
 Fig.~\ref{fig:failed_fits} shows the emittances for the successful trials.
@@
 Unlike the apparent emittances, the intrinsic emittances are strongly correlated and are not centered on the correct values.
+Our primary concern is to reduce the latter effect, which we refer to as bias.
 
@@
 Woodley and Emma proposed to abandon the fixed-optics method due to the bias in the reconstructed intrinsic emittances introduced by large errors in the measured moments, suggesting to instead measure the apparent emittances and iteratively minimize $\varepsilon_y$.
-Agapov, Blair, and Woodley revisited this problem and showed that the linear system used to reconstruct the cross-plane moments can easily become ill-conditioned, and therefore very sensitive to errors in the measured moments, suggesting the use of the coefficient number $C = \Vert \mathbf{A} \Vert \Vert \mathbf{A}^{-1} \Vert$ to characterize the sensitivity.
+Agapov, Blair, and Woodley revisited this problem and showed that the linear system used to reconstruct the cross-plane moments can easily become ill-conditioned, and hence very sensitive to errors in the measured moments, suggesting the use of the coefficient number $C = \Vert \mathbf{A} \Vert \Vert \mathbf{A}^{-1} \Vert$ to characterize the sensitivity.
 Faus-Golfe et al.
@@
 Recall that there are only two knobs available in our case: the two power supplies in the wire-scanner region used to control the phase advances at the final wire-scanner.
-To search for a better set of optics, we varied the phase advances at the last wire-scanner ($\mu_x$, $\mu_y$) around their nominal values ($\mu_{x0}$, $\mu_{y0}$) in a $90\degree$ window.
+To search for a better set of optics, we varied these phase advances ($\mu_x$, $\mu_y$) in a $90\degree$ window around their nominal values ($\mu_{x0}$, $\mu_{y0}$).
 At each setting, a matched covariance matrix with $\varepsilon_1 = \varepsilon_2 = \varepsilon_x = \varepsilon_y$ was generated and tracked to the wire-scanner locations.
@@
 The apparent emittances are not displayed because they remained within 1\% of their true values at every optics setting.
-Modifying the optics so that $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$ reduces the fractional errors to $\approx 7\%$ and the fractional standard deviation to $\approx 5\%$.
-The fraction of failed fits, which is very large along the diagonal in the figure, is reduced to zero.
+It is clear that modifying the optics so that $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$ — i.e., the lower-right corner of each subplot — reduces the fractional errors to $\approx 7\%$ and the fractional standard deviation to $\approx 5\%$.
+The fraction of failed fits, which is very large along the diagonal in the figure, is reduced to zero at this setting.
 
-It is also important to examine the effect of mismatched beam parameters — $\alpha_x$, $\beta_x$, $\alpha_y$, $\beta_y$ — on the accuracy of the reconstruction.
+It is also important to examine the effect of mismatched beam parameters — $\alpha_x$, $\beta_x$, $\alpha_y$, $\beta_y$ — on the reconstruction accuracy.
 All previous phase advance calculations have assumed that the beam Twiss parameters are the same as the ring Twiss parameters at extraction.
@@
 %
-\begin{table}[!p]
+\begin{table}[!h]
     \centering
-    \caption{Measured mismatch in the RTBT.}
     \begin{tabular}{lll}
@@
     \end{tabular}
+    \caption{Measured mismatch in the RTBT.}
     \label{tab:mismatch}
@@
 With this level of bias in the measurement, it may be difficult to resolve a distribution with weak cross-plane correlations; however, the measurement should still resolve a distribution with strong cross-plane correlations.
-This is demonstrated in Fig.~\ref{fig:mismatch_correlatedbeam}, which repeats the calculations for an input beam with $\varepsilon_1 / \varepsilon_2 = 3$.
-The bias in the reconstruction is now largely absent — the mean reconstructed intrinsic emittances in the Monte Carlo trails are close to their correct values.
-
-We conclude that with small changes to the optics, the fixed-optics method should be sufficient for fast 4D emittance measurements in the SNS.
-Such measurements will be useful to measure the emittance growth during accumulation for qualitative comparison with simulation, as well as to evaluate various machine settings, within a single study period.
+This is demonstrated in Fig.~\ref{fig:mismatch_unequal_emittances}, which repeats the calculations for an input beam with $\varepsilon_1 / \varepsilon_2 = 3$.
+The bias in the reconstruction is now largely absent — the reconstructed intrinsic emittances are clustered around their true values.
+We conclude that with small modifications to the RTBT optics, the fixed-optics method should be sufficient for fast 4D emittance measurements in the SNS.
 
@@
 \label{sec:Example application}
+
+We now demonstrate the usefulness of the fixed-optics emittance measurement in the SNS.
+Again, our goal is to generate a beam with a uniform charge density, elliptical transverse profile, and small 4D emittance.
+This can be accomplished using phase space painting to inject particles along an eigenvector of the ring transfer matrix; if this is accomplished, the particles trace ellipses on a turn-by-turn basis in the $x$-$y$ plane and a uniform density ellipse is maintained throughout injection; hence, the 4D emittance is near zero throughout accumulation.
+This technique, which we refer to as \textit{elliptical painting}, requires variation not only of the distance between circulating and injected beams — as in \textit{correlated painting} — but also of the angle between the beams.
+We represent the distances as $x$ and $y$ and the angles as $x'$ and $y'$.
+In our case, we start with $x = x' = y = y' = 0$, then move along a line in the $x$-$y'$ plane.
+Details are contained in \cite{HooverThesis};
+
+Initial attempts to perform elliptical painting in the SNS have been carried out.
+Due to current hardware constraints, we did not expect the painted beam to approach the ideal case of zero 4D emittance; however, we did expect significant deviations when compared to the standard correlated painting method.
+Fig.~\ref{fig:emittances_exp1a} shows the measured emittances at ten intervals over five-hundred injected turns using the standard correlated painting method.
+As expected, the beam does not develop any significant cross-plane correlations.
+In Fig.~\ref{fig:emittances_exp1b}, the painting proceeded with initial coordinates ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 0.7 mrad).
+The measured intrinsic emittances are significantly different than the measured apparent emittances.
+These plots allow qualitative comparisons with computer simulation and will be useful in future experiments.
 
@@
         \includegraphics[width=\textwidth]{figures/emittances_exp1a.pdf}
+        \label{fig:emittances_exp1a}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{figures/emittances_exp1b.pdf}
+        \label{fig:emittances_exp1a}
     \end{subfigure}
     \caption{Caption.}
-    \label{fig:measured_emittances}
 \end{figure}
@@
 \label{sec:Conclusion}
-
-This is a sentence to fill some space.
 

### 2022-02-23 article.tex
Grammar; change mismatch section; create bibliography

@@
 \usepackage{dblfloatfix} % Put figures at bottom of page
+\usepackage{booktabs} % For tables
 
@@
 Tentative: A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance could mitigate space charge effects in circular accelerators.
-A scheme to approximately create such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source (SNS).
+A scheme to generate such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source (SNS).
 A critical component of these efforts is to measure the 4D emittance of the beam.
@@
 A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance — i.e.
-volume in $x$-$x'$-$y$-$y'$ phase space — could mitigate space charge effects in circular accelerators \cite{Danilov2003, Burov2010, Holmes2018, Hoover2021}.
-A scheme to approach such such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source \cite{Hoover2021HB, Hoover2021Thesis}.
+volume in $x$-$x'$-$y$-$y'$ phase space — could mitigate space charge effects in circular accelerators \cite{Danilov2003, Burov2013, Holmes2018, Hoover2021}.
+A scheme to approach such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source.
 A critical component of these efforts is to measure the 4D beam emittance throughout accumulation, which remains close to zero in the desired case.
@@
 The covariance matrix defines an ellipsoid from $\mathbf{x}^T \bm{\Sigma}^{-1} \mathbf{x} = 1$.
-The 4D emittance $\varepsilon_{4D}$ is proportional to the volume of this ellipsoid and is conserved in any linear focusing system.
+The 4D emittance $\varepsilon_{4D}$ is proportional to the volume of this ellipsoid and is conserved in any linear focusing system \cite{Lebedev2010}.
 It is defined by
@@
 where $|...|$ is the determinant.
-We have also defined the intrinsic emittances $\varepsilon_{1,2}$, which are individually conserved and found by a symplectic diagonalization of $\bm{\Sigma}$ \cite{Dragtbook}, i.e., they are the imaginary components of the eigenvalues of $\bm{\Sigma}\mathbf{U}$ with
+We have also defined the intrinsic emittances $\varepsilon_{1,2}$, which are individually conserved and found by a symplectic diagonalization of $\bm{\Sigma}$ \cite{Dragt2018}, i.e., they are the imaginary components of the eigenvalues of $\bm{\Sigma}\mathbf{U}$ with
 %
@@
 We repeat the measurement at least four times with different transfer matrices and solve the system using linear least squares (LLSQ).
-The transfer matrix can be changed by varying the transfer matrix, which we refer to as the multi-optics method, or by varying the measurement location, which we refer to as the fixed-optics method.
+The transfer matrix elements be modified by varying the optics, which we refer to as the multi-optics method, or by varying the measurement location, which we refer to as the fixed-optics method.
 
@@
     \hspace{1cm}
-    \includegraphics[width=\columnwidth]{figures/rtbt_optics.pdf}
+    \includegraphics[width=1.2\columnwidth]{figures/rtbt_optics.pdf}
     \caption{The wire-scanner region of the ring-target beam transport (RTBT) section of the SNS.}
@@
 Since the four SNS wire-scanners are already spaced somewhat evenly in phase advance, maximal phase coverage is possible by varying the phase advances at each wire-scanner in a $30\degree$ window; however, control of the phase advances between each wire-scanner is limited due to the shared power supplies of the RTBT quadrupoles.
-There are two power supplies in the wire-scanner region — one controls \{QH18, QH20, QH22, QH24\} and the other controls \{QH19, QH21, QH23, QH25\} — with the last five quadrupoles are controlled independently.
+There are two power supplies in the wire-scanner region — one controls \{QH18, QH20, QH22, QH24\} and the other controls \{QH19, QH21, QH23, QH25\} — while the last five quadrupoles are controlled independently.
 In addition to these constraints, the $\beta$ functions must be kept small in the wire-scanner region and must remain close to their nominal values at the target.
@@
 The best we can do is to control the phase advances from the first varied quadrupole (QH18) to the last wire-scanner (WS24), which also modifies the phase advances at the other wire-scanners by similar amounts.
-To control these phase advances the two power supplies (eight quadrupoles) in the wire-scanner region were varied to minimize the following cost function:
+To control these phase advances, the two power supplies (eight quadrupoles) in the wire-scanner region are varied to minimize the following cost function:
 %
@@
 %
-The quadrupole strengths are contained in the vector $\mathbf{g}$; the calculated phase advances are $\bm{\mu} = (\mu_x, \mu_y)$; the desired phase advances are $\tilde{\bm{\mu}} = (\tilde{\mu}_x, \tilde{\mu}_y)$; the maximum calculated $\beta$ functions in the wire-scanner region is $\bm{\beta}_{max} = (\beta_{x_{max}}, \beta_{y_{max}})$; the maximum allowed $\beta$ function in the wire-scanner region is $\tilde{\bm{\beta}}_{max} = (\tilde{\beta}_{x_{max}}, \tilde{\beta}_{y_{max}})$; $\Theta$ is the Heaviside step function; $\epsilon$ is a constant.
+The quadrupole strengths are contained in the vector $\mathbf{g}$; the calculated phase advances are $\bm{\mu} = (\mu_x, \mu_y)$; the desired phase advances are $\tilde{\bm{\mu}} = (\tilde{\mu}_x, \tilde{\mu}_y)$; the maximum calculated $\beta$ functions in the wire-scanner region are $\bm{\beta}_{max} = (\beta_{x_{max}}, \beta_{y_{max}})$; the maximum allowed $\beta$ function in the wire-scanner region are $\tilde{\bm{\beta}}_{max} = (\tilde{\beta}_{x_{max}}, \tilde{\beta}_{y_{max}})$; $\Theta$ is the Heaviside step function; $\epsilon$ is a constant.
 After this process is completed, the remaining five quadrupoles before the target are varied to constrain the beam size at the target.
 
-This multi-optics method was tested on a fully accumulated production beam in the SNS using ten total measurements (forty profiles), which was completed in one hour.
+This multi-optics method was tested on a fully accumulated production beam in the SNS using ten measurements (forty profiles), which were completed in one hour.
 The reconstructed Twiss parameters, emittances, and best-fit ellipses in the $x$-$x'$ and $y$-$y'$ planes (normalized by the reconstructed Twiss parameters) are displayed in Fig.~\ref{fig:multi_optics_measurement}.
@@
 The only downside is the slow measurement speed, for the following reasons.
-First, we are not only interested in the beam emittances at a single time, but are also interested in the growth and evolution of the emittances throughout accumulation.
-For example, it could be possible for $\varepsilon_2$ to remain small (as desired) for the first half of accumulation before growing to a much larger value in the second half of accumulation.
+First, we are not only interested in the beam emittances at a single time but are also interested in the growth and evolution of the emittances throughout accumulation.
+For example, it could be possible for $\varepsilon_2$ to remain small (as desired) in the first half of accumulation before growing to a much larger value in the second half of accumulation.
 Measurement of this emittance evolution would convey valuable information about the beam dynamics and allow for qualitative comparison with computer simulation.
 Second, it would be beneficial to quickly evaluate various machine states, the best of which will be unknown during initial experiments.
-Finally, a practical point: the time reserved for accelerator physics (AP) studies at the SNS is limited, and setup for initial experiments will be much longer than typical AP studies for reasons not discussed in this paper.
+Finally, a practical point: the time reserved for accelerator physics (AP) studies at the SNS is limited, and the setup for initial experiments will be much longer than typical AP studies for reasons not discussed in this paper.
 Thus, the fixed-optics method is preferred in which the reconstruction is performed in one pass, without changing magnet strengths.
@@
 To investigate the sensitivity of the fixed-optics reconstruction, we generated a covariance matrix with $\varepsilon_1 = \varepsilon_x$ = 32 mm~mrad and $\varepsilon_2 = \varepsilon_y$ = 25 mm~mrad, close to the measured values, and with Twiss parameters matched to the lattice.
-This covariance matrix was tracked to the wire-scanners using the transfer matrices from the fifth step in the scan of Fig.~\ref{fig:multi_optics_measurement}, and the reconstruction was performed many times as 3\% random noise was added to the $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$ moments.
-This resulted in a large fraction of failed trials, but some successful trials.
-Fig.~\ref{fig:failed_fits} shows the emittances for the successful trials.
+This covariance matrix was tracked to the wire-scanners using the transfer matrices from the fifth step in the scan of Fig.~\ref{fig:multi_optics_measurement}, and the reconstruction was performed many times with 3\% random noise added to the $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$ moments.
+(We ignore any uncertainty in the transfer matrix elements, which is expected to be small.) This resulted in a large fraction of failed trials, but some successful trials.
+Fig.~\ref{fig:failed_fits} shows the emittances in the successful trials.
 %
-\begin{figure}[b!]
+\begin{figure}[t!]
     \centering
     \includegraphics[width=\columnwidth]{figures/failed_fits.pdf}
-    \caption{Caption..}
+    \caption{Simulated emittance measurement using the nominal optics in the RTBT.}
     \label{fig:failed_fits}
@@
 built on this work, studying the problem analytically.
-They suggested that the optics in the planned ILC emittance measurement station, which contains four wire-scanners, could be modified to allow use of the fixed-optics reconstruction.
+They suggested that the optics in the planned ILC emittance measurement station, which contains four wire-scanners, could be modified to allow the use of the fixed-optics reconstruction.
 
 We performed a similar modification of the RTBT optics.
-Recall that there are only two knobs available in our case: the two power supplies in the wire-scanner region used to control the phase advances at the final wire-scanner.
+Recall that there are only two knobs available: the two power supplies in the wire-scanner region used to control the phase advances at the final wire-scanner.
 To search for a better set of optics, we varied these phase advances ($\mu_x$, $\mu_y$) in a $90\degree$ window around their nominal values ($\mu_{x0}$, $\mu_{y0}$).
-At each setting, a matched covariance matrix with $\varepsilon_1 = \varepsilon_2 = \varepsilon_x = \varepsilon_y$ was generated and tracked to the wire-scanner locations.
+At each setting, a matched covariance matrix with $\varepsilon_1 = \varepsilon_2 = \varepsilon_x = \varepsilon_y$ = 20 mm~mrad was generated and tracked to the wire-scanner locations.
 The reconstruction was again simulated with 3\% random noise added to the ``measured" moments, repeating over a few thousand trials.
 The mean and standard deviation of the emittances were calculated over all successful trials.
-The fractional difference between the mean emittances and the true emittances are plotted for each optics setting in Fig.~\ref{fig:sensitivity_scan}, as well as the fractional standard deviations on the bottom row.
+The difference between the mean emittances and the true emittances, which we refer to as the \textit{bias}, is plotted for each set of optics in Fig.~\ref{fig:sensitivity_scan}, as well as the standard deviations in the bottom row.
 %
-\begin{figure}[!b]
+\begin{figure}[t!]
     \centering
-    \includegraphics[width=\columnwidth]{figures/sensitivity_scan.pdf}
-    \caption{Scan of the phase advances at WS24.}
+    \includegraphics[width=\columnwidth]{figures/sensitivity_scan2.pdf}
+    \caption{Simulated bias and standard deviation of the intrinsic emittances in the RTBT as a function of the phase advances at WS24.}
     \label{fig:sensitivity_scan}
@@
 The apparent emittances are not displayed because they remained within 1\% of their true values at every optics setting.
-It is clear that modifying the optics so that $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$ — i.e., the lower-right corner of each subplot — reduces the fractional errors to $\approx 7\%$ and the fractional standard deviation to $\approx 5\%$.
+Modifying the optics so that $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$ reduces the fractional errors to $\approx 7\%$ and the fractional standard deviation to $\approx 5\%$.
 The fraction of failed fits, which is very large along the diagonal in the figure, is reduced to zero at this setting.
@@
 All previous phase advance calculations have assumed that the beam Twiss parameters are the same as the ring Twiss parameters at extraction.
-As seen in Fig.~\ref{fig:multi_optics_measurement}, this is approximately true for the normal injection scheme in the SNS.
 It is possible, however, for space charge to effectively modify the ring Twiss parameters, resulting in mismatch when entering the RTBT.
-This modification is small for the normal injection scheme, as shown in Fig.~\ref{fig:prod_meas}, but we have generated more significant mismatch in our studies of non-standard injection schemes.
+This modification is small for the normal injection scheme, as shown in Fig.~\ref{fig:multi_optics_measurement}, but we have generated more significant mismatch in our studies of non-standard injection schemes.
 One example is shown in Table~\ref{tab:mismatch}.
@@
     \begin{tabular}{lll}
-    % \midrule
-    \textbf{Parameter} & \textbf{Measured} & \textbf{Model} \\
-    % \midrule
+        \toprule
+        % \textbf{Parameter} & \textbf{Measured} & \textbf{Model} \\
+        Parameter & Measured & Model \\
+        \midrule
         $\beta_x$ [m/rad] & 6.26 & 5.49 \\
@@
         $\alpha_y$ & 1.17 & 1.91 \\
-    % \midrule    
+        \midrule 
     \end{tabular}
@@
 The beam mismatch is unlikely to exceed these values in our studies.
-To examine the effect of mismatch, we first moved the operating point to $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$, then varied $\beta_x$ and $\beta_y$ within a $\pm 20\%$ window around their model values, $\alpha_x$ within a $\pm 15\%$ window, and $\alpha_y$ within a $-40\%, +10\%$ window to extend beyond the measured discrepancies, and finally repeated the Monte Carlo trials.
-Fig.~\ref{fig:mismatch} plots the fractional error and standard deviation of the reconstructed intrinsic emittances as a function of the sum of the mismatch parameters $M_x$ and $M_y$.\footnote{For ellipse 1 with Twiss parameters \{$\alpha_1$, $\beta_1$, $\gamma_1$\} and ellipse 2 with Twiss parameters \{$\alpha_2$, $\beta_2$, $\gamma_2$\}, the mismatch parameter $M$ is defined as $M = \frac{1}{2}(\beta_1\gamma_2 - 2\alpha_1\alpha_2 + \gamma_1\beta_2)$ \cite{book:Minty2003}.
-$M = 1$ if the ellipses are identical.}
+To examine the effect of mismatch, we first moved the operating point to $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$, then varied $\beta_x$ and $\beta_y$ within a $\pm 20\%$ window around their model values, $\alpha_x$ within a $\pm 15\%$ window, and $\alpha_y$ within a $-40\%, +10\%$ window to extend beyond the measured discrepancies, and repeated the Monte Carlo trials for each initial beam, thus producing a collection of means and standard deviations for the intrinsic emittances.
+The left plot in Fig.~\ref{fig:mismatch} displays the standard deviations and biases for $\varepsilon_1$ (red) and $\varepsilon_2$ (blue).
+%
+% \begin{figure*}
+%     \centering
+%     \begin{subfigure}{0.99\columnwidth}
+%         \includegraphics[width=\textwidth]{figures/mismatch.pdf}
+%         \caption{}
+%         \label{fig:mismatch}
+%     \end{subfigure}
+%     \hspace{0.5cm}
+%     \begin{subfigure}{0.99\columnwidth}
+%         \includegraphics[width=\textwidth]{figures/mismatch_unequal_emittances.pdf}
+%         \caption{}
+%         \label{fig:mismatch_unequal_emittances}
+%     \end{subfigure}
+%     \caption{Simulated fractional error and standard deviation of reconstructed intrinsic emittances as a function of the beam mismatch parameter.
+(a) $\varepsilon_1 / \varepsilon_2 = 1$; (b) $\varepsilon_1 / \varepsilon_2 = 3$.}
+% \end{figure*}
 %
@@
     \centering
-    \begin{subfigure}{0.99\columnwidth}
-        \includegraphics[width=\textwidth]{figures/mismatch.pdf}
-        \caption{}
+    \includegraphics[width=\textwidth]{figures/mismatch2.pdf}
+    \caption{Bias and standard deviation of $\varepsilon_1$ (red) and $\varepsilon_2$ (blue) from simulated reconstructions in the RTBT.
+In each plot, the collection of points is generated by varying the initial beam Twiss parameters.
+The true values of the emittances are printed on the top of the figures.}
     \label{fig:mismatch}
-    \end{subfigure}
-    \hspace{0.5cm}
-    \begin{subfigure}{0.99\columnwidth}
-        \includegraphics[width=\textwidth]{figures/mismatch_unequal_emittances.pdf}
-        \caption{}
-        \label{fig:mismatch_unequal_emittances}
-    \end{subfigure}
-    \caption{Simulated fractional error and standard deviation of reconstructed intrinsic emittances as a function of the beam mismatch parameter.
-(a) $\varepsilon_1 / \varepsilon_2 = 1$; (b) $\varepsilon_1 / \varepsilon_2 = 3$.}
 \end{figure*}
+%
 
-The standard deviation remains acceptable, but the error of the mean emittances grows from $\approx 7\%$ to $\approx 12\%$ in some cases.
-With this level of bias in the measurement, it may be difficult to resolve a distribution with weak cross-plane correlations; however, the measurement should still resolve a distribution with strong cross-plane correlations.
-This is demonstrated in Fig.~\ref{fig:mismatch_unequal_emittances}, which repeats the calculations for an input beam with $\varepsilon_1 / \varepsilon_2 = 3$.
-The bias in the reconstruction is now largely absent — the reconstructed intrinsic emittances are clustered around their true values.
+Although most of the points are clustered near the original bias and standard deviation of 7\% and 5\%, respectively, the bias increases to nearly 15\% in some cases, which may make it difficult to resolve weak cross-plane correlations; however, the measurement should still resolve strong cross-plane correlations.
+This is demonstrated in the rest of the plots in Fig.~\ref{fig:mismatch}, in which the entire process is repeated with $\varepsilon_1 / \varepsilon_2 > 1$.
+The bias in the reconstruction quickly decreases — the emittances are clustered around their true values.
 We conclude that with small modifications to the RTBT optics, the fixed-optics method should be sufficient for fast 4D emittance measurements in the SNS.
@@
 We now demonstrate the usefulness of the fixed-optics emittance measurement in the SNS.
-Again, our goal is to generate a beam with a uniform charge density, elliptical transverse profile, and small 4D emittance.
-This can be accomplished using phase space painting to inject particles along an eigenvector of the ring transfer matrix; if this is accomplished, the particles trace ellipses on a turn-by-turn basis in the $x$-$y$ plane and a uniform density ellipse is maintained throughout injection; hence, the 4D emittance is near zero throughout accumulation.
+Again, our ultimate goal is to generate a beam with a uniform charge density, elliptical transverse profile, and small 4D emittance.
+This can be accomplished using charge-exchange injection and phase space painting.
+The working principle is to inject particles along an eigenvector of the one-turn transfer matrix; if this is accomplished, the particles trace ellipses on a turn-by-turn basis in the $x$-$y$ plane, and a uniform density ellipse is maintained throughout accumulation; hence, the 4D emittance remains near zero throughout accumulation.
 This technique, which we refer to as \textit{elliptical painting}, requires variation not only of the distance between circulating and injected beams — as in \textit{correlated painting} — but also of the angle between the beams.
 We represent the distances as $x$ and $y$ and the angles as $x'$ and $y'$.
-In our case, we start with $x = x' = y = y' = 0$, then move along a line in the $x$-$y'$ plane.
-Details are contained in \cite{HooverThesis};
+Details are contained in \cite{HooverThesis}.
 
@@
 Due to current hardware constraints, we did not expect the painted beam to approach the ideal case of zero 4D emittance; however, we did expect significant deviations when compared to the standard correlated painting method.
-Fig.~\ref{fig:emittances_exp1a} shows the measured emittances at ten intervals over five-hundred injected turns using the standard correlated painting method.
+Fig.~\ref{fig:emittances_exp1a} shows the measured emittances at ten intervals over five hundred injected turns using the standard correlated painting method.
 As expected, the beam does not develop any significant cross-plane correlations.
-In Fig.~\ref{fig:emittances_exp1b}, the painting proceeded with initial coordinates ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 0.7 mrad).
+In Fig.~\ref{fig:emittances_exp1b}, painting was performed with initial coordinates ($x$, $x'$, $y$, $y'$) $\approx$ (10 mm, 0 mrad, 0 mm, 0 mrad) and final coordinates ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 0.7 mrad).
 The measured intrinsic emittances are significantly different than the measured apparent emittances.
-These plots allow qualitative comparisons with computer simulation and will be useful in future experiments.
+This data set, which was collected in less than two hours, allowed qualitative comparisons with computer simulation, which was used to guide future experiments.
 
@@
         \includegraphics[width=\textwidth]{figures/emittances_exp1a.pdf}
+        \caption{}
         \label{fig:emittances_exp1a}
@@
         \includegraphics[width=\textwidth]{figures/emittances_exp1b.pdf}
-        \label{fig:emittances_exp1a}
+        \caption{}
+        \label{fig:emittances_exp1b}
     \end{subfigure}
-    \caption{Caption.}
+    \caption{Measured emittances vs. number of injected turns in the SNS ring. (a) correlated (production) painting scheme; (b) non-standard painting scheme. [To do: larger axis labels.]}
 \end{figure}

### 2022-02-27 article.tex
Updates from Overleaf

@@
 \affiliation[author1]{organization={The University of Tennessee},%Department and Organization
-            addressline={}, 
             city={Knoxville},
@@
 \begin{abstract}
-Tentative: A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance could mitigate space charge effects in circular accelerators.
-A scheme to generate such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source (SNS).
+A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance could mitigate space charge effects in circular accelerators.
+A scheme to approach such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source (SNS).
 A critical component of these efforts is to measure the 4D emittance of the beam.
@@
 
-A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance — i.e.
-volume in $x$-$x'$-$y$-$y'$ phase space — could mitigate space charge effects in circular accelerators \cite{Danilov2003, Burov2013, Holmes2018, Hoover2021}.
-A scheme to approach such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source.
-A critical component of these efforts is to measure the 4D beam emittance throughout accumulation, which remains close to zero in the desired case.
+A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance could mitigate space charge effects in circular accelerators \cite{Danilov2003, Burov2002, Burov2013}.
+A scheme to generate such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source (SNS) accumulator ring \cite{Holmes2018, Hoover2021}.
+A critical component of these efforts is to measure the 4D beam emittance.
 
-[\dots...]
+The available diagnostics in the SNS ring-target beam transport line (RTBT) are four wire-scanners that measure 1D projections of the distribution onto a horizontal, vertical, and diagonal axis in the transverse plane.
+The covariance matrix, and hence the root-mean-square emittances, can be reconstructed from at least four wire-scanner measurements with different transfer matrices connecting the measurement and reconstruction locations \cite{book:Minty2003}.\footnote{Reconstruction of the transverse phase space distribution is possible using 2D projections of the distribution on a screen \cite{Hock2013, Wang2019, Wolski2020}.
+This may be possible using the SNS target imaging system \cite{Blokland2010} but is not pursued here.} The transfer matrix elements can be controlled by varying the machine optics (multi-optics method), the measurement location (fixed-optics method), or any combination of the two \cite{Prat2014}.
+The fixed-optics method is possible and preferred in our case due to its speed; however, previous studies have shown that the method can be sensitive to errors \cite{Raimondi1993, Woodley2000, Agapov2007, Faus-Golfe2016}.
+
+The purpose of this work is to determine whether the multi-optics and/or fixed-optics methods are feasible in the SNS.
+The reconstruction method is reviewed in Section \ref{sec:Four-dimensional emittance measurement}; the implementation of the method in the SNS is discussed in Section \ref{sec:Implementation in the SNS}; the method is applied to measure the 4D emittance of an SNS beam throughout accumulation in Section \ref{sec:Example application}.
 
 \section{Four-dimensional emittance measurement}
+\label{sec:Four-dimensional emittance measurement}
 
-It is often sufficient to characterize a phase space distribution by its covariance matrix $\bm{\Sigma} = \langle{\mathbf{x}\mathbf{x}^T}\rangle$, where $\mathbf{x}$ is the phase space coordinate vector and $\langle{\dots}\rangle$ represents the average over the distribution.
-In the transverse plane:
+Let $\mathbf{x} = (x, x', y, y')^T$ be the transverse phase space coordinate vector.
+The covariance matrix $\mathbf{\Sigma}$ is defined by $\mathbf{\Sigma} = \langle{\mathbf{x}\mathbf{x}^T}\rangle$, where $\langle{\dots}\rangle$ represents the average over the distribution; i.e.,
 %
@@
 The covariance matrix defines an ellipsoid from $\mathbf{x}^T \bm{\Sigma}^{-1} \mathbf{x} = 1$.
-The 4D emittance $\varepsilon_{4D}$ is proportional to the volume of this ellipsoid and is conserved in any linear focusing system \cite{Lebedev2010}.
-It is defined by
+The 4D emittance $\varepsilon_{4D}$ is proportional to the volume of this ellipsoid and is conserved in any linear focusing system \cite{Lebedev2010}; it is defined by
 %
@@
 where $|...|$ is the determinant.
-We have also defined the intrinsic emittances $\varepsilon_{1,2}$, which are individually conserved and found by a symplectic diagonalization of $\bm{\Sigma}$ \cite{Dragt2018}, i.e., they are the imaginary components of the eigenvalues of $\bm{\Sigma}\mathbf{U}$ with
+We have also defined the intrinsic emittances $\varepsilon_{1,2}$, which are individually conserved and found by a symplectic diagonalization of $\bm{\Sigma}$ \cite{Dragt2018}; i.e., they are the imaginary components of the eigenvalues of $\bm{\Sigma}\mathbf{U}$ with
 %
@@
 
-The covariance matrix at position $a$ along the beamline can be reconstructed by measuring $\langle{xx}\rangle$, $\langle{yy}\rangle$ and $\langle{xy}\rangle$ at position $b$, downstream of $a$.
+The covariance matrix at position $a$ along the beamline can be reconstructed by measuring $\langle{xx}\rangle$, $\langle{yy}\rangle$ and $\langle{xy}\rangle$ at position $b$, downstream of $a$ \cite{book:Minty2003}.
 Assuming linear transport, the two covariance matrices are related by $\bm{\Sigma}_b = \mathbf{M} \bm{\Sigma}_a \mathbf{M}^T$, where $\mathbf{M}$ is the linear transfer matrix from $a$ to $b$.
-Thus, each measurement produces the following linear system of equations \cite{Wolski2020}:
+Thus, each measurement produces a linear system of equations:
 %
@@
 %
-with
+where $\mathbf{A}$ is a function of $\mathbf{M}$.
+We repeat the measurement at least four times with different transfer matrices and solve the system using linear least squares (LLSQ).
+The transfer matrix elements can be modified by varying the optics, which we refer to as the multi-optics method, or by varying the measurement location, which we refer to as the fixed-optics method.
+
+\section{Implementation in the SNS}
+\label{sec:Implementation in the SNS}
+
+The real space moments of an accumulated beam in the SNS can be meausred using four wire-scanners — labeled WS20, WS21, WS23, and WS24 — in the ring-target beam transport (RTBT) section of the machine \cite{Henderson2014}.
+The wire-scanners are run in parallel and take approximately five minutes to move across the beam and return to their original positions.
+Their step size is 3 mm and their dynamic range is approximately $10^2$.
+They are run at a beam pulse frequency of 1 Hz.\footnote{Each data point corresponds to a separate beam pulse, so the measurement relies on pulse-to-pulse stability.} Each wire-scanner has three wires to measure the 1D projection of the distribution onto the $x$, $y$ and $u$ axes, where $u$ is tilted at an angle $\phi = \pi / 4$ above the $x$ axis; $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$ can be extracted from these projections, as well as $\langle{xy}\rangle$ from
 %
 \begin{equation}
-    \mathbf{A}^T = 
-    \begin{bmatrix}
-        M_{11}M_{11} & M_{11}M_{31} & M_{31}M_{31} \\
-        2M_{11}M_{12} & M_{12}M_{31} + M_{11}M_{32} & 2M_{31}M_{32} \\
-        2M_{11}M_{13} & M_{13}M_{31} + M_{11}M_{33} & 2M_{31}M_{33} \\
-        2M_{11}M_{14} & M_{14}M_{31} + M_{11}M_{34} & 2M_{31}M_{34} \\
-        M_{12}M_{12} & M_{12}M_{32} & M_{32}M_{32} \\
-        2M_{12}M_{13} & M_{13}M_{32} + M_{12}M_{33} & 2M_{32}M_{33} \\
-        2M_{12}M_{14} & M_{14}M_{32} + M_{12}M_{34} & 2M_{32}M_{34} \\
-        M_{13}M_{13} & M_{13}M_{33} & M_{33}M_{33} \\
-        2M_{13}M_{14} & M_{14}M_{33} + M_{13}M_{34} & 2M_{33}M_{34} \\
-        M_{14}M_{14} & M_{14}M_{34} & M_{34}M_{34}
-    \end{bmatrix}
-    ,
+    \langle{xy}\rangle = \frac{\langle{uu}\rangle - \langle{xx}\rangle \cos^2\phi - \langle{yy}\rangle \sin^2\phi}{2\sin\phi\cos\phi}
+    .
 \end{equation}
 %
-where $M_{ij}$ is the $i$,$j$ element of $\mathbf{M}$.
-We repeat the measurement at least four times with different transfer matrices and solve the system using linear least squares (LLSQ).
-The transfer matrix elements be modified by varying the optics, which we refer to as the multi-optics method, or by varying the measurement location, which we refer to as the fixed-optics method.
-
-\section{Implementation in the SNS}
-
-The real space moments of an accumulated beam in the SNS can be estimated using four wire-scanners — labeled WS20, WS21, WS23, and WS24 — in the ring-target beam transport (RTBT) section of the machine.
 The wire-scanner locations, quadrupole locations, and nominal optical functions at the end of the RTBT are shown in Fig.~\ref{fig:rtbt}.
 %
-\begin{figure*}[!t]
+\begin{figure*}[]
     \centering
@@
 
-The wire-scanners are run in parallel and take approximately five minutes to move across the beam and return to their original positions.
-Their step size is 3 mm and their dynamic range is approximately 100.
-They are run at a beam pulse frequency of 1 Hz.\footnote{Each data point corresponds to a separate beam pulse, so the measurement relies on pulse-to-pulse stability.} Each wire-scanner has three wires to measure the 1D projection of the distribution onto the $x$, $y$ and $u$ axes, where $u$ is tilted at an angle $\phi = \pi / 4$ above the $x$ axis; $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$ can be extracted from these projections, as well as $\langle{xy}\rangle$ from
-%
-\begin{equation}
-    \langle{xy}\rangle = \frac{\langle{uu}\rangle - \langle{xx}\rangle \cos^2\phi - \langle{yy}\rangle \sin^2\phi}{2\sin\phi\cos\phi}
-    .
-\end{equation}
-%
-
 We first implemented a variant of the multi-optics method.
-In 2D emittance measurements, the phase advance from the reconstruction location to the measurement location is typically varied in a $180\degree$ range.\footnote{The phase advances are calculated under the assumption that the beam Twiss parameters are matched to the lattice Twiss parameters at the reconstruction location.} Prat and Aiba \cite{Prat2014} applied this strategy to the 4D emittance measurement: in the first half of the scan, the horizontal phase advance was varied while the vertical phase advance was held fixed, and in the second half of the scan, the vertical phase advance was varied while the horizontal phase advance was held fixed.
+There is considerable freedom in the choice of optics since two degrees of freedom are present.
+In 2D emittance measurements, the phase advance from the reconstruction location to the measurement location is typically varied uniformly within a $180\degree$ range.\footnote{Intuitively, the error is expected to be minimized when the projection angles are spread uniformly between 0 and $\pi$; however, the projection angles are only equal to the phase advances in normalized phase space \cite{Hock2011}.
+Nonetheless, it is often convenient to vary the phase advances instead of the projection angles.} Prat and Aiba \cite{Prat2014} applied this strategy to the 4D emittance measurement: in the first half of the scan, the horizontal phase advance was varied while the vertical phase advance was held fixed, and in the second half of the scan, the vertical phase advance was varied while the horizontal phase advance was held fixed.
 Since the four SNS wire-scanners are already spaced somewhat evenly in phase advance, maximal phase coverage is possible by varying the phase advances at each wire-scanner in a $30\degree$ window; however, control of the phase advances between each wire-scanner is limited due to the shared power supplies of the RTBT quadrupoles.
@@
 %
-The quadrupole strengths are contained in the vector $\mathbf{g}$; the calculated phase advances are $\bm{\mu} = (\mu_x, \mu_y)$; the desired phase advances are $\tilde{\bm{\mu}} = (\tilde{\mu}_x, \tilde{\mu}_y)$; the maximum calculated $\beta$ functions in the wire-scanner region are $\bm{\beta}_{max} = (\beta_{x_{max}}, \beta_{y_{max}})$; the maximum allowed $\beta$ function in the wire-scanner region are $\tilde{\bm{\beta}}_{max} = (\tilde{\beta}_{x_{max}}, \tilde{\beta}_{y_{max}})$; $\Theta$ is the Heaviside step function; $\epsilon$ is a constant.
+The quadrupole strengths are contained in the vector $\mathbf{g}$; the calculated phase advances are $\bm{\mu} = (\mu_x, \mu_y)$; the desired phase advances are $\tilde{\bm{\mu}} = (\tilde{\mu}_x, \tilde{\mu}_y)$; the maximum calculated $\beta$ functions in the wire-scanner region are $\bm{\beta}_{max} = (\beta_{x_{max}}, \beta_{y_{max}})$; the maximum allowed $\beta$ functions in the wire-scanner region are $\tilde{\bm{\beta}}_{max} = (\tilde{\beta}_{x_{max}}, \tilde{\beta}_{y_{max}})$; $\Theta$ is the Heaviside step function; $\epsilon$ is a constant.
 After this process is completed, the remaining five quadrupoles before the target are varied to constrain the beam size at the target.
@@
 %
-\begin{figure}[!b]
+\begin{figure}[b!]
     \centering
@@
 %
-The uncertainties in the parameters were calculated by propagating the standard deviations of the ten reconstructed moments obtained from the linear least squares (LLSQ) estimator.\footnote{See Appendix A of \cite{Faus-Golfe2016}.} The reconstructed Twiss parameters are close to the model parameters computed from the linear transfer matrices of the ring and RTBT, showing that the beam is matched to the nominal ring optics when it is extracted from the ring.
-The intrinsic emittances are almost equal to the apparent emittances, showing that there is very little cross-plane correlation in the beam.
+The uncertainties in the parameters were calculated by propagating the standard deviations of the ten reconstructed moments obtained from the linear least squares (LLSQ) estimator.\footnote{See Appendix A of \cite{Faus-Golfe2016}.} The reconstructed Twiss parameters are close to the model parameters computed from the linear transfer matrices of the ring and RTBT, showing that the beam was matched to the nominal ring optics when it was extracted from the ring.
+The intrinsic emittances are almost equal to the apparent emittances, showing that there was very little cross-plane correlation in the beam.
 This is expected for a production beam.
@@
 A comprehensive study of errors in the multi-optics 4D emittance measurement was completed at the SwissFEL Injector Test Facility (SITF) by Prat and Aiba in \cite{Prat2014}.
-They considered errors in the measured moments, quadrupole field and alignment errors, beam energy errors, beam mismatch at the reconstruction point, and dispersion/chromaticity \cite{Mostacci2012}, concluding that the multi-optics measurement remained accurate, reporting $< 5\%$ uncertainty in the intrinsic emittances.
-We initially performed similar studies using envelope tracking to estimate the reconstruction errors in the RTBT, also concluding that method should remain accurate \cite{Hoover2021-IPAC}: from repeated wire-scanner measurements with the same machine setup, we estimate the error in the measured moments to be only 3\%, and none of the other sources of uncertainty were found to have a large effect on the reconstructed emittances.
-Space charge forces, which can render the method invalid for high-perveance beams \cite{Anderson2002}, can be neglected: the space charge tune shift in the ring is around 3\%, and the distance between the reconstruction and measurement locations is much smaller than the length of the ring ($\approx$ 250 meters).
+They considered errors in the measured moments, quadrupole field and alignment errors, beam energy errors, beam mismatch at the reconstruction point, and dispersion/chromaticity \cite{Mostacci2012}, concluding that the method remained accurate and reporting $< 5\%$ uncertainty in the intrinsic emittances.
+We initially performed similar studies using envelope tracking to estimate the reconstruction errors in the RTBT, also concluding that method should remain accurate \cite{Hoover2021-IPAC}.
+From repeated wire-scanner measurements with the same machine setup, we estimate the error in the measured moments to be only 3\%, and none of the other sources of uncertainty were found to have a large effect on the reconstructed emittances.
+Space charge forces, which can render the method invalid for high-perveance beams \cite{Anderson2002}, can be neglected since the space charge tune shift in the ring is around 3\% and the distance between the reconstruction and measurement locations is much smaller than the ring length ($\approx$ 250 meters).
 
-In summary, the multi-optics emittance measurement is feasible in the SNS and should produce reasonably accurate values of the intrinsic beam emittances.
-The only downside is the slow measurement speed, for the following reasons.
+In summary, the multi-optics emittance measurement is feasible in the SNS.
+The only downside is the long measurement time, for the following reasons.
 First, we are not only interested in the beam emittances at a single time but are also interested in the growth and evolution of the emittances throughout accumulation.
@@
 Second, it would be beneficial to quickly evaluate various machine states, the best of which will be unknown during initial experiments.
-Finally, a practical point: the time reserved for accelerator physics (AP) studies at the SNS is limited, and the setup for initial experiments will be much longer than typical AP studies for reasons not discussed in this paper.
-Thus, the fixed-optics method is preferred in which the reconstruction is performed in one pass, without changing magnet strengths.
+Finally, a practical point: the time reserved for accelerator physics (AP) experiments at the SNS is limited, and the setup for initial experiments will be much longer than typical AP experiments for reasons not discussed in this paper.
+Thus, the fixed-optics method is preferred.
 A modest reduction in accuracy for the increase in speed is warranted since weak cross-plane correlations ($\varepsilon_1 \varepsilon_2 \approx \varepsilon_x \varepsilon_y$) are uninteresting for our purposes and do not need to be resolved.
@@
 We label this a failed fit.
-A nonlinear solver can be used to ensure a valid covariance matrix \cite{Raimondi1993}, but we found that the answer depended strongly on the initial guess provided to the solver and on the selected measurement index.
+A nonlinear solver \cite{Raimondi1993} or Cholesky decomposition \cite{Agapov2007} can be used to ensure a valid covariance matrix, but we found that the answer depended strongly on the initial guess provided to the solver and on which measurement in the scan was used in the reconstruction.
 
-To investigate the sensitivity of the fixed-optics reconstruction, we generated a covariance matrix with $\varepsilon_1 = \varepsilon_x$ = 32 mm~mrad and $\varepsilon_2 = \varepsilon_y$ = 25 mm~mrad, close to the measured values, and with Twiss parameters matched to the lattice.
+To investigate the sensitivity of the fixed-optics method, we generated a covariance matrix with $\varepsilon_1 = \varepsilon_x$ = 32 mm~mrad and $\varepsilon_2 = \varepsilon_y$ = 25 mm~mrad, close to the measured values, and with Twiss parameters matched to the lattice.
 This covariance matrix was tracked to the wire-scanners using the transfer matrices from the fifth step in the scan of Fig.~\ref{fig:multi_optics_measurement}, and the reconstruction was performed many times with 3\% random noise added to the $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$ moments.
-(We ignore any uncertainty in the transfer matrix elements, which is expected to be small.) This resulted in a large fraction of failed trials, but some successful trials.
+(We ignored any uncertainty in the transfer matrix elements, which were expected to be small.) This resulted in a large fraction of failed trials, but some successful trials.
 Fig.~\ref{fig:failed_fits} shows the emittances in the successful trials.
 %
-\begin{figure}[t!]
+\begin{figure}[]
     \centering
@@
 The motivation for these studies was to remove the cross-plane correlation in the beam to minimize the vertical emittance $\varepsilon_y$.
-Woodley and Emma proposed to abandon the fixed-optics method due to the bias in the reconstructed intrinsic emittances introduced by large errors in the measured moments, suggesting to instead measure the apparent emittances and iteratively minimize $\varepsilon_y$.
-Agapov, Blair, and Woodley revisited this problem and showed that the linear system used to reconstruct the cross-plane moments can easily become ill-conditioned, and hence very sensitive to errors in the measured moments, suggesting the use of the coefficient number $C = \Vert \mathbf{A} \Vert \Vert \mathbf{A}^{-1} \Vert$ to characterize the sensitivity.
+Woodley and Emma proposed to abandon the fixed-optics method due to the bias in the intrinsic emittances introduced by large errors in the measured moments, suggesting to instead measure the apparent emittances and iteratively minimize $\varepsilon_y$.
+Agapov, Blair, and Woodley revisited this problem and showed that the linear system used to reconstruct the cross-plane moments can easily become ill-conditioned, and hence very sensitive to errors in the measured moments, suggesting the use of the condition number $C = |\mathbf{A}| |\mathbf{A}^{-1} |$ to characterize the sensitivity, where $| \dots |$ is a matrix norm \cite{Golub1985}.
 Faus-Golfe et al.
 built on this work, studying the problem analytically.
-They suggested that the optics in the planned ILC emittance measurement station, which contains four wire-scanners, could be modified to allow the use of the fixed-optics reconstruction.
+They suggested that the optics in the planned ILC emittance measurement station, which contained four wire-scanners, could be modified to allow the use of the fixed-optics reconstruction.
 
-We performed a similar modification of the RTBT optics.
-Recall that there are only two knobs available: the two power supplies in the wire-scanner region used to control the phase advances at the final wire-scanner.
+We performed a similar modification of the RTBT optics, using these previous studies as a guide.
+Recall that we have two knobs: the two power supplies in the wire-scanner region used to control the phase advances at the final wire-scanner.
 To search for a better set of optics, we varied these phase advances ($\mu_x$, $\mu_y$) in a $90\degree$ window around their nominal values ($\mu_{x0}$, $\mu_{y0}$).
@@
 The reconstruction was again simulated with 3\% random noise added to the ``measured" moments, repeating over a few thousand trials.
-The mean and standard deviation of the emittances were calculated over all successful trials.
-The difference between the mean emittances and the true emittances, which we refer to as the \textit{bias}, is plotted for each set of optics in Fig.~\ref{fig:sensitivity_scan}, as well as the standard deviations in the bottom row.
+The mean and standard deviation of the emittances were calculated over the successful trials.
+The difference between the mean emittances and the true emittances, which we refer to as the \textit{bias}, is plotted for each set of optics in the top row of Fig.~\ref{fig:sensitivity_scan}, as well as the standard deviations in the bottom row.
 %
-\begin{figure}[t!]
+\begin{figure}[]
     \centering
@@
 \end{figure}
-
+%
+%
+\begin{figure*}[]
+    \centering
+    \includegraphics[width=\textwidth]{figures/mismatch2.pdf}
+    \caption{Bias and standard deviation of $\varepsilon_1$ (pink) and $\varepsilon_2$ (blue) from simulated reconstructions in the RTBT.
+In each plot, the collection of points is generated by varying the initial beam Twiss parameters.
+The true values of the emittances are printed on the top of the figures.}
+    \label{fig:mismatch}
+\end{figure*}
+%
 Settings that produced no successful trials appear as white cells.
 The apparent emittances are not displayed because they remained within 1\% of their true values at every optics setting.
-Modifying the optics so that $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$ reduces the fractional errors to $\approx 7\%$ and the fractional standard deviation to $\approx 5\%$.
+Modifying the optics so that $\mu_x - \mu_{x0} = 45\degree$ and $\mu_y - \mu_{y0} = -45\degree$ reduces the bias to $\approx 7\%$ and the standard deviation to $\approx 5\%$.
 The fraction of failed fits, which is very large along the diagonal in the figure, is reduced to zero at this setting.
 
-It is also important to examine the effect of mismatched beam parameters — $\alpha_x$, $\beta_x$, $\alpha_y$, $\beta_y$ — on the reconstruction accuracy.
+It is also important to examine the effect of mismatched beam parameters — $\alpha_x$, $\beta_x$, $\alpha_y$, $\beta_y$ — on the accuracy of the reconstructed intrinsic emittances, just as was done for the apparent emittances in \cite{Prat2014}.
 All previous phase advance calculations have assumed that the beam Twiss parameters are the same as the ring Twiss parameters at extraction.
@@
 %
-\begin{table}[!h]
+\begin{table}[!b]
     \centering
@@
         \midrule
-        $\beta_x$ [m/rad] & 6.26 & 5.49 \\
-        $\beta_y$ [m/rad] & 20.82 & 19.25 \\
+        $\beta_x$ [m] & 6.26 & 5.49 \\
+        $\beta_y$ [m] & 20.82 & 19.25 \\
         $\alpha_x$ & -0.89 & -0.78 \\
@@
 The beam mismatch is unlikely to exceed these values in our studies.
-To examine the effect of mismatch, we first moved the operating point to $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$, then varied $\beta_x$ and $\beta_y$ within a $\pm 20\%$ window around their model values, $\alpha_x$ within a $\pm 15\%$ window, and $\alpha_y$ within a $-40\%, +10\%$ window to extend beyond the measured discrepancies, and repeated the Monte Carlo trials for each initial beam, thus producing a collection of means and standard deviations for the intrinsic emittances.
-The left plot in Fig.~\ref{fig:mismatch} displays the standard deviations and biases for $\varepsilon_1$ (red) and $\varepsilon_2$ (blue).
+To examine the effect of mismatch, we first moved the operating point to $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$, then varied $\beta_x$ and $\beta_y$ within a $\pm 20\%$ window around their model values, $\alpha_x$ within a $\pm 15\%$ window, and $\alpha_y$ within a $-40\%, +10\%$ window to extend beyond the measured discrepancies, and repeated the Monte Carlo trials for each initial beam, thus producing a collection of means and standard deviations for the reconstructed intrinsic emittances.
+The left plot in Fig.~\ref{fig:mismatch} displays the standard deviations and biases for $\varepsilon_1$ (pink) and $\varepsilon_2$ (blue).
+
 %
@@
 % \end{figure*}
-%
-\begin{figure*}
-    \centering
-    \includegraphics[width=\textwidth]{figures/mismatch2.pdf}
-    \caption{Bias and standard deviation of $\varepsilon_1$ (red) and $\varepsilon_2$ (blue) from simulated reconstructions in the RTBT.
-In each plot, the collection of points is generated by varying the initial beam Twiss parameters.
-The true values of the emittances are printed on the top of the figures.}
-    \label{fig:mismatch}
-\end{figure*}
-%
 
-Although most of the points are clustered near the original bias and standard deviation of 7\% and 5\%, respectively, the bias increases to nearly 15\% in some cases, which may make it difficult to resolve weak cross-plane correlations; however, the measurement should still resolve strong cross-plane correlations.
+Although most of the points are clustered near the original bias and standard deviation of 7\% and 5\%, respectively, the bias increases to nearly 15\% in some cases, which may make it difficult to resolve weak cross-plane correlation; however, the measurement should still resolve strong cross-plane correlation.
 This is demonstrated in the rest of the plots in Fig.~\ref{fig:mismatch}, in which the entire process is repeated with $\varepsilon_1 / \varepsilon_2 > 1$.
@@
 This can be accomplished using charge-exchange injection and phase space painting.
-The working principle is to inject particles along an eigenvector of the one-turn transfer matrix; if this is accomplished, the particles trace ellipses on a turn-by-turn basis in the $x$-$y$ plane, and a uniform density ellipse is maintained throughout accumulation; hence, the 4D emittance remains near zero throughout accumulation.
+The working principle is to create elliptical modes in the ring — elliptical turn-by-turn trajectories of particles in the $x$-$y$ plane — and to inject particles into one of the modes, scaling the particle amplitudes with square root time-dependence.
+If the method works as intended, a uniform density ellipse with near-zero 4D emittance is maintained throughout accumulation.
 This technique, which we refer to as \textit{elliptical painting}, requires variation not only of the distance between circulating and injected beams — as in \textit{correlated painting} — but also of the angle between the beams.
-We represent the distances as $x$ and $y$ and the angles as $x'$ and $y'$.
-Details are contained in \cite{HooverThesis}.
+We represent the distances as $x$ and $y$ and the angles as $x'$ and $y'$ in this section.
+The best painting path in the SNS is a line in the $x$-$y'$ plane — i.e., the horizontal position and vertical angle of the closed orbit are varied while the vertical position and horizontal angle are fixed at zero — such that the apparent emittances are equal, painting an approximately circular distribution at the injection point.
 
-Initial attempts to perform elliptical painting in the SNS have been carried out.
-Due to current hardware constraints, we did not expect the painted beam to approach the ideal case of zero 4D emittance; however, we did expect significant deviations when compared to the standard correlated painting method.
-Fig.~\ref{fig:emittances_exp1a} shows the measured emittances at ten intervals over five hundred injected turns using the standard correlated painting method.
-As expected, the beam does not develop any significant cross-plane correlations.
-In Fig.~\ref{fig:emittances_exp1b}, painting was performed with initial coordinates ($x$, $x'$, $y$, $y'$) $\approx$ (10 mm, 0 mrad, 0 mm, 0 mrad) and final coordinates ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 0.7 mrad).
-The measured intrinsic emittances are significantly different than the measured apparent emittances.
-This data set, which was collected in less than two hours, allowed qualitative comparisons with computer simulation, which was used to guide future experiments.
+Initial attempts to perform this painting method in the SNS were carried out.
+The conditions were not ideal: First, due to hardware constraints at the time of the experiment, the required initial injection coordinates $x = x' = y = y' = 0$ could not be obtained at the nominal beam energy of 1 GeV.
+The closest possible coordinates were ($x$, $x'$, $y$, $y'$) = (10 mm, 0 mrad, 0 mm, 0 mrad), meaning that the initial distribution would have a hollow center and would not have a uniform charge density.
+Second, the maximum $y'$ was quite small at only 0.7 mrad, placing a severe limit on the vertical beam size.
+Finally, because no coupled elements existed in the SNS ring, elliptical modes had to be generated by equating the horizontal and vertical tunes; it was predicted that such a setup would be quite sensitive to the tune split and that nonlinearities would strongly influence the beam dynamics near the difference resonance $\nu_x \approx \nu_y$.
+Therefore, we did not expect the painted beam to approach the ideal case of uniform density and zero 4D emittance.
+Instead, we hoped for measurable deviations in the beam evolution when compared to the standard correlated painting method in which the injection angle is kept at zero.
 
-\begin{figure}
+Although the beam can only be measured after it has been accumulated in the ring, it can be extracted at different times during accumulation.
+In this initial experiment, the beam was accumulated over 500 injected turns and extracted every 50 turns.
+The measured emittances throughout accumulation are shown for correlated painting in Fig.~\ref{fig:emittances_exp1a}.
+%
+\begin{figure}[]
     \centering
@@
     \end{subfigure}
-    \caption{Measured emittances vs. number of injected turns in the SNS ring. (a) correlated (production) painting scheme; (b) non-standard painting scheme. [To do: larger axis labels.]}
+    \vfill
+    % \vspace*{0.25cm}
+    \vfill
+    \begin{subfigure}{0.49\columnwidth}
+        \includegraphics[width=\textwidth]{figures/emittances_exp2.pdf}
+        \caption{}
+        \label{fig:emittances_exp2}
+    \end{subfigure}
+    \begin{subfigure}{0.49\columnwidth}
+        \includegraphics[width=\textwidth]{figures/emittances_exp3.pdf}
+        \caption{}
+        \label{fig:emittances_exp3}
+    \end{subfigure}
+    \caption{Measured emittances vs. number of injected turns in the SNS ring. (a) correlated (production) painting scheme; (b) non-standard painting scheme; (c)-(d) elliptical painting.
+    [To do: larger axis labels? Different caption?]}
+    \label{fig:emittances_exp}
 \end{figure}
+%
+As expected, the beam does not develop any significant cross-plane correlations.
+The error bar centers and widths were determined by repeating the reconstruction as 3\% noise was added to the measured moments, then computing the means and standard deviations of the emittances over these trials.
+(Using the uncertainties in the LLSQ fit parameters was not possible since the cross-plane moments were exactly determined by the four measured profiles.) The beam was essentially matched at the RTBT entrance, so bias in the measurement was not a concern.
+
+The experiment was repeated with a different painting scheme.
+The initial injected coordinates were ($x$, $x'$, $y$, $y'$) $\approx$ (10 mm, 0 mrad, 0 mm, 0 mrad) and the final coordinates were ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 0.7 mrad).
+The measured intrinsic emittances shown in Fig.~\ref{fig:emittances_exp1b} are significantly different than the apparent emittances.
+This data set, which was collected in less than two hours, allowed qualitative comparisons with computer simulation and was used to guide future experiments.
+
+We also display the results of a second experiment in which the beam energy was lowered to 0.8 GeV, allowing initial injected coordinates $x = x' = y = y' = 0$ and final coordinates ($x$, $x'$, $y$, $y'$) = (21 mm, 0 mrad, 0 mm, 1.1 mrad).
+The beam Twiss parameters were more significantly mismatched at the RTBT entrance in this experiment, likely due to the increased space charge intensity, leading to larger uncertainty in the intrinsic emittances.
+Simulations predicted small cross-plane correlation in the beam, and although this was measured, it is on the order of the expected bias when the beam is significantly mismatched.
+In Fig.~\ref{fig:emittances_exp3}, the measurement was repeated for a larger beam size and smaller beam intensity, which simulations predicted would reduce the 4D emittance during accumulation.
+In this case, the differences between the intrinsic and apparent emittances cannot be explained by the expected bias in the reconstruction.
 
@@
 \label{sec:Conclusion}
+
+One critical component of efforts to generate a beam with small 4D emittance in the Spallation Neutron Source (SNS) is to measure the 4D emittance throughout accumulation.
+A variant of the multi-optics emittance reconstruction method was implemented using four available wire-scanners, but the fixed-optics method was not possible with the nominal machine optics: the probability of failed fits was large, and there was a significant bias in intrinsic emittances in the successful fits.
+Monte Carlo simulations were employed to select a new set of quadrupole strengths, eliminating the problem of failed fits and reducing the bias and uncertainty to acceptable values.
+
+The effect of beam mismatch on the reconstruction accuracy was also studied by varying the initial beam parameters and repeating the Monte Carlo trials.
+The bias in the intrinsic emittances increased from 7\% to 12\%, making it difficult to resolve small cross-plane correlation; however, this bias disappeared when significant cross-plane correlation was present in the beam.
+Thus, we concluded that the fixed-optics method was sufficient for fast measurements of the intrinsic beam emittances in the SNS.
+
+Finally, the method was applied to initial experiments at the SNS.
+The fast measurement time allowed the intrinsic emittances to be measured throughout accumulation for several different injection schemes.
+Significant differences in the intrinsic/apparent emittances were resolved.
+These results will be compared with simulations and used to guide future experiments.
 

### 2022-04-14 article.tex
Update figures

@@
 
-\author[author1]{A. Hoover}
-\affiliation[author1]{organization={The University of Tennessee},%Department and Organization
+\author[author1]{A. Hoover%
+% \thanks{Currently at Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA.} % This doesn't work!
+}
+\affiliation[author1]{organization={Department of Physics and Astronomy, University of Tennessee},
             city={Knoxville},
+            state={Tennessee},
             postcode={37996}, 
-            state={Tennessee},
             country={USA}}
@@
 \author[author2]{N. J. Evans}
-\affiliation[author2]{organization={Oak Ridge National Laboratory},%Department and Organization
+
+\affiliation[author2]{organization={Oak Ridge National Laboratory},
             addressline={One Bethel Valley Road}, 
             city={Oak Ridge},
+            state={Tennessee},
             postcode={37831}, 
-            state={Tennessee},
             country={USA}}
@@
 \begin{abstract}
-A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance could mitigate space charge effects in circular accelerators.
+A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance could mitigate space charge effects in circular accelerators, and improve collider performance.
 A scheme to approach such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source (SNS).
 A critical component of these efforts is to measure the 4D emittance of the beam.
-The 4D emittance can be reconstructed from at least four measurements of the real-space moments with different transfer matrices connecting the reconstruction and measurement locations, accomplished by varying either the machine optics (multi-optics method) or the measurement location (fixed-optics method).
+Reconstruction of the 4D emittance from wire-scanner data is a well-known technique.
 In this paper, we discuss the implementation of a variant of the multi-optics method using the four available wire-scanners near the SNS target, as well as the modification of the wire-scanner region to utilize the fixed-optics method — a method that is preferred due to its speed but can potentially lead to unacceptable bias and uncertainty in the reconstructed emittances.
@@
 
-A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance could mitigate space charge effects in circular accelerators \cite{Danilov2003, Burov2002, Burov2013}.
-A scheme to generate such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source (SNS) accumulator ring \cite{Holmes2018, Hoover2021}.
+A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance could mitigate space charge effects in circular accelerators and improve collider performance \cite{Danilov2003, Burov2002, Burov2013}.
+A phase space painting method to generate such a distribution is being tested in the Spallation Neutron Source (SNS) accumulator ring \cite{Holmes2018, Hoover2021}.
 A critical component of these efforts is to measure the 4D beam emittance.
@@
 The covariance matrix, and hence the root-mean-square emittances, can be reconstructed from at least four wire-scanner measurements with different transfer matrices connecting the measurement and reconstruction locations \cite{book:Minty2003}.\footnote{Reconstruction of the transverse phase space distribution is possible using 2D projections of the distribution on a screen \cite{Hock2013, Wang2019, Wolski2020}.
-This may be possible using the SNS target imaging system \cite{Blokland2010} but is not pursued here.} The transfer matrix elements can be controlled by varying the machine optics (multi-optics method), the measurement location (fixed-optics method), or any combination of the two \cite{Prat2014}.
-The fixed-optics method is possible and preferred in our case due to its speed; however, previous studies have shown that the method can be sensitive to errors \cite{Raimondi1993, Woodley2000, Agapov2007, Faus-Golfe2016}.
+This may be possible using the SNS target imaging system \cite{Blokland2010} but is not pursued here.} In general, the transfer matrix elements can be controlled by varying the machine optics (multi-optics method), the measurement location (fixed-optics method), or any combination of the two \cite{Prat2014}.
+With four available wire-scanners, the fixed-optics method is possible and preferred in our case due to its speed; however, previous studies have shown that the method can be sensitive to errors \cite{Raimondi1993, Woodley2000, Agapov2007, Faus-Golfe2016}.
 
-The purpose of this work is to determine whether the multi-optics and/or fixed-optics methods are feasible in the SNS.
-The reconstruction method is reviewed in Section \ref{sec:Four-dimensional emittance measurement}; the implementation of the method in the SNS is discussed in Section \ref{sec:Implementation in the SNS}; the method is applied to measure the 4D emittance of an SNS beam throughout accumulation in Section \ref{sec:Example application}.
+The purpose of this work is to determine the limitations of the fixed-optics method in the SNS.
+The reconstruction method is reviewed in Section \ref{sec:Four-dimensional emittance measurement}; the implementation of the multi-optics and fixed-optics methods in the SNS is discussed in Section \ref{sec:Implementation in the SNS}; the fixed-optics method is demonstrated in Section \ref{sec:Example application} by measuring the 4D emittance as a function of time during accumulation in the SNS ring.
 
@@
     \centering
-    \includegraphics[width=0.7\columnwidth]{figures/rtbt.png}
-    \hspace{1cm}
-    \includegraphics[width=1.2\columnwidth]{figures/rtbt_optics.pdf}
-    \caption{The wire-scanner region of the ring-target beam transport (RTBT) section of the SNS.}
+    \raisebox{20pt}{\includegraphics[width=0.71\columnwidth]{figures/rtbt_mod.pdf}
+    \hspace{1cm}}
+    \includegraphics[width=1.2\columnwidth]{figures/rtbt_optics_mod.pdf}
+    \caption{The wire-scanner region of the ring-target beam transport (RTBT) section of the SNS. The red box indicates where the measurement takes place.}
     \label{fig:rtbt}
@@
 In 2D emittance measurements, the phase advance from the reconstruction location to the measurement location is typically varied uniformly within a $180\degree$ range.\footnote{Intuitively, the error is expected to be minimized when the projection angles are spread uniformly between 0 and $\pi$; however, the projection angles are only equal to the phase advances in normalized phase space \cite{Hock2011}.
-Nonetheless, it is often convenient to vary the phase advances instead of the projection angles.} Prat and Aiba \cite{Prat2014} applied this strategy to the 4D emittance measurement: in the first half of the scan, the horizontal phase advance was varied while the vertical phase advance was held fixed, and in the second half of the scan, the vertical phase advance was varied while the horizontal phase advance was held fixed.
+Nonetheless, it is often convenient to vary the phase advances instead of the projection angles.} Prat and Aiba \cite{Prat2014} applied this strategy to the 4D emittance measurement: in the first half of the scan, the horizontal phase advance was varied while the vertical phase advance was held fixed; in the second half of the scan, the vertical phase advance was varied while the horizontal phase advance was held fixed.
 Since the four SNS wire-scanners are already spaced somewhat evenly in phase advance, maximal phase coverage is possible by varying the phase advances at each wire-scanner in a $30\degree$ window; however, control of the phase advances between each wire-scanner is limited due to the shared power supplies of the RTBT quadrupoles.
@@
 
-The best we can do is to control the phase advances from the first varied quadrupole (QH18) to the last wire-scanner (WS24), which also modifies the phase advances at the other wire-scanners by similar amounts.
+Therefore, we chose to vary the phase advances from the first varied quadrupole (QH18) to the last wire-scanner (WS24), which also modifies the phase advances at the other wire-scanners by similar amounts.
 To control these phase advances, the two power supplies (eight quadrupoles) in the wire-scanner region are varied to minimize the following cost function:
@@
 \begin{equation}
-    C(\mathbf{g}) = \left\Vert{\tilde{\bm{\mu}} - \bm{\mu} }\right\Vert^2
+    C(\mathbf{g}) = 
+    \left\Vert{
+        \bm{\mu} - \tilde{\bm{\mu}}
+    }\right\Vert^2
     + 
@@
     \left\Vert
-        \Theta\left(
-            \tilde{\bm{\beta}}_{max} - \bm{\beta}_{max}
+        \max\left(
+            0, \,
+            \bm{\beta}_{max} - \tilde{\bm{\beta}}_{max}
         \right)
@@
 %
-The quadrupole strengths are contained in the vector $\mathbf{g}$; the calculated phase advances are $\bm{\mu} = (\mu_x, \mu_y)$; the desired phase advances are $\tilde{\bm{\mu}} = (\tilde{\mu}_x, \tilde{\mu}_y)$; the maximum calculated $\beta$ functions in the wire-scanner region are $\bm{\beta}_{max} = (\beta_{x_{max}}, \beta_{y_{max}})$; the maximum allowed $\beta$ functions in the wire-scanner region are $\tilde{\bm{\beta}}_{max} = (\tilde{\beta}_{x_{max}}, \tilde{\beta}_{y_{max}})$; $\Theta$ is the Heaviside step function; $\epsilon$ is a constant.
-After this process is completed, the remaining five quadrupoles before the target are varied to constrain the beam size at the target.
+The quadrupole strengths are contained in the vector $\mathbf{g}$; the calculated phase advances are $\bm{\mu} = (\mu_x, \mu_y)$; the desired phase advances are $\tilde{\bm{\mu}} = (\tilde{\mu}_x, \tilde{\mu}_y)$; the maximum calculated $\beta$ functions in the wire-scanner region are $\bm{\beta}_{max} = (\beta_{x_{max}}, \beta_{y_{max}})$; the maximum allowed $\beta$ functions in the wire-scanner region are $\tilde{\bm{\beta}}_{max} = (\tilde{\beta}_{x_{max}}, \tilde{\beta}_{y_{max}})$; $\epsilon$ is a constant.
+After this process is completed, the remaining five quadrupoles before the target are used to constrain the beam size at the target.
 
-This multi-optics method was tested on a fully accumulated production beam in the SNS using ten measurements (forty profiles), which were completed in one hour.
+This multi-optics method was tested on a fully accumulated production beam in the SNS using ten measurements (forty profiles), which were collected in one hour.
 The reconstructed Twiss parameters, emittances, and best-fit ellipses in the $x$-$x'$ and $y$-$y'$ planes (normalized by the reconstructed Twiss parameters) are displayed in Fig.~\ref{fig:multi_optics_measurement}.
@@
 %
-The uncertainties in the parameters were calculated by propagating the standard deviations of the ten reconstructed moments obtained from the linear least squares (LLSQ) estimator.\footnote{See Appendix A of \cite{Faus-Golfe2016}.} The reconstructed Twiss parameters are close to the model parameters computed from the linear transfer matrices of the ring and RTBT, showing that the beam was matched to the nominal ring optics when it was extracted from the ring.
+The uncertainties in the parameters were calculated by propagating the standard deviations of the ten reconstructed moments obtained from the linear least squares (LLSQ) estimator.\footnote{See Appendix A of \cite{Faus-Golfe2016}.} The reconstructed Twiss parameters are close to the model parameters computed from the linear transfer matrices of the ring and RTBT, showing that the beam was matched to the nominal optics when it was extracted from the ring.
 The intrinsic emittances are almost equal to the apparent emittances, showing that there was very little cross-plane correlation in the beam.
@@
 We initially performed similar studies using envelope tracking to estimate the reconstruction errors in the RTBT, also concluding that method should remain accurate \cite{Hoover2021-IPAC}.
-From repeated wire-scanner measurements with the same machine setup, we estimate the error in the measured moments to be only 3\%, and none of the other sources of uncertainty were found to have a large effect on the reconstructed emittances.
-Space charge forces, which can render the method invalid for high-perveance beams \cite{Anderson2002}, can be neglected since the space charge tune shift in the ring is around 3\% and the distance between the reconstruction and measurement locations is much smaller than the ring length ($\approx$ 250 meters).
+From repeated wire-scanner measurements with the same machine setup, we estimated the error in the measured moments to be only 3\%, and none of the other sources of uncertainty were found to have a large effect on the reconstructed emittances.
+Space charge forces, which can render the method invalid for high-perveance beams \cite{Anderson2002}, can be neglected since the space charge tune shift in the ring is around 3\% and the distance between the reconstruction and measurement locations is much smaller than the ring length.
 
@@
 For example, it could be possible for $\varepsilon_2$ to remain small (as desired) in the first half of accumulation before growing to a much larger value in the second half of accumulation.
-Measurement of this emittance evolution would convey valuable information about the beam dynamics and allow for qualitative comparison with computer simulation.
-Second, it would be beneficial to quickly evaluate various machine states, the best of which will be unknown during initial experiments.
-Finally, a practical point: the time reserved for accelerator physics (AP) experiments at the SNS is limited, and the setup for initial experiments will be much longer than typical AP experiments for reasons not discussed in this paper.
+Measurement of this emittance evolution would convey valuable information about the beam dynamics and allow qualitative comparison with computer simulation.
+Second, it would be beneficial to quickly evaluate various machine states: although computer simulation can be used as a guide in choosing the experimental parameters, online tuning is expected to be necessary since small changes to the accelerator may have large effects on the painted phase space distribution.
+Third, the time reserved for accelerator physics experiments at the SNS is limited, and the setup for our initial experiments will take longer than usual due to the modification of the beam energy.
 Thus, the fixed-optics method is preferred.
@@
 We performed a similar modification of the RTBT optics, using these previous studies as a guide.
-Recall that we have two knobs: the two power supplies in the wire-scanner region used to control the phase advances at the final wire-scanner.
+Recall the two available knobs: the two power supplies in the wire-scanner region used to control the phase advances at the final wire-scanner.
 To search for a better set of optics, we varied these phase advances ($\mu_x$, $\mu_y$) in a $90\degree$ window around their nominal values ($\mu_{x0}$, $\mu_{y0}$).
@@
     \centering
-    \includegraphics[width=\textwidth]{figures/mismatch2.pdf}
+    \includegraphics[width=0.92\textwidth]{figures/mismatch2.pdf}
     \caption{Bias and standard deviation of $\varepsilon_1$ (pink) and $\varepsilon_2$ (blue) from simulated reconstructions in the RTBT.
@@
 It is possible, however, for space charge to effectively modify the ring Twiss parameters, resulting in mismatch when entering the RTBT.
-This modification is small for the normal injection scheme, as shown in Fig.~\ref{fig:multi_optics_measurement}, but we have generated more significant mismatch in our studies of non-standard injection schemes.
+This modification is small for the normal injection scheme, as shown in Fig.~\ref{fig:multi_optics_measurement}, but we have generated more significant mismatch in our studies of non-standard injection schemes at lower beam energies.
 One example is shown in Table~\ref{tab:mismatch}.
@@
 The beam mismatch is unlikely to exceed these values in our studies.
-To examine the effect of mismatch, we first moved the operating point to $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$, then varied $\beta_x$ and $\beta_y$ within a $\pm 20\%$ window around their model values, $\alpha_x$ within a $\pm 15\%$ window, and $\alpha_y$ within a $-40\%, +10\%$ window to extend beyond the measured discrepancies, and repeated the Monte Carlo trials for each initial beam, thus producing a collection of means and standard deviations for the reconstructed intrinsic emittances.
+To examine the effect of mismatch, we first moved the operating point to $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$, then varied $\beta_x$ and $\beta_y$ within a $\pm 20\%$ window around their model values, $\alpha_x$ within a $\pm 15\%$ window, and $\alpha_y$ within a $-40\%, +10\%$ window to extend beyond the measured discrepancies, and repeated the Monte Carlo trials for each initial beam, producing a collection of means and standard deviations for the reconstructed intrinsic emittances.
 The left plot in Fig.~\ref{fig:mismatch} displays the standard deviations and biases for $\varepsilon_1$ (pink) and $\varepsilon_2$ (blue).
@@
 
-We now demonstrate the usefulness of the fixed-optics emittance measurement in the SNS.
-Again, our ultimate goal is to generate a beam with a uniform charge density, elliptical transverse profile, and small 4D emittance.
-This can be accomplished using charge-exchange injection and phase space painting.
-The working principle is to create elliptical modes in the ring — elliptical turn-by-turn trajectories of particles in the $x$-$y$ plane — and to inject particles into one of the modes, scaling the particle amplitudes with square root time-dependence.
-If the method works as intended, a uniform density ellipse with near-zero 4D emittance is maintained throughout accumulation.
-This technique, which we refer to as \textit{elliptical painting}, requires variation not only of the distance between circulating and injected beams — as in \textit{correlated painting} — but also of the angle between the beams.
-We represent the distances as $x$ and $y$ and the angles as $x'$ and $y'$ in this section.
-The best painting path in the SNS is a line in the $x$-$y'$ plane — i.e., the horizontal position and vertical angle of the closed orbit are varied while the vertical position and horizontal angle are fixed at zero — such that the apparent emittances are equal, painting an approximately circular distribution at the injection point.
-
-Initial attempts to perform this painting method in the SNS were carried out.
-The conditions were not ideal: First, due to hardware constraints at the time of the experiment, the required initial injection coordinates $x = x' = y = y' = 0$ could not be obtained at the nominal beam energy of 1 GeV.
-The closest possible coordinates were ($x$, $x'$, $y$, $y'$) = (10 mm, 0 mrad, 0 mm, 0 mrad), meaning that the initial distribution would have a hollow center and would not have a uniform charge density.
-Second, the maximum $y'$ was quite small at only 0.7 mrad, placing a severe limit on the vertical beam size.
-Finally, because no coupled elements existed in the SNS ring, elliptical modes had to be generated by equating the horizontal and vertical tunes; it was predicted that such a setup would be quite sensitive to the tune split and that nonlinearities would strongly influence the beam dynamics near the difference resonance $\nu_x \approx \nu_y$.
-Therefore, we did not expect the painted beam to approach the ideal case of uniform density and zero 4D emittance.
-Instead, we hoped for measurable deviations in the beam evolution when compared to the standard correlated painting method in which the injection angle is kept at zero.
-
-Although the beam can only be measured after it has been accumulated in the ring, it can be extracted at different times during accumulation.
-In this initial experiment, the beam was accumulated over 500 injected turns and extracted every 50 turns.
-The measured emittances throughout accumulation are shown for correlated painting in Fig.~\ref{fig:emittances_exp1a}.
+We now demonstrate the usefulness of the fixed-optics emittance measurement.
+For later comparison, we first measured a 1 GeV beam produced by standard correlated painting.
+The beam was accumulated over 500 injected turns and extracted and measured every 50 turns.
+The reconstructed emittances throughout accumulation are shown in Fig.~\ref{fig:emittances_exp}a.
 %
-\begin{figure}[]
+\begin{figure}[b!]
     \centering
-    \begin{subfigure}{0.49\columnwidth}
-        \includegraphics[width=\textwidth]{figures/emittances_exp1a.pdf}
-        \caption{}
-        \label{fig:emittances_exp1a}
-    \end{subfigure}
-    \begin{subfigure}{0.49\columnwidth}
-        \includegraphics[width=\textwidth]{figures/emittances_exp1b.pdf}
-        \caption{}
-        \label{fig:emittances_exp1b}
-    \end{subfigure}
-    \vfill
-    % \vspace*{0.25cm}
-    \vfill
-    \begin{subfigure}{0.49\columnwidth}
-        \includegraphics[width=\textwidth]{figures/emittances_exp2.pdf}
-        \caption{}
-        \label{fig:emittances_exp2}
-    \end{subfigure}
-    \begin{subfigure}{0.49\columnwidth}
-        \includegraphics[width=\textwidth]{figures/emittances_exp3.pdf}
-        \caption{}
-        \label{fig:emittances_exp3}
-    \end{subfigure}
-    \caption{Measured emittances vs. number of injected turns in the SNS ring. (a) correlated (production) painting scheme; (b) non-standard painting scheme; (c)-(d) elliptical painting.
-    [To do: larger axis labels? Different caption?]}
+    \includegraphics[width=\columnwidth]{figures/emittances2.pdf}
+    \caption{Measured emittances vs.
+number of injected turns in the SNS ring.
+(a) correlated (production) painting at 1 GeV; (b) attempted elliptical painting at 1 GeV; (c)-(d) elliptical painting at 0.8 GeV.}
     \label{fig:emittances_exp}
@@
 %
-As expected, the beam does not develop any significant cross-plane correlations.
+As expected, the beam did not develop any significant cross-plane correlation.
 The error bar centers and widths were determined by repeating the reconstruction as 3\% noise was added to the measured moments, then computing the means and standard deviations of the emittances over these trials.
@@
 
-The experiment was repeated with a different painting scheme.
-The initial injected coordinates were ($x$, $x'$, $y$, $y'$) $\approx$ (10 mm, 0 mrad, 0 mm, 0 mrad) and the final coordinates were ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 0.7 mrad).
-The measured intrinsic emittances shown in Fig.~\ref{fig:emittances_exp1b} are significantly different than the apparent emittances.
-This data set, which was collected in less than two hours, allowed qualitative comparisons with computer simulation and was used to guide future experiments.
+Our ultimate goal is to generate a beam with a uniform charge density, elliptical transverse profile, and small 4D emittance.
+This can be accomplished using phase space painting: the working principle is to create elliptical modes in the ring — elliptical turn-by-turn trajectories of particles in the $x$-$y$ plane — and to inject particles into one of the modes, scaling the particle amplitudes with square root time-dependence.
+If the method works as intended, a uniform density ellipse with near-zero 4D emittance is maintained throughout accumulation.
+This technique, which we refer to as \textit{elliptical painting}, requires variation not only of the distance between the circulating and injected beams, but also of the angle between the beams.
+We denote the distances as $x$ and $y$ and the angles as $x'$ and $y'$ in this section.
+The most promising painting path in the SNS is a line in the $x$-$y'$ plane with a slope chosen such that the apparent emittances are equal, resulting in an approximately circular distribution at the injection point.
+These injection parameters are measured and controlled using beam-position-monitor (BPM) waveforms in the ring and eight time-dependent injection kicker magnets \cite{Hoover2022-thesis}.
 
-We also display the results of a second experiment in which the beam energy was lowered to 0.8 GeV, allowing initial injected coordinates $x = x' = y = y' = 0$ and final coordinates ($x$, $x'$, $y$, $y'$) = (21 mm, 0 mrad, 0 mm, 1.1 mrad).
+An initial attempt to perform elliptical painting was carried out.
+The conditions were not ideal: First, due to hardware constraints, the required initial injection coordinates $x = x' = y = y' = 0$ could not be obtained at the nominal beam energy of 1 GeV.
+The closest possible coordinates were ($x$, $x'$, $y$, $y'$) = (10 mm, 0 mrad, 0 mm, 0 mrad), meaning that the initial distribution had have a hollow center and would not have a uniform charge density.
+Second, the maximum $y'$ was quite small at 0.7 mrad, placing a limit on the vertical beam size.
+Third, because no coupled elements existed in the SNS ring, elliptical modes were generated by equating the horizontal and vertical tunes; it was expected that such a setup would be sensitive to the tune split and that nonlinearities would strongly influence the beam dynamics near the difference resonance $\nu_x \approx \nu_y$.
+Therefore, we did not expect the painted beam to approach the ideal case of uniform density and zero 4D emittance.
+Instead, we hoped for measurable deviations in the beam evolution when compared to the standard correlated painting method.
+
+The results of the attempt are displayed in Fig.~\ref{fig:emittances_exp}b.
+The initial injected coordinates were ($x$, $x'$, $y$, $y'$) $\approx$ (10 mm, 0 mrad, 0 mm, 0 mrad) and the final injected coordinates were ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 0.7 mrad).
+The measured intrinsic emittances are significantly different than the apparent emittances.
+The twenty measurements in Fig.~\ref{fig:emittances_exp}a and Fig.~\ref{fig:emittances_exp}b, which were completed in less than two hours, allowed qualitative comparisons with computer simulation and were used to guide future experiments.
+
+In Fig.~\ref{fig:emittances_exp}c, we display the results of a second experiment in which the beam energy was lowered to 0.8 GeV, allowing initial injected coordinates $x \approx x' \approx y \approx y' \approx 0$ and final coordinates ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 1.1 mrad).
 The beam Twiss parameters were more significantly mismatched at the RTBT entrance in this experiment, likely due to the increased space charge intensity, leading to larger uncertainty in the intrinsic emittances.
 Simulations predicted small cross-plane correlation in the beam, and although this was measured, it is on the order of the expected bias when the beam is significantly mismatched.
-In Fig.~\ref{fig:emittances_exp3}, the measurement was repeated for a larger beam size and smaller beam intensity, which simulations predicted would reduce the 4D emittance during accumulation.
+In Fig.~\ref{fig:emittances_exp}d, the measurement was repeated for a larger beam size and smaller beam intensity, which simulations predicted would reduce the 4D emittance during accumulation.
 In this case, the differences between the intrinsic and apparent emittances cannot be explained by the expected bias in the reconstruction.
@@
 The bias in the intrinsic emittances increased from 7\% to 12\%, making it difficult to resolve small cross-plane correlation; however, this bias disappeared when significant cross-plane correlation was present in the beam.
-Thus, we concluded that the fixed-optics method was sufficient for fast measurements of the intrinsic beam emittances in the SNS.
+Thus, we concluded that the fixed-optics method is sufficient for fast measurements of the intrinsic beam emittances in the SNS.
 
 Finally, the method was applied to initial experiments at the SNS.
-The fast measurement time allowed the intrinsic emittances to be measured throughout accumulation for several different injection schemes.
+The fast measurement time allowed the intrinsic emittances to be measured throughout accumulation for several different painting methods.
 Significant differences in the intrinsic/apparent emittances were resolved.
 These results will be compared with simulations and used to guide future experiments.
+
+\section{Acknowledgements}
+This manuscript has been authored by UT-Battelle, LLC, under Contract No.
+DE-AC05-00OR22725 with the U.S.
+Department of Energy.
+The United States Government retains, and the publisher, by accepting the article for publication, acknowledges that the United States Government retains a nonexclusive, paid-up, irrevocable, world-wide license to publish or reproduce the published form of this manuscript, or allow others to do so, for United States Government purposes.
 

### 2022-04-14 main.tex
Flat file structure for figures — required by Elsevier

--- 2022-04-14 article.tex
@@
 \begin{abstract}
-A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance could mitigate space charge effects in circular accelerators, and improve collider performance.
-A scheme to approach such a distribution using charge-exchange injection and phase space painting is being tested in the Spallation Neutron Source (SNS).
+A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance could mitigate space charge effects in circular accelerators and improve collider performance.
+A phase space painting method to generate such a distribution is being tested in the Spallation Neutron Source (SNS) accumulator ring.
 A critical component of these efforts is to measure the 4D emittance of the beam.
@@
 The wire-scanners are run in parallel and take approximately five minutes to move across the beam and return to their original positions.
-Their step size is 3 mm and their dynamic range is approximately $10^2$.
+Their step size is 3 mm and their dynamic range is approximately $100$.
 They are run at a beam pulse frequency of 1 Hz.\footnote{Each data point corresponds to a separate beam pulse, so the measurement relies on pulse-to-pulse stability.} Each wire-scanner has three wires to measure the 1D projection of the distribution onto the $x$, $y$ and $u$ axes, where $u$ is tilted at an angle $\phi = \pi / 4$ above the $x$ axis; $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$ can be extracted from these projections, as well as $\langle{xy}\rangle$ from
@@
 %
-The wire-scanner locations, quadrupole locations, and nominal optical functions at the end of the RTBT are shown in Fig.~\ref{fig:rtbt}.
+The wire-scanner locations, quadrupole locations, and nominal optical functions at the end of the RTBT are shown in Fig.~\ref{fig:1}.
+
 %
@@
     \centering
-    \raisebox{20pt}{\includegraphics[width=0.71\columnwidth]{figures/rtbt_mod.pdf}
+    \raisebox{20pt}{\includegraphics[width=0.71\columnwidth]{fig1a.pdf}
     \hspace{1cm}}
-    \includegraphics[width=1.2\columnwidth]{figures/rtbt_optics_mod.pdf}
+    \includegraphics[width=1.2\columnwidth]{fig1b.pdf}
     \caption{The wire-scanner region of the ring-target beam transport (RTBT) section of the SNS. The red box indicates where the measurement takes place.}
-    \label{fig:rtbt}
+    \label{fig:1}
 \end{figure*}
@@
 This multi-optics method was tested on a fully accumulated production beam in the SNS using ten measurements (forty profiles), which were collected in one hour.
-The reconstructed Twiss parameters, emittances, and best-fit ellipses in the $x$-$x'$ and $y$-$y'$ planes (normalized by the reconstructed Twiss parameters) are displayed in Fig.~\ref{fig:multi_optics_measurement}.
+The reconstructed Twiss parameters, emittances, and best-fit ellipses in the $x$-$x'$ and $y$-$y'$ planes (normalized by the reconstructed Twiss parameters) are displayed in Fig.~\ref{fig:2}.
 %
@@
     \centering
-    \includegraphics[width=\columnwidth]{figures/multi_optics_measurement.pdf}
+    \includegraphics[width=\columnwidth]{fig2.pdf}
     % \par\medskip
@@
     \caption{Reconstructed beam parameters and graphical output (in normalized phase space) from a multi-optics emittance measurement of a production beam.}
-    \label{fig:multi_optics_measurement}
+    \label{fig:2}
 \end{figure}
@@
 
-Unfortunately, the nominal optics in the RTBT are ill-suited for the fixed-optics reconstruction: if only one set of optics from Fig.~\ref{fig:multi_optics_measurement} is used, the resulting covariance matrix is not positive-definite.
+Unfortunately, the nominal optics in the RTBT are ill-suited for the fixed-optics reconstruction: if only one set of optics from Fig.~\ref{fig:2} is used, the resulting covariance matrix is not positive-definite.
 We label this a failed fit.
@@
 To investigate the sensitivity of the fixed-optics method, we generated a covariance matrix with $\varepsilon_1 = \varepsilon_x$ = 32 mm~mrad and $\varepsilon_2 = \varepsilon_y$ = 25 mm~mrad, close to the measured values, and with Twiss parameters matched to the lattice.
-This covariance matrix was tracked to the wire-scanners using the transfer matrices from the fifth step in the scan of Fig.~\ref{fig:multi_optics_measurement}, and the reconstruction was performed many times with 3\% random noise added to the $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$ moments.
+This covariance matrix was tracked to the wire-scanners using the transfer matrices from the fifth step in the scan of Fig.~\ref{fig:2}, and the reconstruction was performed many times with 3\% random noise added to the $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$ moments.
 (We ignored any uncertainty in the transfer matrix elements, which were expected to be small.) This resulted in a large fraction of failed trials, but some successful trials.
-Fig.~\ref{fig:failed_fits} shows the emittances in the successful trials.
+Fig.~\ref{fig:3} shows the emittances in the successful trials.
 %
@@
     \centering
-    \includegraphics[width=\columnwidth]{figures/failed_fits.pdf}
+    \includegraphics[width=\columnwidth]{fig3.pdf}
     \caption{Simulated emittance measurement using the nominal optics in the RTBT.}
-    \label{fig:failed_fits}
+    \label{fig:3}
 \end{figure}
-%
-%
-% \begin{figure}[h!]
-%     \centering
-%     \includegraphics[width=\columnwidth]{figures/profiles.pdf}
-%     \caption{Profiles from two consecutive wire-scanner measurements in the SNS.}
-%     \label{fig:profiles}
-% \end{figure}
 %
@@
 The mean and standard deviation of the emittances were calculated over the successful trials.
-The difference between the mean emittances and the true emittances, which we refer to as the \textit{bias}, is plotted for each set of optics in the top row of Fig.~\ref{fig:sensitivity_scan}, as well as the standard deviations in the bottom row.
+The difference between the mean emittances and the true emittances, which we refer to as the \textit{bias}, is plotted for each set of optics in the top row of Fig.~\ref{fig:4}, as well as the standard deviations in the bottom row.
 %
@@
     \centering
-    \includegraphics[width=\columnwidth]{figures/sensitivity_scan2.pdf}
+    \includegraphics[width=\columnwidth]{fig4.pdf}
     \caption{Simulated bias and standard deviation of the intrinsic emittances in the RTBT as a function of the phase advances at WS24.}
-    \label{fig:sensitivity_scan}
+    \label{fig:4}
 \end{figure}
@@
     \centering
-    \includegraphics[width=0.92\textwidth]{figures/mismatch2.pdf}
+    \includegraphics[width=0.92\textwidth]{fig5.pdf}
     \caption{Bias and standard deviation of $\varepsilon_1$ (pink) and $\varepsilon_2$ (blue) from simulated reconstructions in the RTBT.
@@
 The true values of the emittances are printed on the top of the figures.}
-    \label{fig:mismatch}
+    \label{fig:5}
 \end{figure*}
@@
 It is possible, however, for space charge to effectively modify the ring Twiss parameters, resulting in mismatch when entering the RTBT.
-This modification is small for the normal injection scheme, as shown in Fig.~\ref{fig:multi_optics_measurement}, but we have generated more significant mismatch in our studies of non-standard injection schemes at lower beam energies.
+This modification is small for the normal injection scheme, as shown in Fig.~\ref{fig:2}, but we have generated more significant mismatch in our studies of non-standard injection schemes at lower beam energies.
 One example is shown in Table~\ref{tab:mismatch}.
@@
 To examine the effect of mismatch, we first moved the operating point to $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$, then varied $\beta_x$ and $\beta_y$ within a $\pm 20\%$ window around their model values, $\alpha_x$ within a $\pm 15\%$ window, and $\alpha_y$ within a $-40\%, +10\%$ window to extend beyond the measured discrepancies, and repeated the Monte Carlo trials for each initial beam, producing a collection of means and standard deviations for the reconstructed intrinsic emittances.
-The left plot in Fig.~\ref{fig:mismatch} displays the standard deviations and biases for $\varepsilon_1$ (pink) and $\varepsilon_2$ (blue).
-
-%
-% \begin{figure*}
-%     \centering
-%     \begin{subfigure}{0.99\columnwidth}
-%         \includegraphics[width=\textwidth]{figures/mismatch.pdf}
-%         \caption{}
-%         \label{fig:mismatch}
-%     \end{subfigure}
-%     \hspace{0.5cm}
-%     \begin{subfigure}{0.99\columnwidth}
-%         \includegraphics[width=\textwidth]{figures/mismatch_unequal_emittances.pdf}
-%         \caption{}
-%         \label{fig:mismatch_unequal_emittances}
-%     \end{subfigure}
-%     \caption{Simulated fractional error and standard deviation of reconstructed intrinsic emittances as a function of the beam mismatch parameter.
-(a) $\varepsilon_1 / \varepsilon_2 = 1$; (b) $\varepsilon_1 / \varepsilon_2 = 3$.}
-% \end{figure*}
+The left plot in Fig.~\ref{fig:5} displays the standard deviations and biases for $\varepsilon_1$ (pink) and $\varepsilon_2$ (blue).
 
 Although most of the points are clustered near the original bias and standard deviation of 7\% and 5\%, respectively, the bias increases to nearly 15\% in some cases, which may make it difficult to resolve weak cross-plane correlation; however, the measurement should still resolve strong cross-plane correlation.
-This is demonstrated in the rest of the plots in Fig.~\ref{fig:mismatch}, in which the entire process is repeated with $\varepsilon_1 / \varepsilon_2 > 1$.
+This is demonstrated in the rest of the plots in Fig.~\ref{fig:5}, in which the entire process is repeated with $\varepsilon_1 / \varepsilon_2 > 1$.
 The bias in the reconstruction quickly decreases — the emittances are clustered around their true values.
@@
 The beam was accumulated over 500 injected turns and extracted and measured every 50 turns.
-The reconstructed emittances throughout accumulation are shown in Fig.~\ref{fig:emittances_exp}a.
+The reconstructed emittances throughout accumulation are shown in Fig.~\ref{fig:6}a.
 %
@@
     \centering
-    \includegraphics[width=\columnwidth]{figures/emittances2.pdf}
+    \includegraphics[width=\columnwidth]{fig6.pdf}
     \caption{Measured emittances vs.
@@
 (a) correlated (production) painting at 1 GeV; (b) attempted elliptical painting at 1 GeV; (c)-(d) elliptical painting at 0.8 GeV.}
-    \label{fig:emittances_exp}
+    \label{fig:6}
 \end{figure}
@@
 
-The results of the attempt are displayed in Fig.~\ref{fig:emittances_exp}b.
+The results of the attempt are displayed in Fig.~\ref{fig:6}b.
 The initial injected coordinates were ($x$, $x'$, $y$, $y'$) $\approx$ (10 mm, 0 mrad, 0 mm, 0 mrad) and the final injected coordinates were ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 0.7 mrad).
 The measured intrinsic emittances are significantly different than the apparent emittances.
-The twenty measurements in Fig.~\ref{fig:emittances_exp}a and Fig.~\ref{fig:emittances_exp}b, which were completed in less than two hours, allowed qualitative comparisons with computer simulation and were used to guide future experiments.
+The twenty measurements in Fig.~\ref{fig:6}a and Fig.~\ref{fig:6}b, which were completed in less than two hours, allowed qualitative comparisons with computer simulation and were used to guide future experiments.
 
-In Fig.~\ref{fig:emittances_exp}c, we display the results of a second experiment in which the beam energy was lowered to 0.8 GeV, allowing initial injected coordinates $x \approx x' \approx y \approx y' \approx 0$ and final coordinates ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 1.1 mrad).
+In Fig.~\ref{fig:6}c, we display the results of a second experiment in which the beam energy was lowered to 0.8 GeV, allowing initial injected coordinates $x \approx x' \approx y \approx y' \approx 0$ and final coordinates ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 1.1 mrad).
 The beam Twiss parameters were more significantly mismatched at the RTBT entrance in this experiment, likely due to the increased space charge intensity, leading to larger uncertainty in the intrinsic emittances.
 Simulations predicted small cross-plane correlation in the beam, and although this was measured, it is on the order of the expected bias when the beam is significantly mismatched.
-In Fig.~\ref{fig:emittances_exp}d, the measurement was repeated for a larger beam size and smaller beam intensity, which simulations predicted would reduce the 4D emittance during accumulation.
+In Fig.~\ref{fig:6}d, the measurement was repeated for a larger beam size and smaller beam intensity, which simulations predicted would reduce the 4D emittance during accumulation.
 In this case, the differences between the intrinsic and apparent emittances cannot be explained by the expected bias in the reconstruction.
@@
 
-%% The Appendices part is started with the command \appendix;
-%% appendix sections are then done as normal sections
-%% \appendix
-
-%% \section{}
-%% \label{}
-
-%% If you have bibdatabase file and want bibtex to generate the
-%% bibitems, please use
-%%
-%%  \bibliographystyle{elsarticle-num} 
-%%  \bibliography{<your bibdatabase>}
-
-%% else use the following coding to input the bibitems directly in the
-%% TeX file.
-
 \bibliographystyle{elsarticle-num} 

### 2022-07-23 main.tex
NIM submission version
Updates from Overleaf

@@
 %%
-\documentclass[final,5p,twocolumn,times]{elsarticle}
 
 %% Use the option review to obtain double line spacing
-%% \documentclass[authoryear,preprint,review,12pt]{elsarticle}
+% \documentclass[preprint,review,times]{elsarticle}
 
@@
 %% \documentclass[final,1p,times]{elsarticle}
-%% \documentclass[final,1p,times,twocolumn]{elsarticle}
+% \documentclass[final,1p,times,twocolumn]{elsarticle}
 %% \documentclass[final,3p,times]{elsarticle}
-%% \documentclass[final,3p,times,twocolumn]{elsarticle}
+% \documentclass[final,3p,times,twocolumn]{elsarticle}
 %% \documentclass[final,5p,times]{elsarticle}
-%% \documentclass[final,5p,times,twocolumn]{elsarticle}
+\documentclass[final,5p,times,twocolumn]{elsarticle}
 
@@
 %% please give \usepackage{epsfig}
-
 %% The amssymb package provides various useful mathematical symbols
@@
 %% \usepackage{amsthm}
-
-%% The lineno packages adds line numbers. Start line numbering with
-%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
-%% for the whole article with \linenumbers.
-%% \usepackage{lineno}
-
 \usepackage{subcaption} % subfigures
@@
 \usepackage{booktabs} % For tables
+\usepackage{lineno} % Line numbers
+% \linenumbers
 
@@
 
-\author[author1]{A. Hoover%
-% \thanks{Currently at Oak Ridge National Laboratory, Oak Ridge, Tennessee 37831, USA.} % This doesn't work!
-}
-\affiliation[author1]{organization={Department of Physics and Astronomy, University of Tennessee},
-            city={Knoxville},
-            state={Tennessee},
-            postcode={37996}, 
-            country={USA}}
-
-\author[author2]{N. J. Evans}
-
-\affiliation[author2]{organization={Oak Ridge National Laboratory},
-            addressline={One Bethel Valley Road}, 
-            city={Oak Ridge},
-            state={Tennessee},
-            postcode={37831}, 
-            country={USA}}
+\author{A. Hoover, N. J. Evans} 
+\address{Oak Ridge National Laboratory, One Bethel Valley Road, Oak Ridge, Tennessee, 37831, USA}
 
 \begin{abstract}
-A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance could mitigate space charge effects in circular accelerators and improve collider performance.
+A coasting hadron beam with an elliptical transverse profile, uniform charge density, and small transverse four-dimensional (4D) emittance could improve accelerator performance in several contexts.
 A phase space painting method to generate such a distribution is being tested in the Spallation Neutron Source (SNS) accumulator ring.
 A critical component of these efforts is to measure the 4D emittance of the beam.
-Reconstruction of the 4D emittance from wire-scanner data is a well-known technique.
-In this paper, we discuss the implementation of a variant of the multi-optics method using the four available wire-scanners near the SNS target, as well as the modification of the wire-scanner region to utilize the fixed-optics method — a method that is preferred due to its speed but can potentially lead to unacceptable bias and uncertainty in the reconstructed emittances.
-We then demonstrate the usefulness of the fixed-optics method by reconstructing the 4D emittance as a function of time during accumulation in the SNS ring.
+The 4D emittance can be reconstructed from measured beam profiles in two ways: in the multi-optics method, the optics between a reconstruction and measurement location are varied; in the fixed-optics method, multiple measurement locations are used without modifying the optics.
+The fixed-optics is much faster but can potentially lead to unacceptable bias and uncertainty in the reconstructed 4D emittance.
+In this paper, we discuss the implementation of a variant of the multi-optics method using the four available wire-scanners near the SNS target, as well as the modification of the wire-scanner region to utilize the fixed-optics method.
+We then demonstrate the usefulness of the fixed-optics method by reconstructing the 4D emittance evolution during accumulation in the SNS ring.
 \end{abstract}
@@
 
-%% \linenumbers
+% \footnotetext{Currently at Oak Ridge National Laboratory, Oak Ridge, Tennessee, 37831, USA.}
 
@@
 
-A hadron beam with a uniform charge density, elliptical transverse profile, and small four-dimensional (4D) emittance could mitigate space charge effects in circular accelerators and improve collider performance \cite{Danilov2003, Burov2002, Burov2013}.
-A phase space painting method to generate such a distribution is being tested in the Spallation Neutron Source (SNS) accumulator ring \cite{Holmes2018, Hoover2021}.
-A critical component of these efforts is to measure the 4D beam emittance.
+A coasting hadron beam with an elliptical transverse profile, uniform charge density, and small transverse four-dimensional (4D) emittance could improve accelerator performance in several contexts.
+First, such a beam could mitigate space charge effects in circular accelerators: the space charge force within the beam would depend linearly on the transverse coordinates, resulting in the minimum possible peak tune shift and zero tune spread \cite{Danilov2003}; at high intensities, a uniform charge density could suppress incoherent space charge resonances due to the lack of higher-order multipoles in the space charge potential; simulations indicate that these resonances can also be mitigated by decreasing the 4D beam emittance \cite{Cheon2022}.
+Second, a uniform density beam would be ideal for fixed-target applications where the peak density on the target is a concern \cite{Haines2014}.
+Third, a hadron beam with small 4D emittance could improve collider performance, mainly due to the possibility of rotating the beam in phase space such that the $x$-$y$ projection is completely flat, increasing the luminosity, but also due to the suppression of beam-beam effects \cite{Burov2002, Burov2013}.
+
+Danilov \cite{Danilov2003} proposed a method to generate such a distribution in a ring using phase space painting.
+Holmes \cite{Holmes2018} computationally investigated the feasibility of the method in the Spallation Neutron Source (SNS) ring.
+Efforts to implement and test the method in the SNS are ongoing.
+A critical component of these efforts is to measure the 4D beam emittance during accumulation in the ring.
 
@@
 The purpose of this work is to determine the limitations of the fixed-optics method in the SNS.
-The reconstruction method is reviewed in Section \ref{sec:Four-dimensional emittance measurement}; the implementation of the multi-optics and fixed-optics methods in the SNS is discussed in Section \ref{sec:Implementation in the SNS}; the fixed-optics method is demonstrated in Section \ref{sec:Example application} by measuring the 4D emittance as a function of time during accumulation in the SNS ring.
+The reconstruction method is reviewed in Section \ref{sec:Four-dimensional emittance measurement}; the implementation of the multi-optics and fixed-optics methods in the SNS is discussed in Section \ref{sec:Implementation in the SNS}; the fixed-optics method is demonstrated in Section \ref{sec:Example application} by measuring the 4D emittance evolution during accumulation in the SNS ring.
 
@@
 %
-The covariance matrix defines an ellipsoid from $\mathbf{x}^T \bm{\Sigma}^{-1} \mathbf{x} = 1$.
+The covariance matrix defines an ellipsoid in phase space from $\mathbf{x}^T \bm{\Sigma}^{-1} \mathbf{x} = 1$.
 The 4D emittance $\varepsilon_{4D}$ is proportional to the volume of this ellipsoid and is conserved in any linear focusing system \cite{Lebedev2010}; it is defined by
 %
-\begin{equation}
+\begin{equation}\label{eq:eps4D}
     \varepsilon_{4D} = \left|{\bm{\Sigma}}\right|^{1/2} = \varepsilon_1\varepsilon_2 \le \varepsilon_x\varepsilon_y,
@@
 where $|...|$ is the determinant.
-We have also defined the intrinsic emittances $\varepsilon_{1,2}$, which are individually conserved and found by a symplectic diagonalization of $\bm{\Sigma}$ \cite{Dragt2018}; i.e., they are the imaginary components of the eigenvalues of $\bm{\Sigma}\mathbf{U}$ with
+We have also introduced the intrinsic emittances $\varepsilon_{1,2}$, which are individually conserved and found by a symplectic diagonalization of $\bm{\Sigma}$ \cite{Dragt2018}; i.e., they are the imaginary components of the eigenvalues of $\bm{\Sigma}\mathbf{U}$ with
 %
@@
 %
-The apparent emittances $\varepsilon_x = \left|{\bm\sigma}_{xx}\right|^{1/2}$ and $\varepsilon_y = \left|{\bm\sigma}_{yy}\right|^{1/2}$ are conserved only in uncoupled linear focusing systems.
-The intrinsic and apparent emittances coincide in the absence of cross-plane correlations ($\bm{\sigma}_{xy} = 0$).
+The solution can be written in compact form \cite{Xiao2013}:
+%
+\begin{equation}\label{eq:eps12}
+    \varepsilon_{1,2} = \frac{1}{2}\sqrt{
+      -tr\left[(\bm{\Sigma} \mathbf{U})^2\right] \pm \sqrt{tr^2\left[(\bm{\Sigma} \mathbf{U})^2\right] - 16|{\bm{\Sigma}}|}
+    }
+\end{equation}
+%
+where $tr$ denotes the matrix trace.\footnote{Eq.~\eqref{eq:eps12} does not associate either intrinsic emittance with a specific rotational mode of the beam; instead, $\varepsilon_1$ and $\varepsilon_2$ are ordered by magnitude so that $\varepsilon_1 > \varepsilon_2$, regardless of the sign of the beam's angular momentum (or vorticity, more generally \cite{Groening2021}).
+We maintain this definition in this work but note that it is inconsistent with the following diagonal form of the covariance matrix:
+%
+\begin{equation}
+    \mathbf{\Sigma} = 
+    \mathbf{V} 
+    \begin{bmatrix}
+        \varepsilon_1 & 0 & 0 & 0 \\
+        0 & \varepsilon_1 & 0 & 0 \\
+        0 & 0 & \varepsilon_2 & 0 \\
+        0 & 0 & 0 & \varepsilon_2 \\
+    \end{bmatrix}
+    \mathbf{V}^T
+    \nonumber
+\end{equation}
+%
+where $\mathbf{V}$ is a symplectic matrix and each intrinsic emittance is associated with one mode.\label{fn:1}} The apparent emittances $\varepsilon_x = \left|{\bm\sigma}_{xx}\right|^{1/2}$ and $\varepsilon_y = \left|{\bm\sigma}_{yy}\right|^{1/2}$ are conserved only in uncoupled linear focusing systems and coincide with the intrinsic emittances in the absence of cross-plane correlations ($\bm{\sigma}_{xy} = 0$).
 
@@
 %
-\begin{equation}
+\begin{equation}\label{eq:lsq}
     \begin{bmatrix}
@@
 %
-where $\mathbf{A}$ is a function of $\mathbf{M}$.
-We repeat the measurement at least four times with different transfer matrices and solve the system using linear least squares (LLSQ).
+with \cite{Wolski2020}
+%
+\begin{equation}
+    \mathbf{A}^T = 
+    \begin{bmatrix}
+        M_{11}M_{11} & M_{11}M_{31} & M_{31}M_{31} \\
+        2M_{11}M_{12} & M_{12}M_{31} + M_{11}M_{32} & 2M_{31}M_{32} \\
+        2M_{11}M_{13} & M_{13}M_{31} + M_{11}M_{33} & 2M_{31}M_{33} \\
+        2M_{11}M_{14} & M_{14}M_{31} + M_{11}M_{34} & 2M_{31}M_{34} \\
+        M_{12}M_{12} & M_{12}M_{32} & M_{32}M_{32} \\
+        2M_{12}M_{13} & M_{13}M_{32} + M_{12}M_{33} & 2M_{32}M_{33} \\
+        2M_{12}M_{14} & M_{14}M_{32} + M_{12}M_{34} & 2M_{32}M_{34} \\
+        M_{13}M_{13} & M_{13}M_{33} & M_{33}M_{33} \\
+        2M_{13}M_{14} & M_{14}M_{33} + M_{13}M_{34} & 2M_{33}M_{34} \\
+        M_{14}M_{14} & M_{14}M_{34} & M_{34}M_{34}
+    \end{bmatrix}
+\end{equation}
+%
+where $M_{ij}$ is the element in row $i$ and column $j$ of the transfer matrix $\mathbf{M}$.
+The ten unique elements of $\mathbf{\Sigma}_a$ are obtained by repeating the measurement at least four times with different transfer matrices and computing the linear least squares (LLSQ) solution to the resulting system of equations.
 The transfer matrix elements can be modified by varying the optics, which we refer to as the multi-optics method, or by varying the measurement location, which we refer to as the fixed-optics method.
@@
 
-The real space moments of an accumulated beam in the SNS can be meausred using four wire-scanners — labeled WS20, WS21, WS23, and WS24 — in the ring-target beam transport (RTBT) section of the machine \cite{Henderson2014}.
-The wire-scanners are run in parallel and take approximately five minutes to move across the beam and return to their original positions.
-Their step size is 3 mm and their dynamic range is approximately $100$.
-They are run at a beam pulse frequency of 1 Hz.\footnote{Each data point corresponds to a separate beam pulse, so the measurement relies on pulse-to-pulse stability.} Each wire-scanner has three wires to measure the 1D projection of the distribution onto the $x$, $y$ and $u$ axes, where $u$ is tilted at an angle $\phi = \pi / 4$ above the $x$ axis; $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$ can be extracted from these projections, as well as $\langle{xy}\rangle$ from
+\subsection{SNS facility and diagnostics}
+
+The SNS produces short neutron pulses by colliding a proton beam with a liquid mercury target.
+The beam starts as a continuous wave of H$^-$ ions which is chopped and then bunched in a 402.5 MHz radio-frequency quadrupole (RFQ), forming microsecond-long minipulses.
+Each minipulse is accelerated in a linac to a kinetic energy of 1 GeV, stripped of its electrons using a carbon foil, and injected into a ring.
+Approximately one thousand minipulses are accumulated in the ring over $10^{-3}$ seconds.
+Finally, the proton beam is extracted and guided through the ring-target beam transport line (RTBT) to the target.
+This process repeats sixty times per second, resulting in an average beam power of 1.5 megawatts.
+A comprehensive description of the SNS is given in \cite{Henderson2014}; several design parameters of the SNS ring and RTBT are listed in Table~\ref{tab:SNS}; an overhead view of the ring and RTBT is shown in Fig.~\ref{fig:1}.
+
+%
+\begin{table}[!b]
+    \centering
+    \begin{tabular}{ll}
+        \toprule
+        {Quantity} & {Value} \\
+        \midrule
+        Ring length & 248 [m] \\
+        RTBT length & 151 [m] \\
+        Beam kinetic energy & 1 [GeV] \\
+        Average beam power & 1.4 [MW] \\
+        Repetition rate & 60 [Hz] \\
+        Transverse tunes ($\nu_x$, $\nu_y$) & (6.23, 6.20) \\
+        Longitudinal tune & $7 \times 10^{-4}$ \\
+        \midrule 
+    \end{tabular}
+    \caption{Several design parameters of the SNS ring and RTBT.}
+    \label{tab:SNS}
+\end{table}
+%
+
+Diagnostics in the SNS ring are limited to beam position and loss monitors.
+Beam profile measurements are performed in the RTBT using four wire-scanners, labeled WS20, WS21, WS23, and WS24, the locations of which are shown in Fig.~\ref{fig:1}.
+Each wire-scanner consists of three 100$\mu m$-thick tungsten wires mounted on a fork at forty-five degree angles relative to each other.
+The intensity of secondary electron emission from each wire is recorded as the fork moves across the beam, thus measuring the 1D projection of the beam distribution onto the $x$, $y$ and $u$ axes, where $u$ is tilted 45 degrees above the $x$ axis.
+The second-order moments $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$ are estimated from the profiles by averaging over the wire positions weighted by the signal amplitude.
+The cross-plane moment $\langle{xy}\rangle$ is thus measured indirectly: if the tilt angle of the $u$ axis is $\phi$, then $u = x\cos\phi + y\sin\phi$ and
 %
 \begin{equation}
-    \langle{xy}\rangle = \frac{\langle{uu}\rangle - \langle{xx}\rangle \cos^2\phi - \langle{yy}\rangle \sin^2\phi}{2\sin\phi\cos\phi}
-    .
+    \langle{xy}\rangle = \frac{\langle{uu}\rangle - \langle{xx}\rangle \cos^2\phi - \langle{yy}\rangle \sin^2\phi}{2\sin\phi\cos\phi}.
 \end{equation}
 %
-The wire-scanner locations, quadrupole locations, and nominal optical functions at the end of the RTBT are shown in Fig.~\ref{fig:1}.
-
+The wire-scanners are run in parallel, taking approximately five minutes to move across the beam and return to their original positions.
+Their step size is 3 mm and their dynamic range (the ratio of maximum to minimum measured signal) is approximately $100$.\footnote{The root-mean-square beam sizes may depend on beam tails/halo that cannot be measured by the RTBT wire-scanners.
+Investigation into the effect of beam halo on emittance measurements in the RTBT is left as future work.} They are run at a beam pulse frequency of 1 Hz.\footnote{Each data point corresponds to a separate beam pulse, so the measurement relies on pulse-to-pulse stability.}
 %
-\begin{figure*}[]
+\begin{figure*}[!t]
     \centering
-    \raisebox{20pt}{\includegraphics[width=0.71\columnwidth]{fig1a.pdf}
-    \hspace{1cm}}
-    \includegraphics[width=1.2\columnwidth]{fig1b.pdf}
-    \caption{The wire-scanner region of the ring-target beam transport (RTBT) section of the SNS. The red box indicates where the measurement takes place.}
+    \begin{subfigure}{0.375\columnwidth}
+        % \raisebox{20pt}{\includegraphics[width=\textwidth]{fig1a.pdf}}
+        \includegraphics[width=\textwidth]{fig1a.pdf}
+    \end{subfigure}
+    % \hspace{1cm}}
+    \begin{subfigure}{0.61\columnwidth}
+        \includegraphics[width=\textwidth]{fig1b.pdf}
+    \end{subfigure}
+    \caption{Left: The accumulator ring and ring-target-beam-transport (RTBT) sections of the Spallation Neutron Source (SNS).
+Right: $\beta$ functions (top), phase advances (middle), and focusing element and wire-scanner positions (bottom) in the second half of the RTBT.
+The red box outlines the wire-scanner region.}
     \label{fig:1}
@@
 
-We first implemented a variant of the multi-optics method.
-There is considerable freedom in the choice of optics since two degrees of freedom are present.
-In 2D emittance measurements, the phase advance from the reconstruction location to the measurement location is typically varied uniformly within a $180\degree$ range.\footnote{Intuitively, the error is expected to be minimized when the projection angles are spread uniformly between 0 and $\pi$; however, the projection angles are only equal to the phase advances in normalized phase space \cite{Hock2011}.
-Nonetheless, it is often convenient to vary the phase advances instead of the projection angles.} Prat and Aiba \cite{Prat2014} applied this strategy to the 4D emittance measurement: in the first half of the scan, the horizontal phase advance was varied while the vertical phase advance was held fixed; in the second half of the scan, the vertical phase advance was varied while the horizontal phase advance was held fixed.
+\subsection{Multi-optics method}
+
+We first implemented a variant of the multi-optics method in the SNS.
+There is considerably more freedom in the choice of optics used in the 4D reconstruction than in 2D reconstruction.
+We do not consider the general case of coupled optics in this work since the RTBT optics are uncoupled.
+Thus, the problem reduces to sampling the space of horizontal/vertical phase advances from the reconstruction location to the measurement location such that the measurement error is minimized.\footnote{
+    In 2D reconstructions, the phase advance from the reconstruction location to the measurement location is typically varied uniformly within a $180\degree$ range.
+The error is expected to be minimized when the projection angles are spread uniformly between 0 and $\pi$ (the projection angles are only equal to the phase advances in normalized phase space, but it is often convenient to vary the phase advances instead) \cite{Hock2011}.
+A clear geometric argument is based on the fact that the measured beam sizes define a set of lines that bound an ellipse in 2D phase space at the reconstruction location, so the reconstruction error will be minimized if these lines are evenly distributed around the ellipse.
+But this argument is less clear in a 4D reconstruction: the measurements of $\left\{\langle{xx}\rangle, \langle{yy}\rangle, \langle{xy}\rangle\right\}$ define a set of surfaces that bound an ellipsoid in 4D phase space at the reconstruction location, and it is not entirely clear how to "evenly distribute" these surfaces around the ellipsoid.
+} We chose to follow Prat and Aiba \cite{Prat2014}: in the first half of the scan, the horizontal phase advance is varied while the vertical phase advance is held fixed; in the second half of the scan, the vertical phase advance is varied while the horizontal phase advance is held fixed.
 Since the four SNS wire-scanners are already spaced somewhat evenly in phase advance, maximal phase coverage is possible by varying the phase advances at each wire-scanner in a $30\degree$ window; however, control of the phase advances between each wire-scanner is limited due to the shared power supplies of the RTBT quadrupoles.
-There are two power supplies in the wire-scanner region — one controls \{QH18, QH20, QH22, QH24\} and the other controls \{QH19, QH21, QH23, QH25\} — while the last five quadrupoles are controlled independently.
+There are two power supplies in the wire-scanner region — one controls \{QH18, QH20, QH22, QH24\} and the other controls \{QV19, QV21, QV23, QV25\} — while the last five quadrupoles are controlled independently.
 In addition to these constraints, the $\beta$ functions must be kept small in the wire-scanner region and must remain close to their nominal values at the target.
@@
 %
-The quadrupole strengths are contained in the vector $\mathbf{g}$; the calculated phase advances are $\bm{\mu} = (\mu_x, \mu_y)$; the desired phase advances are $\tilde{\bm{\mu}} = (\tilde{\mu}_x, \tilde{\mu}_y)$; the maximum calculated $\beta$ functions in the wire-scanner region are $\bm{\beta}_{max} = (\beta_{x_{max}}, \beta_{y_{max}})$; the maximum allowed $\beta$ functions in the wire-scanner region are $\tilde{\bm{\beta}}_{max} = (\tilde{\beta}_{x_{max}}, \tilde{\beta}_{y_{max}})$; $\epsilon$ is a constant.
+The quadrupole strengths are contained in the vector $\mathbf{g}$; the calculated phase advances are $\bm{\mu} = (\mu_x, \mu_y)$; the desired phase advances are $\tilde{\bm{\mu}} = (\tilde{\mu}_x, \tilde{\mu}_y)$; the maximum calculated $\beta$ functions in the wire-scanner region are $\bm{\beta}_{max} = (\beta_{x_{max}}, \beta_{y_{max}})$; the maximum allowed $\beta$ functions in the wire-scanner region are $\tilde{\bm{\beta}}_{max} = (\tilde{\beta}_{x_{max}}, \tilde{\beta}_{y_{max}})$; $\epsilon$ is a hand-tuned constant.
 After this process is completed, the remaining five quadrupoles before the target are used to constrain the beam size at the target.
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig2.pdf}
+    \includegraphics[width=0.65\columnwidth]{fig2.pdf}
     % \par\medskip
@@
 %
-The uncertainties in the parameters were calculated by propagating the standard deviations of the ten reconstructed moments obtained from the linear least squares (LLSQ) estimator.\footnote{See Appendix A of \cite{Faus-Golfe2016}.} The reconstructed Twiss parameters are close to the model parameters computed from the linear transfer matrices of the ring and RTBT, showing that the beam was matched to the nominal optics when it was extracted from the ring.
+The uncertainties in the parameters were calculated by propagating the standard deviations of the ten reconstructed moments obtained from the LLSQ estimator \cite{Faus-Golfe2016}.
+The reconstructed Twiss parameters are close to the model parameters computed from the linear transfer matrices of the ring and RTBT, showing that the beam was matched to the nominal optics when it was extracted from the ring.
 The intrinsic emittances are almost equal to the apparent emittances, showing that there was very little cross-plane correlation in the beam.
@@
 They considered errors in the measured moments, quadrupole field and alignment errors, beam energy errors, beam mismatch at the reconstruction point, and dispersion/chromaticity \cite{Mostacci2012}, concluding that the method remained accurate and reporting $< 5\%$ uncertainty in the intrinsic emittances.
-We initially performed similar studies using envelope tracking to estimate the reconstruction errors in the RTBT, also concluding that method should remain accurate \cite{Hoover2021-IPAC}.
-From repeated wire-scanner measurements with the same machine setup, we estimated the error in the measured moments to be only 3\%, and none of the other sources of uncertainty were found to have a large effect on the reconstructed emittances.
-Space charge forces, which can render the method invalid for high-perveance beams \cite{Anderson2002}, can be neglected since the space charge tune shift in the ring is around 3\% and the distance between the reconstruction and measurement locations is much smaller than the ring length.
+We initially performed similar studies using envelope tracking to estimate the reconstruction errors in the RTBT \cite{Hoover2021-IPAC}.
+We considered uncertainty in the beam moments ($\pm 5\%$) quadrupole tilt angles ($\pm\%$ 1 mrad), quadrupole field strengths ($\pm$ 1\%), beam kinetic energy ($\pm$ 3 MeV for a 1 GeV beam), and beam Twiss parameters at the reconstruction point ($\pm$ 5\%), with all other effects turned off.
+The emittances were successfully reconstructed with systematic and random errors of a few percent.
+Most of these uncertainties had only a small affect on the reconstructed intrinsic emittances, with the largest coming from beam mismatch and errors in the measured beam size.
+Therefore, we only consider these sources of uncertainty going forward.\footnote{Space charge forces, which can render the method invalid for high-perveance beams \cite{Anderson2002}, can be neglected since the space charge tune shift in the ring is around 3\% and the distance from the reconstruction location to the measurement location is much less than the length of the ring.} From repeated wire-scanner measurements with the same machine setup (see Fig.~\ref{fig:3}), we estimated the error in the measured moments to be only 3\%.
+%
+\begin{figure}
+    \centering
+    \includegraphics[width=0.5\textwidth]{profiles.pdf}
+    \caption{Measured profiles of a production beam at WS20 in the RTBT.}
+    \label{fig:3}
+\end{figure}
+%
 
-In summary, the multi-optics emittance measurement is feasible in the SNS.
-The only downside is the long measurement time, for the following reasons.
-First, we are not only interested in the beam emittances at a single time but are also interested in the growth and evolution of the emittances throughout accumulation.
-For example, it could be possible for $\varepsilon_2$ to remain small (as desired) in the first half of accumulation before growing to a much larger value in the second half of accumulation.
-Measurement of this emittance evolution would convey valuable information about the beam dynamics and allow qualitative comparison with computer simulation.
+\subsection{Fixed-optics method}
+
+Th downside of the multi-optics method is its long execution time, for the following reasons.
+First, we are not only interested in the beam emittances at a single time but are also interested in the emittance evolution throughout accumulation, which conveys valuable information about the beam dynamics and allows qualitative comparison with computer simulation.
 Second, it would be beneficial to quickly evaluate various machine states: although computer simulation can be used as a guide in choosing the experimental parameters, online tuning is expected to be necessary since small changes to the accelerator may have large effects on the painted phase space distribution.
-Third, the time reserved for accelerator physics experiments at the SNS is limited, and the setup for our initial experiments will take longer than usual due to the modification of the beam energy.
+Third, the time reserved for accelerator physics experiments at the SNS is limited, and our initial experiments will require substantial setup time due to modification of the beam energy.
 Thus, the fixed-optics method is preferred.
@@
 (We ignored any uncertainty in the transfer matrix elements, which were expected to be small.) This resulted in a large fraction of failed trials, but some successful trials.
-Fig.~\ref{fig:3} shows the emittances in the successful trials.
+Fig.~\ref{fig:4} shows the emittances in the successful trials.
 %
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig3.pdf}
+    \includegraphics[width=0.5\columnwidth]{fig3.pdf}
     \caption{Simulated emittance measurement using the nominal optics in the RTBT.}
-    \label{fig:3}
+    \label{fig:4}
 \end{figure}
@@
 Woodley and Emma proposed to abandon the fixed-optics method due to the bias in the intrinsic emittances introduced by large errors in the measured moments, suggesting to instead measure the apparent emittances and iteratively minimize $\varepsilon_y$.
-Agapov, Blair, and Woodley revisited this problem and showed that the linear system used to reconstruct the cross-plane moments can easily become ill-conditioned, and hence very sensitive to errors in the measured moments, suggesting the use of the condition number $C = |\mathbf{A}| |\mathbf{A}^{-1} |$ to characterize the sensitivity, where $| \dots |$ is a matrix norm \cite{Golub1985}.
+Agapov, Blair, and Woodley revisited this problem and showed that the linear system used to reconstruct the cross-plane moments can easily become ill-conditioned, and hence very sensitive to errors in the measured moments, suggesting the use of the condition number $C = |\mathbf{A}| |\mathbf{A}^{-1} |$, where $| \dots |$ is a matrix norm \cite{Golub1985} and $\mathbf{A}$ is defined in Eq.~\eqref{eq:lsq}, to characterize the sensitivity.
 Faus-Golfe et al.
@@
 The mean and standard deviation of the emittances were calculated over the successful trials.
-The difference between the mean emittances and the true emittances, which we refer to as the \textit{bias}, is plotted for each set of optics in the top row of Fig.~\ref{fig:4}, as well as the standard deviations in the bottom row.
+The difference between the mean emittances and the true emittances, which we refer to as the \textit{bias}, is plotted for each set of optics in the top row of Fig.~\ref{fig:5}, as well as the standard deviations in the bottom row.
 %
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig4.pdf}
+    \includegraphics[width=0.5\columnwidth]{fig4.pdf}
     \caption{Simulated bias and standard deviation of the intrinsic emittances in the RTBT as a function of the phase advances at WS24.}
-    \label{fig:4}
+    \label{fig:5}
 \end{figure}
@@
 %
-\begin{figure*}[]
+\begin{figure*}[t!]
     \centering
-    \includegraphics[width=0.92\textwidth]{fig5.pdf}
-    \caption{Bias and standard deviation of $\varepsilon_1$ (pink) and $\varepsilon_2$ (blue) from simulated reconstructions in the RTBT.
-In each plot, the collection of points is generated by varying the initial beam Twiss parameters.
-The true values of the emittances are printed on the top of the figures.}
-    \label{fig:5}
+    \begin{subfigure}[b]{0.92\textwidth}
+       \includegraphics[width=\linewidth]{fig5.pdf}
+       \caption{}
+       \label{fig:6a} 
+    \end{subfigure}
+    \begin{subfigure}[b]{0.92\textwidth}
+       \includegraphics[width=\linewidth]{fig5b.pdf}
+       \caption{}
+       \label{fig:6b}
+    \end{subfigure}
+    \caption{(a) Bias and standard deviations of $\varepsilon_1$ (pink) and $\varepsilon_2$ (blue) from simulated reconstructions in the RTBT as the beam Twiss parameters $\left\{\alpha_x, \alpha_y, \beta_x, \beta_y\right\}$ are scanned within a four-dimensional grid around their nominal values (as defined by the lattice).
+Each point in each subfigure corresponds to a simulation with the same beam emittances but different Twiss parameters.
+The beam emittances are fixed in each column, varying from no cross-plane correlation on the far left to large cross-plane correlation on the far right.
+(b) For each subfigure in (a), from left to right, we plot the distribution of intrinsic emittances generated by the random trials for one set of Twiss parameters (grey scale).
+Each blue shaded band is centered at the mean of the distribution one axis, with a width equal to twice the standard deviation along that axis.
+The red lines show the true values of the emittances.}
+    \label{fig:6}
 \end{figure*}
@@
     \end{tabular}
-    \caption{Measured mismatch in the RTBT.}
+    \caption{Measured and model Twiss values in the RTBT.}
     \label{tab:mismatch}
@@
 To examine the effect of mismatch, we first moved the operating point to $\mu_x = \mu_{x0} + 45\degree$, $\mu_y = \mu_{y0} - 45\degree$, then varied $\beta_x$ and $\beta_y$ within a $\pm 20\%$ window around their model values, $\alpha_x$ within a $\pm 15\%$ window, and $\alpha_y$ within a $-40\%, +10\%$ window to extend beyond the measured discrepancies, and repeated the Monte Carlo trials for each initial beam, producing a collection of means and standard deviations for the reconstructed intrinsic emittances.
-The left plot in Fig.~\ref{fig:5} displays the standard deviations and biases for $\varepsilon_1$ (pink) and $\varepsilon_2$ (blue).
+The left plot in Fig.~\ref{fig:6a} displays the standard deviations and biases for $\varepsilon_1$ (pink) and $\varepsilon_2$ (blue).
 
 Although most of the points are clustered near the original bias and standard deviation of 7\% and 5\%, respectively, the bias increases to nearly 15\% in some cases, which may make it difficult to resolve weak cross-plane correlation; however, the measurement should still resolve strong cross-plane correlation.
-This is demonstrated in the rest of the plots in Fig.~\ref{fig:5}, in which the entire process is repeated with $\varepsilon_1 / \varepsilon_2 > 1$.
+This is demonstrated in the rest of the plots in Fig.~\ref{fig:6}a, in which the entire process is repeated with $\varepsilon_1 / \varepsilon_2 > 1$.
 The bias in the reconstruction quickly decreases — the emittances are clustered around their true values.
-We conclude that with small modifications to the RTBT optics, the fixed-optics method should be sufficient for fast 4D emittance measurements in the SNS.
+We conclude that with modifications to the RTBT optics, the fixed-optics method should be sufficient for four-dimensional emittance measurements in the SNS.
+
+(The explanation for the dependence of the bias on the cross-plane correlation in the beam is the following: The perturbations applied to the covariance matrix in our random trials produce only small changes to the reconstructed apparent emittances.
+If the reconstructed apparent emittances are assumed to be constant over the trials, the 4D emittance is bounded from above by $\varepsilon_1\varepsilon_2 \le \varepsilon_x\varepsilon_y$.
+If there is no cross-plane correlation in the beam so that $\varepsilon_1\varepsilon_2 = \varepsilon_x\varepsilon_y$ — as is the case in the left column of Fig.~\ref{fig:6a} — the mean of the distribution of 4D emittances will be less than the true value since $\varepsilon_1\varepsilon_2$ is always less than or equal to $\varepsilon_x\varepsilon_y$.
+If there is significant cross-plane correlation in the beam — as is the case in the right column of Fig.~\ref{fig:6a} — the 4D emittance has more freedom to increase or decrease without violating Eq.~\eqref{eq:eps4D} and may, therefore, be centered on the correct value.
+As discussed in Footnote~\ref{fn:1}, Eq.~\eqref{eq:eps12} orders the intrinsic emittances by magnitude; as a consequence of this ordering, as well as the constraint just discussed, $\varepsilon_1$ is bounded from below and $\varepsilon_2$ is bounded from above.
+This is evident in Fig.~\ref{fig:6b}, which plots the distribution of intrinsic emittances for one set of Twiss parameters from each plot in Fig.~\ref{fig:6a}.)
 
@@
 
-We now demonstrate the usefulness of the fixed-optics emittance measurement.
-For later comparison, we first measured a 1 GeV beam produced by standard correlated painting.
-The beam was accumulated over 500 injected turns and extracted and measured every 50 turns.
-The reconstructed emittances throughout accumulation are shown in Fig.~\ref{fig:6}a.
+We now demonstrate the use of the fixed-optics method to measure the intrinsic and apparent emittances of a beam during accumulation in the SNS ring.
+The purpose of this section is not to analyze the measurement results in any detail; rather, it is to demonstrate that the measurement is responsive to changes in the ring lattice and injection parameters.
+
+It is first necessary to describe our approach to assigning uncertainty, in the form of error bars, to the emittances reconstructed by the fixed optics method.
+Propagating the uncertainties in the reconstructed moments, as obtained from the LLSQ estimator, is not an option since no least-squares fit is performed — the cross-plane moments are exactly determined by the four measured profiles.
+Since the wire-scanners take over five minutes to measure the beam profiles, it is impossible to compute the mean and standard deviation over many trials.
+Our proposal is to use a similar approach as in the previous section: repeatedly perturb the measured moments in a 3\% range, each time reconstructing the covariance matrix and computing the emittances; compute the the mean and standard deviation of the emittances over all trials; plot an error bar centered at the mean, with a width equal to twice the standard deviation.
+
+We first display the measured emittance evolution of a 1 GeV beam produced by the standard SNS painting method.\footnote{The standard painting method is often referred to as "correlated painting".
+The distance between the injected and circulating beam is varied as the square root of time while the angle between the beams is fixed at zero.
+Note that "correlated painting" tends not to produce any cross-plane correlation in the beam.
+See \cite{Wang1999, Hotchi2020}.} The beam was accumulated over 500 injected turns; it was extracted and measured every 50 turns during accumulation.
+The reconstructed emittances throughout accumulation are shown in Fig.~\ref{fig:7}a.
 %
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig6.pdf}
+    \includegraphics[width=0.5\columnwidth]{fig6.pdf}
     \caption{Measured emittances vs.
 number of injected turns in the SNS ring.
-(a) correlated (production) painting at 1 GeV; (b) attempted elliptical painting at 1 GeV; (c)-(d) elliptical painting at 0.8 GeV.}
-    \label{fig:6}
+(a) correlated (production) painting at 1 GeV; (b) attempted elliptical painting at 1 GeV; (c)-(d) elliptical painting at 0.8 GeV.
+In (d), the painted beam size was increased and the beam intensity was decreased relative to (c).}
+    \label{fig:7}
 \end{figure}
@@
 As expected, the beam did not develop any significant cross-plane correlation.
-The error bar centers and widths were determined by repeating the reconstruction as 3\% noise was added to the measured moments, then computing the means and standard deviations of the emittances over these trials.
-(Using the uncertainties in the LLSQ fit parameters was not possible since the cross-plane moments were exactly determined by the four measured profiles.) The beam was essentially matched at the RTBT entrance, so bias in the measurement was not a concern.
+The beam Twiss parameters were essentially matched at the nominal optics at the RTBT entrance, so bias in the measurement was not a concern.
 
-Our ultimate goal is to generate a beam with a uniform charge density, elliptical transverse profile, and small 4D emittance.
-This can be accomplished using phase space painting: the working principle is to create elliptical modes in the ring — elliptical turn-by-turn trajectories of particles in the $x$-$y$ plane — and to inject particles into one of the modes, scaling the particle amplitudes with square root time-dependence.
-If the method works as intended, a uniform density ellipse with near-zero 4D emittance is maintained throughout accumulation.
-This technique, which we refer to as \textit{elliptical painting}, requires variation not only of the distance between the circulating and injected beams, but also of the angle between the beams.
+The rest of the figures repeat this measurement using a different painting method, which we now briefly describe.
+As mentioned in Section 1, our goal is to produce a beam with a uniform charge density, elliptical transverse profile, and small 4D emittance.
+A proposed method to generate such a distribution is called ``elliptical painting" \cite{Holmes2018}: the working principle is to generate elliptical modes in the ring — elliptical turn-by-turn trajectories of particles in the $x$-$y$ plane — and to inject particles into one of the modes, scaling the particle amplitudes with square root time-dependence.\footnote{The turn-by-turn trajectory of a particle in the $x$-$y$ plane is an ellipse if its phase space coordinates lie along an eigenvector of the ring transfer matrix.
+If there are no coupled elements in the ring, the eigenvectors correspond to uncoupled horizontal or vertical motion.
+In general, coupled elements must be used to create elliptical trajectories.
+However, there is special case in which the $x$ and $y$ tunes are equal; in this case, any vector is an eigenvector, so any initial phase space coordinates will result in elliptical modes.
+See \cite{Hoover2022-thesis}.} If the method works as intended, a uniform density ellipse with near-zero 4D emittance is maintained throughout accumulation.
+The key difference from the standard SNS painting scheme is is that the angles between the circulating and injected beams must changed during injection, not just the distances.
 We denote the distances as $x$ and $y$ and the angles as $x'$ and $y'$ in this section.
 The most promising painting path in the SNS is a line in the $x$-$y'$ plane with a slope chosen such that the apparent emittances are equal, resulting in an approximately circular distribution at the injection point.
-These injection parameters are measured and controlled using beam-position-monitor (BPM) waveforms in the ring and eight time-dependent injection kicker magnets \cite{Hoover2022-thesis}.
+These injection parameters are measured and controlled using beam-position-monitor (BPM) waveforms in the ring and eight time-dependent injection kicker magnets.
 
-An initial attempt to perform elliptical painting was carried out.
-The conditions were not ideal: First, due to hardware constraints, the required initial injection coordinates $x = x' = y = y' = 0$ could not be obtained at the nominal beam energy of 1 GeV.
-The closest possible coordinates were ($x$, $x'$, $y$, $y'$) = (10 mm, 0 mrad, 0 mm, 0 mrad), meaning that the initial distribution had have a hollow center and would not have a uniform charge density.
+Figures Fig.~\ref{fig:7}b represents an initial attempt to perform elliptical painting in the SNS ring.
+The conditions were not ideal: First, due to hardware constraints, the required initial injection coordinates $x = x' = y = y' = 0$ could not be obtained at the nominal beam energy of 1 GeV; the closest possible coordinates were ($x$, $x'$, $y$, $y'$) = (10 mm, 0 mrad, 0 mm, 0 mrad), meaning that the initial distribution had have a hollow center and would not have a uniform charge density.
 Second, the maximum $y'$ was quite small at 0.7 mrad, placing a limit on the vertical beam size.
-Third, because no coupled elements existed in the SNS ring, elliptical modes were generated by equating the horizontal and vertical tunes; it was expected that such a setup would be sensitive to the tune split and that nonlinearities would strongly influence the beam dynamics near the difference resonance $\nu_x \approx \nu_y$.
-Therefore, we did not expect the painted beam to approach the ideal case of uniform density and zero 4D emittance.
-Instead, we hoped for measurable deviations in the beam evolution when compared to the standard correlated painting method.
+Third, because no coupled elements existed in the SNS ring, elliptical modes were generated by equating the fractional parts of the horizontal and vertical tunes; it was expected that such a setup would be sensitive to the tune split and that nonlinearities would strongly influence the beam dynamics near the difference resonance $\nu_x \approx \nu_y$.
+Therefore, we did not expect the painted beam to approach the ideal case of zero 4D emittance.
+However, we note that the emittance evolution is significantly different than in Fig.~\ref{fig:7}a, and that the intrinsic emittances are not the same as the apparent emittances.
 
-The results of the attempt are displayed in Fig.~\ref{fig:6}b.
-The initial injected coordinates were ($x$, $x'$, $y$, $y'$) $\approx$ (10 mm, 0 mrad, 0 mm, 0 mrad) and the final injected coordinates were ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 0.7 mrad).
-The measured intrinsic emittances are significantly different than the apparent emittances.
-The twenty measurements in Fig.~\ref{fig:6}a and Fig.~\ref{fig:6}b, which were completed in less than two hours, allowed qualitative comparisons with computer simulation and were used to guide future experiments.
+Fig.~\ref{fig:7}c shows a second experiment in which the beam energy was lowered to 0.8 GeV, allowing initial injected coordinates $x \approx x' \approx y \approx y' \approx 0$, as required by the painting method, and final injection coordinates ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 1.1 mrad).
+Simulations predicted small cross-plane correlation in the beam, and although this was measured, it is on the order of the expected bias when the beam is significantly mismatched.\footnote{The beam Twiss parameters were more significantly mismatched at the RTBT entrance in this experiment, likely due to the increased space charge intensity, leading to larger uncertainties in the intrinsic emittances.} In Fig.~\ref{fig:7}d, the measurement was repeated for a larger beam size and smaller beam intensity, which simulations predicted would reduce the 4D emittance during accumulation.
+In this case, the differences between the intrinsic and apparent emittances is larger than any expected bias in the reconstruction.
 
-In Fig.~\ref{fig:6}c, we display the results of a second experiment in which the beam energy was lowered to 0.8 GeV, allowing initial injected coordinates $x \approx x' \approx y \approx y' \approx 0$ and final coordinates ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 1.1 mrad).
-The beam Twiss parameters were more significantly mismatched at the RTBT entrance in this experiment, likely due to the increased space charge intensity, leading to larger uncertainty in the intrinsic emittances.
-Simulations predicted small cross-plane correlation in the beam, and although this was measured, it is on the order of the expected bias when the beam is significantly mismatched.
-In Fig.~\ref{fig:6}d, the measurement was repeated for a larger beam size and smaller beam intensity, which simulations predicted would reduce the 4D emittance during accumulation.
-In this case, the differences between the intrinsic and apparent emittances cannot be explained by the expected bias in the reconstruction.
+As mentioned at the beginning of this section, a detailed discussion of the measured beam evolution is beyond the scope of this paper; our main emphasis is that the data in each plot in Fig.~\ref{fig:7} took approximately one hour to collect, which fits within the typical study periods at the SNS, and allowed for qualitative comparisons with computer simulation which can be used to guide future experiments.
+One example of such a comparison is found in Fig.~\ref{fig:8}, which shows a simulation of injection into the SNS ring with similar ring/injection parameters as Fig.~\ref{fig:7}d.
+%
+\begin{figure}[b!]
+    \centering
+    \includegraphics[width=0.5\textwidth]{sim_emittances_nux6.195_nuy6.18.png}
+    \caption{Simulated emittance evolution of with ring/injection parameters similar to those in the measurement in Fig.~\ref{fig:7}d.}
+    \label{fig:8}
+\end{figure}
+%
 
@@
 One critical component of efforts to generate a beam with small 4D emittance in the Spallation Neutron Source (SNS) is to measure the 4D emittance throughout accumulation.
-A variant of the multi-optics emittance reconstruction method was implemented using four available wire-scanners, but the fixed-optics method was not possible with the nominal machine optics: the probability of failed fits was large, and there was a significant bias in intrinsic emittances in the successful fits.
+A variant of the multi-optics emittance reconstruction method was implemented using four available wire-scanners in the ring-target-beam-transport (RTBT) section of the SNS, after the beam is extracted from the ring; however, the fixed-optics reconstruction method was not possible with the nominal machine optics: the probability of failed fits was large, and there was a significant bias in intrinsic emittances in the successful fits.
 Monte Carlo simulations were employed to select a new set of quadrupole strengths, eliminating the problem of failed fits and reducing the bias and uncertainty to acceptable values.
@@
 The effect of beam mismatch on the reconstruction accuracy was also studied by varying the initial beam parameters and repeating the Monte Carlo trials.
-The bias in the intrinsic emittances increased from 7\% to 12\%, making it difficult to resolve small cross-plane correlation; however, this bias disappeared when significant cross-plane correlation was present in the beam.
+This increased the bias in the reconstructed intrinsic emittances from 7\% to 12\%, making it difficult to measure small cross-plane correlation in the beam; however, this bias decreased when significant cross-plane correlation was present in the beam.
 Thus, we concluded that the fixed-optics method is sufficient for fast measurements of the intrinsic beam emittances in the SNS.
 
-Finally, the method was applied to initial experiments at the SNS.
-The fast measurement time allowed the intrinsic emittances to be measured throughout accumulation for several different painting methods.
-Significant differences in the intrinsic/apparent emittances were resolved.
-These results will be compared with simulations and used to guide future experiments.
+Finally, the method was applied to several initial experiments at the SNS.
+The decreased measurement time allowed the intrinsic emittances to be measured throughout accumulation for several different painting methods.
+Noticeable differences in the intrinsic/apparent emittances were measured, and the emittance evolution was qualitatively similar to simulated beam evolution.
+These results will be used to guide future experiments at the SNS.
 
@@
 The United States Government retains, and the publisher, by accepting the article for publication, acknowledges that the United States Government retains a nonexclusive, paid-up, irrevocable, world-wide license to publish or reproduce the published form of this manuscript, or allow others to do so, for United States Government purposes.
+
+\appendix
+\section{Clarification of experimental results}
+
+In this appendix, we offer two clarifications on the measurements in Fig.~\ref{fig:7}d.
+First, since the intrinsic emittances are complicated functions of the second-order beam moments, it is not always obvious how changes in the intrinsic emittances affect the beam distribution.
+Therefore, in Fig.~\ref{fig:corner}, we have plotted the 2D projections of the covariance ellipsoid for each measurement in Fig.~\ref{fig:7}d.
+The change in intrinsic emittances manifests in a tilting of the ellipses in planes other than $x$-$x'$ and $y$-$y'$.
+%
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=0.42\textwidth]{corner2.pdf}    \caption{2D projections of the reconstructed covariance ellipsoid as a function of turn number during injection in the SNS ring.
+The measured emittances are shown in Fig.~\ref{fig:7}d.}
+    \label{fig:corner}
+\end{figure}
+%
+%
+\begin{figure*}[!b]
+    \centering
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\linewidth]{eps_rand_2.pdf}
+        \caption{}
+        \label{fig:9a} 
+    \end{subfigure}
+    \hspace{0.4cm}
+    \begin{subfigure}{0.48\textwidth}
+        \includegraphics[width=\linewidth]{eps_rand_7.pdf}
+        \caption{}
+        \label{fig:9b}
+    \end{subfigure}
+    \caption{Emittance distribution used to produce the error bars in Fig.~\ref{fig:7}d at (a) 150 turns (b) 400 turns.
+The points were generated by reconstructing the covariance matrix from perturbations of the measured moments.
+The measured values are plotted in red.}
+    \label{fig:9}
+\end{figure*}
+%
+
+Second, Fig.~\ref{fig:9} displays the distribution of apparent and intrinsic emittances used to generate the error bars in Fig.~\ref{fig:7}d at turn 150 and turn 400.
+Again, these emittances were obtained by repeating the reconstruction as 3\% noise was added to the measured $\langle{xx}\rangle$, $\langle{yy}\rangle$ and $\langle{xy}\rangle$.
+Notice that in (a), when the cross-plane correlation is small, the mean of the distribution is not exactly equal to the measured emittances, leading to the asymmetric error bars in Fig.~\ref{fig:7}d.
 

### 2022-07-24 main.tex
Final edits

@@
 %% The amssymb package provides various useful mathematical symbols
+% \usepackage[margin=1in]{geometry}
 \usepackage{amssymb}
@@
 
-\title{Fixed-optics four-dimensional emittance measurement at the Spallation Neutron Source}
+\title{Four-dimensional emittance measurement at the Spallation Neutron Source}
 
@@
 A phase space painting method to generate such a distribution is being tested in the Spallation Neutron Source (SNS) accumulator ring.
-A critical component of these efforts is to measure the 4D emittance of the beam.
+A critical component of these efforts is to measure the 4D emittance of the beam during accumulation.
 The 4D emittance can be reconstructed from measured beam profiles in two ways: in the multi-optics method, the optics between a reconstruction and measurement location are varied; in the fixed-optics method, multiple measurement locations are used without modifying the optics.
-The fixed-optics is much faster but can potentially lead to unacceptable bias and uncertainty in the reconstructed 4D emittance.
-In this paper, we discuss the implementation of a variant of the multi-optics method using the four available wire-scanners near the SNS target, as well as the modification of the wire-scanner region to utilize the fixed-optics method.
+The fixed-optics method is faster but can lead to a large uncertainty in the reconstructed 4D emittance.
+In this paper, we implement a variant of the multi-optics method using the four available wire-scanners near the SNS target.
+We also modify the wire-scanner region to reduce the uncertainty of the fixed-optics method.
 We then demonstrate the usefulness of the fixed-optics method by reconstructing the 4D emittance evolution during accumulation in the SNS ring.
@@
 
-The available diagnostics in the SNS ring-target beam transport line (RTBT) are four wire-scanners that measure 1D projections of the distribution onto a horizontal, vertical, and diagonal axis in the transverse plane.
-The covariance matrix, and hence the root-mean-square emittances, can be reconstructed from at least four wire-scanner measurements with different transfer matrices connecting the measurement and reconstruction locations \cite{book:Minty2003}.\footnote{Reconstruction of the transverse phase space distribution is possible using 2D projections of the distribution on a screen \cite{Hock2013, Wang2019, Wolski2020}.
-This may be possible using the SNS target imaging system \cite{Blokland2010} but is not pursued here.} In general, the transfer matrix elements can be controlled by varying the machine optics (multi-optics method), the measurement location (fixed-optics method), or any combination of the two \cite{Prat2014}.
-With four available wire-scanners, the fixed-optics method is possible and preferred in our case due to its speed; however, previous studies have shown that the method can be sensitive to errors \cite{Raimondi1993, Woodley2000, Agapov2007, Faus-Golfe2016}.
+The covariance matrix of the transverse phase space distribution of the beam, and hence the root-mean-square emittances, can be reconstructed from 1D projections of the distribution onto a horizontal, vertical, and diagonal axis in the transverse plane \cite{book:Minty2003}.\footnote{
+    Reconstruction of the transverse phase space distribution is possible using 2D projections of the distribution on a screen \cite{Hock2013, Wang2019, Wolski2020}.
+This may be possible using the SNS target imaging system \cite{Blokland2010} but is not pursued here.
+}At least four measurements are required, each with a different linear transfer matrix connecting the phase space coordinates at the measurement location to the reconstruction location.
+The transfer matrix can be controlled by varying the machine optics (multi-optics method), the measurement location (fixed-optics method), or any combination of the two \cite{Prat2014}.
+The SNS has four wire-scanners available along the transfer line connecting the ring to the spallation target.
+Thus, the fixed-optics method is possible and preferred in our case due to its speed; however, previous studies have shown that the method can be sensitive to errors \cite{Raimondi1993, Woodley2000, Agapov2007, Faus-Golfe2016}.
 
-The purpose of this work is to determine the limitations of the fixed-optics method in the SNS.
-The reconstruction method is reviewed in Section \ref{sec:Four-dimensional emittance measurement}; the implementation of the multi-optics and fixed-optics methods in the SNS is discussed in Section \ref{sec:Implementation in the SNS}; the fixed-optics method is demonstrated in Section \ref{sec:Example application} by measuring the 4D emittance evolution during accumulation in the SNS ring.
+The purpose of this work is to optimize the 4D emittance measurement in the SNS.
+The general reconstruction method is reviewed in Section \ref{sec:Four-dimensional emittance measurement}.
+The first part of Section \ref{sec:Implementation in the SNS} details the available diagnostics in the SNS; the second part of Section \ref{sec:Implementation in the SNS} describes our implementation of a variant of the multi-optics method in the SNS; the third part of Section \ref{sec:Implementation in the SNS} describes our implementation of the fixed-optics method in the SNS, focusing on reducing the sensitivity to errors.
+Finally, the usefulness of the fixed-optics method is demonstrated in Section \ref{sec:Example application} by measuring the 4D emittance evolution during accumulation in the SNS ring.
 
@@
 Finally, the proton beam is extracted and guided through the ring-target beam transport line (RTBT) to the target.
-This process repeats sixty times per second, resulting in an average beam power of 1.5 megawatts.
+This process repeats sixty times per second, resulting in an average beam power of 1.4 megawatts.
 A comprehensive description of the SNS is given in \cite{Henderson2014}; several design parameters of the SNS ring and RTBT are listed in Table~\ref{tab:SNS}; an overhead view of the ring and RTBT is shown in Fig.~\ref{fig:1}.
+%
+\begin{figure*}[t!]
+    \centering
+    \begin{subfigure}{0.35\textwidth}
+        % \raisebox{20pt}{\includegraphics[width=\textwidth]{fig1a.pdf}}
+        \includegraphics[width=\textwidth]{fig1a.pdf}
+    \end{subfigure}
+    \hspace{0.25cm}
+    \begin{subfigure}{0.615\textwidth}
+        \includegraphics[width=\textwidth]{fig1b.pdf}
+    \end{subfigure}
+    \caption{Left: The accumulator ring and ring-target-beam-transport (RTBT) sections of the Spallation Neutron Source (SNS).
+Right: $\beta$ functions (top), phase advances (middle), and focusing element and wire-scanner positions (bottom) in the second half of the RTBT.
+The red box outlines the wire-scanner region.}
+    \label{fig:1}
+\end{figure*}
+%
 
@@
         \toprule
-        {Quantity} & {Value} \\
+        \textbf{Quantity} & \textbf{Value} \\
         \midrule
@@
 Beam profile measurements are performed in the RTBT using four wire-scanners, labeled WS20, WS21, WS23, and WS24, the locations of which are shown in Fig.~\ref{fig:1}.
-Each wire-scanner consists of three 100$\mu m$-thick tungsten wires mounted on a fork at forty-five degree angles relative to each other.
-The intensity of secondary electron emission from each wire is recorded as the fork moves across the beam, thus measuring the 1D projection of the beam distribution onto the $x$, $y$ and $u$ axes, where $u$ is tilted 45 degrees above the $x$ axis.
+Each wire-scanner consists of three 100$\mu m$-thick tungsten wires mounted on a fork at forty-five-degree angles relative to each other.
+The intensity of secondary electron emission from each wire is recorded as the fork moves across the beam, thus measuring the 1D projection of the beam distribution onto the $x$, $y$, and $u$ axes, where $u$ is tilted 45 degrees above the $x$ axis.
 The second-order moments $\langle{xx}\rangle$, $\langle{yy}\rangle$, and $\langle{uu}\rangle$ are estimated from the profiles by averaging over the wire positions weighted by the signal amplitude.
@@
 The wire-scanners are run in parallel, taking approximately five minutes to move across the beam and return to their original positions.
-Their step size is 3 mm and their dynamic range (the ratio of maximum to minimum measured signal) is approximately $100$.\footnote{The root-mean-square beam sizes may depend on beam tails/halo that cannot be measured by the RTBT wire-scanners.
+Their default step size is 3 mm and their dynamic range (the ratio of maximum to minimum measured signal) is approximately $100$.\footnote{The root-mean-square beam sizes may depend on beam tails/halo that cannot be measured by the RTBT wire-scanners.
 Investigation into the effect of beam halo on emittance measurements in the RTBT is left as future work.} They are run at a beam pulse frequency of 1 Hz.\footnote{Each data point corresponds to a separate beam pulse, so the measurement relies on pulse-to-pulse stability.}
-%
-\begin{figure*}[!t]
-    \centering
-    \begin{subfigure}{0.375\columnwidth}
-        % \raisebox{20pt}{\includegraphics[width=\textwidth]{fig1a.pdf}}
-        \includegraphics[width=\textwidth]{fig1a.pdf}
-    \end{subfigure}
-    % \hspace{1cm}}
-    \begin{subfigure}{0.61\columnwidth}
-        \includegraphics[width=\textwidth]{fig1b.pdf}
-    \end{subfigure}
-    \caption{Left: The accumulator ring and ring-target-beam-transport (RTBT) sections of the Spallation Neutron Source (SNS).
-Right: $\beta$ functions (top), phase advances (middle), and focusing element and wire-scanner positions (bottom) in the second half of the RTBT.
-The red box outlines the wire-scanner region.}
-    \label{fig:1}
-\end{figure*}
-%
 
@@
 We do not consider the general case of coupled optics in this work since the RTBT optics are uncoupled.
-Thus, the problem reduces to sampling the space of horizontal/vertical phase advances from the reconstruction location to the measurement location such that the measurement error is minimized.\footnote{
+Thus, the problem reduces to sampling the space of horizontal/vertical phase advances from the reconstruction location to the measurement location such that the reconstruction error is minimized.\footnote{
     In 2D reconstructions, the phase advance from the reconstruction location to the measurement location is typically varied uniformly within a $180\degree$ range.
@@
     \centering
-    \includegraphics[width=0.65\columnwidth]{fig2.pdf}
+    \includegraphics[width=\columnwidth]{fig2.pdf}
     % \par\medskip
     \begin{tabular}{lll}
-        \small\textbf{Parameter} & \small\textbf{Measurement} & \small\textbf{Model} \\
+        \small\textbf{Parameter} & \small\textbf{Measured} & \small\textbf{Model} \\
         % \midrule
@@
 The emittances were successfully reconstructed with systematic and random errors of a few percent.
-Most of these uncertainties had only a small affect on the reconstructed intrinsic emittances, with the largest coming from beam mismatch and errors in the measured beam size.
+Most of these uncertainties had only a small effect on the reconstructed intrinsic emittances, with the largest coming from beam mismatch and errors in the measured beam size.
 Therefore, we only consider these sources of uncertainty going forward.\footnote{Space charge forces, which can render the method invalid for high-perveance beams \cite{Anderson2002}, can be neglected since the space charge tune shift in the ring is around 3\% and the distance from the reconstruction location to the measurement location is much less than the length of the ring.} From repeated wire-scanner measurements with the same machine setup (see Fig.~\ref{fig:3}), we estimated the error in the measured moments to be only 3\%.
+This 3\% noise will be assumed throughout the rest of the analysis.
 %
@@
 
-Th downside of the multi-optics method is its long execution time, for the following reasons.
+The downside of the multi-optics method is its long execution time, for the following reasons.
 First, we are not only interested in the beam emittances at a single time but are also interested in the emittance evolution throughout accumulation, which conveys valuable information about the beam dynamics and allows qualitative comparison with computer simulation.
@@
 %
-\begin{figure}[]
+\begin{figure}[!b]
     \centering
-    \includegraphics[width=0.5\columnwidth]{fig3.pdf}
+    \includegraphics[width=\columnwidth]{fig3.pdf}
     \caption{Simulated emittance measurement using the nominal optics in the RTBT.}
@@
     \centering
-    \includegraphics[width=0.5\columnwidth]{fig4.pdf}
+    \includegraphics[width=\columnwidth]{fig4.pdf}
     \caption{Simulated bias and standard deviation of the intrinsic emittances in the RTBT as a function of the phase advances at WS24.}
@@
     \caption{(a) Bias and standard deviations of $\varepsilon_1$ (pink) and $\varepsilon_2$ (blue) from simulated reconstructions in the RTBT as the beam Twiss parameters $\left\{\alpha_x, \alpha_y, \beta_x, \beta_y\right\}$ are scanned within a four-dimensional grid around their nominal values (as defined by the lattice).
-Each point in each subfigure corresponds to a simulation with the same beam emittances but different Twiss parameters.
+Each point in each subfigure corresponds to a simulation with different Twiss parameters.
 The beam emittances are fixed in each column, varying from no cross-plane correlation on the far left to large cross-plane correlation on the far right.
-(b) For each subfigure in (a), from left to right, we plot the distribution of intrinsic emittances generated by the random trials for one set of Twiss parameters (grey scale).
+(b) For each subfigure in (a), from left to right, we plot the distribution of intrinsic emittances generated by the random trials for one set of Twiss parameters (greyscale).
 Each blue shaded band is centered at the mean of the distribution one axis, with a width equal to twice the standard deviation along that axis.
@@
         % \textbf{Parameter} & \textbf{Measured} & \textbf{Model} \\
-        Parameter & Measured & Model \\
+        \textbf{Parameter} & \textbf{Measured} & \textbf{Model} \\
         \midrule
@@
 The bias in the reconstruction quickly decreases — the emittances are clustered around their true values.
-We conclude that with modifications to the RTBT optics, the fixed-optics method should be sufficient for four-dimensional emittance measurements in the SNS.
+We conclude that with modifications to the RTBT optics, the fixed-optics method should be sufficient for faster (albeit less accurate) four-dimensional emittance measurements in the SNS.
 
@@
 Since the wire-scanners take over five minutes to measure the beam profiles, it is impossible to compute the mean and standard deviation over many trials.
-Our proposal is to use a similar approach as in the previous section: repeatedly perturb the measured moments in a 3\% range, each time reconstructing the covariance matrix and computing the emittances; compute the the mean and standard deviation of the emittances over all trials; plot an error bar centered at the mean, with a width equal to twice the standard deviation.
+We propose to use a similar approach as in the previous section: repeatedly perturb the measured moments in a 3\% range, each time reconstructing the covariance matrix and computing the emittances; compute the mean and standard deviation of the emittances over all trials; plot an error bar centered at the mean, with a width equal to twice the standard deviation.
 
@@
 The distance between the injected and circulating beam is varied as the square root of time while the angle between the beams is fixed at zero.
-Note that "correlated painting" tends not to produce any cross-plane correlation in the beam.
+Note that ``correlated painting" tends not to produce any cross-plane correlation in the beam.
 See \cite{Wang1999, Hotchi2020}.} The beam was accumulated over 500 injected turns; it was extracted and measured every 50 turns during accumulation.
@@
 %
-\begin{figure}[b!]
+\begin{figure}[t!]
     \centering
-    \includegraphics[width=0.5\columnwidth]{fig6.pdf}
+    \includegraphics[width=\columnwidth]{fig6.pdf}
     \caption{Measured emittances vs.
@@
 In general, coupled elements must be used to create elliptical trajectories.
-However, there is special case in which the $x$ and $y$ tunes are equal; in this case, any vector is an eigenvector, so any initial phase space coordinates will result in elliptical modes.
+However, there is a special case in which the $x$ and $y$ tunes are equal; in this case, any vector is an eigenvector, so any initial phase space coordinates will result in elliptical modes.
 See \cite{Hoover2022-thesis}.} If the method works as intended, a uniform density ellipse with near-zero 4D emittance is maintained throughout accumulation.
-The key difference from the standard SNS painting scheme is is that the angles between the circulating and injected beams must changed during injection, not just the distances.
+The key difference from the standard SNS painting scheme is that the angles between the circulating and injected beams must be changed during injection, not just the distances.
 We denote the distances as $x$ and $y$ and the angles as $x'$ and $y'$ in this section.
@@
 
-Figures Fig.~\ref{fig:7}b represents an initial attempt to perform elliptical painting in the SNS ring.
-The conditions were not ideal: First, due to hardware constraints, the required initial injection coordinates $x = x' = y = y' = 0$ could not be obtained at the nominal beam energy of 1 GeV; the closest possible coordinates were ($x$, $x'$, $y$, $y'$) = (10 mm, 0 mrad, 0 mm, 0 mrad), meaning that the initial distribution had have a hollow center and would not have a uniform charge density.
+Figure Fig.~\ref{fig:7}b represents an initial attempt to perform elliptical painting in the SNS ring.
+The conditions were not ideal: First, due to hardware constraints, the required initial injection coordinates $x = x' = y = y' = 0$ could not be obtained at the nominal beam energy of 1 GeV; the closest possible coordinates were ($x$, $x'$, $y$, $y'$) = (10 mm, 0 mrad, 0 mm, 0 mrad), meaning that the initial distribution would have a hollow center and would not have a uniform charge density.
 Second, the maximum $y'$ was quite small at 0.7 mrad, placing a limit on the vertical beam size.
@@
 Therefore, we did not expect the painted beam to approach the ideal case of zero 4D emittance.
-However, we note that the emittance evolution is significantly different than in Fig.~\ref{fig:7}a, and that the intrinsic emittances are not the same as the apparent emittances.
+However, we note that the emittance evolution is significantly different than in Fig.~\ref{fig:7} and that the intrinsic emittances are not the same as the apparent emittances.
 
 Fig.~\ref{fig:7}c shows a second experiment in which the beam energy was lowered to 0.8 GeV, allowing initial injected coordinates $x \approx x' \approx y \approx y' \approx 0$, as required by the painting method, and final injection coordinates ($x$, $x'$, $y$, $y'$) $\approx$ (21 mm, 0 mrad, 0 mm, 1.1 mrad).
-Simulations predicted small cross-plane correlation in the beam, and although this was measured, it is on the order of the expected bias when the beam is significantly mismatched.\footnote{The beam Twiss parameters were more significantly mismatched at the RTBT entrance in this experiment, likely due to the increased space charge intensity, leading to larger uncertainties in the intrinsic emittances.} In Fig.~\ref{fig:7}d, the measurement was repeated for a larger beam size and smaller beam intensity, which simulations predicted would reduce the 4D emittance during accumulation.
-In this case, the differences between the intrinsic and apparent emittances is larger than any expected bias in the reconstruction.
+Simulations predicted that a small cross-plane correlation would develop in the beam after a few hundred turns, and although this was measured, it is on the order of the expected bias.\footnote{The beam Twiss parameters were more significantly mismatched at the RTBT entrance in this experiment, likely due to the increased space charge intensity, leading to larger uncertainties in the intrinsic emittances.
+The measured Twiss parameters are listed in Table \ref{tab:mismatch}.} In Fig.~\ref{fig:7}d, the measurement was repeated for a larger beam size and lower beam intensity, which simulations predicted would reduce the 4D emittance during accumulation.
+In this case, the differences between the intrinsic and apparent emittances are larger than the expected bias in the reconstruction.
 
-As mentioned at the beginning of this section, a detailed discussion of the measured beam evolution is beyond the scope of this paper; our main emphasis is that the data in each plot in Fig.~\ref{fig:7} took approximately one hour to collect, which fits within the typical study periods at the SNS, and allowed for qualitative comparisons with computer simulation which can be used to guide future experiments.
+As mentioned at the beginning of this section, a detailed discussion of the measured beam evolution is beyond the scope of this paper.
+Our main emphasis is that the data represented in Fig.~\ref{fig:7} was collected in approximately four hours, fitting within two rarely-occurring beam study periods with long machine setup times, and allows qualitative comparisons with computer simulation which can be used to guide future experiments.
 One example of such a comparison is found in Fig.~\ref{fig:8}, which shows a simulation of injection into the SNS ring with similar ring/injection parameters as Fig.~\ref{fig:7}d.
 %
-\begin{figure}[b!]
+\begin{figure}[t!]
     \centering
-    \includegraphics[width=0.5\textwidth]{sim_emittances_nux6.195_nuy6.18.png}
+    \includegraphics[width=\columnwidth]{fig8.png}
     \caption{Simulated emittance evolution of with ring/injection parameters similar to those in the measurement in Fig.~\ref{fig:7}d.}
@@
 One critical component of efforts to generate a beam with small 4D emittance in the Spallation Neutron Source (SNS) is to measure the 4D emittance throughout accumulation.
-A variant of the multi-optics emittance reconstruction method was implemented using four available wire-scanners in the ring-target-beam-transport (RTBT) section of the SNS, after the beam is extracted from the ring; however, the fixed-optics reconstruction method was not possible with the nominal machine optics: the probability of failed fits was large, and there was a significant bias in intrinsic emittances in the successful fits.
+A variant of the multi-optics emittance reconstruction method was implemented using four available wire-scanners in the ring-target-beam-transport (RTBT) section of the SNS.
+The fixed-optics reconstruction method was not possible with the nominal machine optics: the probability of failed fits was large, and there was a significant uncertainty/bias in intrinsic emittances in the successful fits.
 Monte Carlo simulations were employed to select a new set of quadrupole strengths, eliminating the problem of failed fits and reducing the bias and uncertainty to acceptable values.
@@
 This increased the bias in the reconstructed intrinsic emittances from 7\% to 12\%, making it difficult to measure small cross-plane correlation in the beam; however, this bias decreased when significant cross-plane correlation was present in the beam.
-Thus, we concluded that the fixed-optics method is sufficient for fast measurements of the intrinsic beam emittances in the SNS.
+Thus, we concluded that the fixed-optics method is sufficient for faster (albeit less accurate) measurements of the intrinsic beam emittances in the SNS.
 
-Finally, the method was applied to several initial experiments at the SNS.
-The decreased measurement time allowed the intrinsic emittances to be measured throughout accumulation for several different painting methods.
-Noticeable differences in the intrinsic/apparent emittances were measured, and the emittance evolution was qualitatively similar to simulated beam evolution.
+Finally, the usefulness of the fixed-optics method was demonstrated by reconstructing the emittance evolution during accumulation in the SNS ring.
+As expected, standard SNS painting produced very little cross-plane correlation.
+Initial tests of "elliptical painting" revealed noticeable changes in the 4D emittance evolution in qualitative agreement with simulations with similar ring/injection parameters.
 These results will be used to guide future experiments at the SNS.
@@
 
-In this appendix, we offer two clarifications on the measurements in Fig.~\ref{fig:7}d.
-First, since the intrinsic emittances are complicated functions of the second-order beam moments, it is not always obvious how changes in the intrinsic emittances affect the beam distribution.
-Therefore, in Fig.~\ref{fig:corner}, we have plotted the 2D projections of the covariance ellipsoid for each measurement in Fig.~\ref{fig:7}d.
-The change in intrinsic emittances manifests in a tilting of the ellipses in planes other than $x$-$x'$ and $y$-$y'$.
 %
-\begin{figure}[t!]
-    \centering
-    \includegraphics[width=0.42\textwidth]{corner2.pdf}    \caption{2D projections of the reconstructed covariance ellipsoid as a function of turn number during injection in the SNS ring.
-The measured emittances are shown in Fig.~\ref{fig:7}d.}
-    \label{fig:corner}
-\end{figure}
-%
-%
-\begin{figure*}[!b]
+\begin{figure*}[!t]
     \centering
     \begin{subfigure}{0.48\textwidth}
-        \includegraphics[width=\linewidth]{eps_rand_2.pdf}
+        \includegraphics[width=\linewidth]{fig10a.pdf}
         \caption{}
-        \label{fig:9a} 
+        \label{fig:10a} 
     \end{subfigure}
@@
     \begin{subfigure}{0.48\textwidth}
-        \includegraphics[width=\linewidth]{eps_rand_7.pdf}
+        \includegraphics[width=\linewidth]{fig10b.pdf}
         \caption{}
-        \label{fig:9b}
+        \label{fig:10b}
     \end{subfigure}
@@
 The measured values are plotted in red.}
-    \label{fig:9}
+    \label{fig:10}
 \end{figure*}
 %
-
-Second, Fig.~\ref{fig:9} displays the distribution of apparent and intrinsic emittances used to generate the error bars in Fig.~\ref{fig:7}d at turn 150 and turn 400.
+%
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\columnwidth]{fig9.pdf}    \caption{2D projections of the reconstructed covariance ellipsoid as a function of turn number during injection in the SNS ring.
+The measured emittances are shown in Fig.~\ref{fig:7}d.}
+    \label{fig:9}
+\end{figure}
+%
+In this appendix, we offer two clarifications on the measurements in Fig.~\ref{fig:7}d.
+First, Fig.~\ref{fig:10} displays the distribution of apparent and intrinsic emittances used to generate the error bars in Fig.~\ref{fig:7}d at turn 150 and turn 400.
 Again, these emittances were obtained by repeating the reconstruction as 3\% noise was added to the measured $\langle{xx}\rangle$, $\langle{yy}\rangle$ and $\langle{xy}\rangle$.
 Notice that in (a), when the cross-plane correlation is small, the mean of the distribution is not exactly equal to the measured emittances, leading to the asymmetric error bars in Fig.~\ref{fig:7}d.
+
+Second, since the intrinsic emittances are complicated functions of the second-order beam moments, it is not always obvious how changes in the intrinsic emittances affect the beam distribution.
+Therefore, in Fig.~\ref{fig:9}, we have plotted the 2D projections of the covariance ellipsoid for each measurement in Fig.~\ref{fig:7}d.
+The change in intrinsic emittances manifests in a tilting of the ellipses in planes other than $x$-$x'$ and $y$-$y'$.
 

### 2022-07-24 main.tex
Rename figures

@@
     \centering
-    \includegraphics[width=0.5\textwidth]{profiles.pdf}
+    \includegraphics[width=0.5\textwidth]{fig3.pdf}
     \caption{Measured profiles of a production beam at WS20 in the RTBT.}
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig3.pdf}
+    \includegraphics[width=\columnwidth]{fig4.pdf}
     \caption{Simulated emittance measurement using the nominal optics in the RTBT.}
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig4.pdf}
+    \includegraphics[width=\columnwidth]{fig5.pdf}
     \caption{Simulated bias and standard deviation of the intrinsic emittances in the RTBT as a function of the phase advances at WS24.}
@@
     \begin{subfigure}[b]{0.92\textwidth}
-       \includegraphics[width=\linewidth]{fig5.pdf}
+       \includegraphics[width=\linewidth]{fig6a.pdf}
        \caption{}
@@
     \begin{subfigure}[b]{0.92\textwidth}
-       \includegraphics[width=\linewidth]{fig5b.pdf}
+       \includegraphics[width=\linewidth]{fig6b.pdf}
        \caption{}
@@
     \centering
-    \includegraphics[width=\columnwidth]{fig6.pdf}
+    \includegraphics[width=\columnwidth]{fig7.pdf}
     \caption{Measured emittances vs.
@@
     \begin{subfigure}{0.48\textwidth}
-        \includegraphics[width=\linewidth]{fig10a.pdf}
+        \includegraphics[width=\linewidth]{fig9a.pdf}
         \caption{}
-        \label{fig:10a} 
+        \label{fig:9a} 
     \end{subfigure}
@@
     \begin{subfigure}{0.48\textwidth}
-        \includegraphics[width=\linewidth]{fig10b.pdf}
+        \includegraphics[width=\linewidth]{fig9b.pdf}
         \caption{}
-        \label{fig:10b}
+        \label{fig:9b}
     \end{subfigure}
@@
 The measured values are plotted in red.}
-    \label{fig:10}
+    \label{fig:9}
 \end{figure*}
@@
 %
-\begin{figure}[t!]
+\begin{figure}[b!]
     \centering
-    \includegraphics[width=\columnwidth]{fig9.pdf}    \caption{2D projections of the reconstructed covariance ellipsoid as a function of turn number during injection in the SNS ring.
-The measured emittances are shown in Fig.~\ref{fig:7}d.}
-    \label{fig:9}
+    \includegraphics[width=\columnwidth]{fig10.pdf}    
+    \caption{2D projections of the reconstructed covariance ellipsoid as a function of turn number during injection in the SNS ring. The measured emittances are shown in Fig.~\ref{fig:7}d.}
+    \label{fig:10}
 \end{figure}
@@
 In this appendix, we offer two clarifications on the measurements in Fig.~\ref{fig:7}d.
-First, Fig.~\ref{fig:10} displays the distribution of apparent and intrinsic emittances used to generate the error bars in Fig.~\ref{fig:7}d at turn 150 and turn 400.
+First, Fig.~\ref{fig:9} displays the distribution of apparent and intrinsic emittances used to generate the error bars in Fig.~\ref{fig:7}d at turn 150 and turn 400.
 Again, these emittances were obtained by repeating the reconstruction as 3\% noise was added to the measured $\langle{xx}\rangle$, $\langle{yy}\rangle$ and $\langle{xy}\rangle$.
@@
 Second, since the intrinsic emittances are complicated functions of the second-order beam moments, it is not always obvious how changes in the intrinsic emittances affect the beam distribution.
-Therefore, in Fig.~\ref{fig:9}, we have plotted the 2D projections of the covariance ellipsoid for each measurement in Fig.~\ref{fig:7}d.
+Therefore, in Fig.~\ref{fig:10}, we have plotted the 2D projections of the covariance ellipsoid for each measurement in Fig.~\ref{fig:7}d.
 The change in intrinsic emittances manifests in a tilting of the ellipses in planes other than $x$-$x'$ and $y$-$y'$.

### 2022-07-24 main.tex
Final changes

@@
 This multi-optics method was tested on a fully accumulated production beam in the SNS using ten measurements (forty profiles), which were collected in one hour.
-The reconstructed Twiss parameters, emittances, and best-fit ellipses in the $x$-$x'$ and $y$-$y'$ planes (normalized by the reconstructed Twiss parameters) are displayed in Fig.~\ref{fig:2}.
+The reconstructed Twiss parameters, emittances, and best-fit ellipses in the $x$-$x'$ and $y$-$y'$ planes are displayed in Fig.~\ref{fig:2}.
 %
@@
     \includegraphics[width=\columnwidth]{fig2.pdf}
+    \vfill
+    \vspace*{0.1cm}
+    \vfill
     % \par\medskip
@@
     % \par\medskip
-    \caption{Reconstructed beam parameters and graphical output (in normalized phase space) from a multi-optics emittance measurement of a production beam.}
+    \caption{Reconstructed beam parameters and graphical output from a multi-optics emittance measurement of a production beam.
+Each measurement defines a vertical line at $x = \sqrt{\langle{xx}\rangle}$ and $y = \sqrt{\langle{yy}\rangle}$ in phase space at the measurement location.
+These lines are transported to the reconstruction location using the transfer matrix and plotted on top of the reconstructed ellipses (gray).
+The coordinates are normalized by the reconstructed Twiss parameters so that the ellipses are circles with areas proportional to $\varepsilon_{x, y}$.}
     \label{fig:2}
@@
     \includegraphics[width=0.5\textwidth]{fig3.pdf}
-    \caption{Measured profiles of a production beam at WS20 in the RTBT.}
+    \caption{Measured profiles of a production beam along the horizontal ($x$), vertical ($y$), and diagonal ($u$) axis at wire-scanner WS20 in the RTBT.
+Two measurements are overlayed with identical machine settings.}
     \label{fig:3}
@@
     \includegraphics[width=\columnwidth]{fig4.pdf}
-    \caption{Simulated emittance measurement using the nominal optics in the RTBT.}
+    \caption{Simulated emittance measurement using the nominal RTBT optics. The true values are $\varepsilon_1 = \varepsilon_x$ = 32 mm~mrad and $\varepsilon_2 = \varepsilon_y$ = 25 mm~mrad.}
     \label{fig:4}
@@
     \includegraphics[width=\columnwidth]{fig5.pdf}
-    \caption{Simulated bias and standard deviation of the intrinsic emittances in the RTBT as a function of the phase advances at WS24.}
+    \caption{Simulated bias and standard deviation of the intrinsic emittances in the RTBT as a function of the phase advances at WS24.
+The true values are $\varepsilon_1 = \varepsilon_2 = \varepsilon_x = \varepsilon_y$ = 20 mm~mrad.
+Settings that produced no successful trials appear as white cells.}
     \label{fig:5}
@@
 (b) For each subfigure in (a), from left to right, we plot the distribution of intrinsic emittances generated by the random trials for one set of Twiss parameters (greyscale).
-Each blue shaded band is centered at the mean of the distribution one axis, with a width equal to twice the standard deviation along that axis.
+Each blue shaded band is centered at the mean of the distribution along one axis, with a width equal to twice the standard deviation along that axis.
 The red lines show the true values of the emittances.}
@@
 %
-Settings that produced no successful trials appear as white cells.
 The apparent emittances are not displayed because they remained within 1\% of their true values at every optics setting.
@@
     \end{tabular}
-    \caption{Measured and model Twiss values in the RTBT.}
+    \caption{Measured and model beam Twiss parameters in the RTBT.}
     \label{tab:mismatch}
@@
 (a) correlated (production) painting at 1 GeV; (b) attempted elliptical painting at 1 GeV; (c)-(d) elliptical painting at 0.8 GeV.
-In (d), the painted beam size was increased and the beam intensity was decreased relative to (c).}
+In (d), the painted beam size was increased and the beam intensity was decreased relative to (c).
+Each error bar is calculated from the mean and standard deviation of 5000 trials: in each trial, the emittances are reconstructed from a random 3\% perturbation of the measured moments.}
     \label{fig:7}
@@
     \caption{Emittance distribution used to produce the error bars in Fig.~\ref{fig:7}d at (a) 150 turns (b) 400 turns.
-The points were generated by reconstructing the covariance matrix from perturbations of the measured moments.
-The measured values are plotted in red.}
+5000 reconstructions were performed from random 3\% perturbations of the measured moments.
+The measured emittances are plotted in red.}
     \label{fig:9}
